### 2017-01-24 paper/images/flowchart/flowchart_conf.tex
[minor] add rough draft

% make sure to download following files before compiling-
% tikzlibrarynode-families.code.tex
% tikzlibrarypositioning-plus.code.tex
% please keep the above files in the same directory
\documentclass[border=2pt]{standalone}
\usepackage{tikz}

\usetikzlibrary{shapes.geometric,backgrounds,positioning-plus,node-families,calc}
\tikzset{
  basic box/.style = {
    shape = rectangle,
    align = center,
    draw  = #1,
    fill  = #1!25,
    %font  = \large,
    rounded corners},
  header node/.style = {
    %Minimum Width = header nodes,
    %font          = \Large\bf,
    %text depth    = +0pt,
    fill          = white,
    draw},
  header/.style = {%
    inner xsep = +1.0em,
    inner ysep = +0.8em,
    append after command = {
      \pgfextra{\let\TikZlastnode\tikzlastnode}
      node [header node] (header-\TikZlastnode) at (\TikZlastnode.north) {#1}
      node [span = (\TikZlastnode)(header-\TikZlastnode)]
        at (fit bounding box) (h-\TikZlastnode) {}
    }
  },
  hv/.style = {to path = {-|(\tikztotarget)\tikztonodes}},
  vh/.style = {to path = {|-(\tikztotarget)\tikztonodes}},
  fat blue line/.style = {ultra thick, blue}
}

\def \scaling {3.5cm}
\begin{document}

\begin{tikzpicture}[every node/.style={transform shape}, thick, >=latex, node distance=1cm]
	\node[basic box = blue, header = Teaching Phase] (teaching) {
		\includegraphics[width=\scaling]{teaching}%\\
		%A demonstration is performed by moving the \\
		%Baxter arms in the appropriate trajectory
	};

	%\node[north right = of teaching, basic box = orange, header = Trajectory Parameterization] (dmp)
	\node[north right = of teaching, basic box = orange, header = Learn Trajectory] (dmp) {
		%Baxter Left Arm Trajectory\\
		\includegraphics[width=\scaling]{dmp}%\\
		%Recorded trajectory is parameterized by DMP
	};

	\node[east below = of teaching, basic box = green, header = Testing Phase] (testing) {
		%Modified Posture\\
		\includegraphics[width=\scaling]{testing}%\\
		%DMP can accomodate new posture
	};

	\node[north right = of testing, basic box = red, header = DMP Generalization] (generalization){
		%DMP Trajectory\\
		\includegraphics[width=\scaling]{dmp_new}
	};

	\path[ultra thick, blue, ->](teaching) edge[->] (dmp);
	\path[ultra thick, orange, ->](dmp) edge[->] (testing);
	\path[ultra thick, green, ->](testing) edge[->] (generalization);
\end{tikzpicture}
\end{document}

### 2017-01-24 paper/paper.tex
[minor] add rough draft

\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
  Paso, Texas USA}
\acmYear{1997}
\copyrightyear{2016}

\acmPrice{15.00}

\begin{document}
\title{Robotic cloth manipulation for clothing assistance task using Dynamic Movement
Primitives}
\titlenote{Produces the permission block, and copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

\author{Ravi P. Joshi}
\authornote{Dr.~Trovato insisted his name be first.}
\orcid{1234-5678-9012}
\affiliation{%
	\institution{Institute for Clarity in Documentation}
	\streetaddress{P.O. Box 1212}
	\city{Dublin}
	\state{Ohio}
	\postcode{43017-6221}
}
\email{joshi-ravi-prakash@edu.brain.kyutech.ac.jp}

\author{Nishanth Koganti}
\authornote{The secretary disavows any knowledge of this author's actions.}
\affiliation{%
	\institution{Institute for Clarity in Documentation}
	\streetaddress{P.O. Box 1212}
	\city{Dublin}
	\state{Ohio}
	\postcode{43017-6221}
}
\email{nishanth-k@is.naist.jp}

\author{Tomohiro Shibata}
\authornote{This author is the
one who did all the really hard work.}
\affiliation{%
	\institution{The Th{\o}rv{\"a}ld Group}
	\streetaddress{1 Th{\o}rv{\"a}ld Circle}
	\city{Hekla}
	\country{Iceland}}
\email{tom@brain.kyutech.ac.jp}

%\author{Lawrence P. Leipuner}
%\affiliation{
%  \institution{Brookhaven Laboratories}
%  \streetaddress{P.O. Box 5000}}
%\email{lleipuner@researchlabs.org}
%
%\author{Sean Fogarty}
%\affiliation{%
%  \institution{NASA Ames Research Center}
%  \city{Moffett Field}
%  \state{California}
%  \postcode{94035}}
%\email{fogartys@amesres.org}
%
%\author{Charles Palmer}
%\affiliation{%
%  \institution{Palmer Research Laboratories}
%  \streetaddress{8600 Datapoint Drive}
%  \city{San Antonio}
%  \state{Texas}
%  \postcode{78229}}
%\email{cpalmer@prl.com}
%
%\author{John Smith}
%\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
%\email{jsmith@affiliation.org}
%
%\author{Julius P.~Kumquat}
%\affiliation{\institution{The Kumquat Consortium}}
%\email{jpkumquat@consortium.net}
%
% The default list of authors is too long for headers}
%\renewcommand{\shortauthors}{B. Trovato et al.}

\graphicspath{{./images/}}

\begin{abstract}
	The need of robotic clothing assistance in the field of assistive robotics is growing, as it is one of the most basic activities in daily life of elderly and disabled people. In this study, we are investigating the applicability of using Dynamic Movement Primitives (DMP) as a task parameterization model for performing clothing assistance tasks. The robotic cloth manipulation task deals with putting the cloth on both the arms. The robot should do cooperative manipulation by holding the cloth. Also, there can be many failure scenarios as clothes are highly non-rigid. DMP can represent nonlinear motion with a set of differential equations. These equations can be adapted to generate any movement trajectory just by changing the goal parameter. The system consists of Baxter humanoid robot and Microsoft Kinect RGBD sensor for tracking the posture of hands. To perform the task, a demonstration is recorded by moving the Baxter arms in the appropriate trajectory. The recorded trajectory is parameterized by using DMP. Once the system is trained, new postures are accommodated by DMP. The cloth manipulation is done by Baxter humanoid robot which follows the trajectory generated by DMP. We have performed the experiments on soft mannequin instead of human. The result shows that DMPs are able to generalize the movement trajectory for the modified posture also.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10010520.10010553.10010562</concept_id>
	<concept_desc>Computer systems organization~Embedded systems</concept_desc>
	<concept_significance>500</concept_significance>
	</concept>
	<concept>
	<concept_id>10010520.10010575.10010755</concept_id>
	<concept_desc>Computer systems organization~Redundancy</concept_desc>
	<concept_significance>300</concept_significance>
	</concept>
	<concept>
	<concept_id>10010520.10010553.10010554</concept_id>
	<concept_desc>Computer systems organization~Robotics</concept_desc>
	<concept_significance>100</concept_significance>
	</concept>
	<concept>
	<concept_id>10003033.10003083.10003095</concept_id>
	<concept_desc>Networks~Network reliability</concept_desc>
	<concept_significance>100</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

% We no longer use \terms command
%\terms{Theory}

\keywords{Robotic Clothing Assistance, Dynamic Movement Primitives (DMP)}

\maketitle

\section{Introduction}

The \textit{proceedings} are the records of a conference\footnote{This
is a footnote}.  ACM seeks
to give these conference by-products a uniform, high-quality
appearance.  To do this, ACM has some rigid requirements for the
format of the proceedings documents: there is a specified format
(balanced double columns), a specified set of fonts (Arial or
Helvetica and Times Roman) in certain specified sizes, a specified
live area, centered on the page, specified size of margins, specified
column width and gutter size.

\section{Related Works}
Typically, the body of a paper is organized into a hierarchical
structure, with numbered or unnumbered headings for sections,
subsections, sub-subsections, and even smaller sections.  The command
\texttt{{\char'134}section} that precedes this paragraph is part of
such a hierarchy.\footnote{This is a footnote.} \LaTeX\ handles the
numbering and placement of these headings for you, when you use the
appropriate heading commands around the titles of the headings.  If
you want a sub-subsection or smaller part to be unnumbered in your
output, simply append an asterisk to the command name.  Examples of
both numbered and unnumbered headings will appear throughout the
balance of this sample document.

\section{Dynamic Movement Primitives}
Dynamic Movement Primitives (DMP) aims at designing contoller for learning and generalization of Motor Skills by learning from demonstration \cite{ijspeert2013dynamical}. The controllers are based on nonlinear dynamical systems, and use locally weighted regression techniques to learn complex, discrete or rhythmic, movements demonstrated by a human subject. These controllers can be considered to be discrete or rhythmic pattern generators which can replay and modulate the learned movements, while being robust against perturbations.

The basic idea behind DMP formulation is to use an analytically well-understood dynamical system and add a nonlinear terms, so that it produces the desired behavior \cite{ijspeert2013dynamical}. Formally, the system is defined by a damped spring model as below:

\begin{equation}
	\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y}) + f
\end{equation}

The term $\alpha_y$ and $\beta_y$ are positive gain terms. $y$ is the system state and $g$ represents goal state. The nonlinear function $f$, which is also called as forcing term is defined over time, making the problem a well defined structure that can be solved in a straight-forward way. This system is termed as canonical dynamical system, denoted by $x$ and has very simple dynamics:

\begin{equation}
	\dot{x} = -\alpha_x x
\end{equation}

The forcing function $f$ is chosen as a function of canonical system:

\begin{equation}
	f(x,g) = \frac{\Sigma_{i=1}^N \psi_i w_i}{\Sigma_{i=1}^N \psi_i} x(g - y_0)
	\label{forcing_func}
\end{equation}

with $N$ exponential basis functions $\psi_i$ and $y_0$ is the initial position of the system,

\begin{equation}
	\psi_i = \textrm{exp}\left( -h_i \left( x - c_i\right)^2 \right)
\end{equation}

where $h_i$ and $c_i$ are constants that determine, respectively, the width and centers of the basis functions. In this way, the forcing function $f$ is comprised of weighted summation of Gaussians, that are going to be activated as system converges to the goal as shown in figure \ref{psi_activations}.

\begin{figure}
	\includegraphics[width=0.45\textwidth]{psi}
	\caption{$\psi$ activations and weighted summation of Gaussians}
	\label{psi_activations}
\end{figure}

Our goal is to design the forcing function that can learn from the demonstration and allows us to scale the movement defined by goal state $g$. In other words, we want to setup the system which can follow a specified path. The forcing term can be redefined as:

\begin{equation}
	\textbf{f}_d = \ddot{\textbf{y}}_d - \alpha_y ( \beta_y (g - \textbf{y}) - \dot{\textbf{y}})
\end{equation}

where desired acceleration $\ddot{\textbf{y}}_d$ can be calculated by double differentiating the position data as:

\begin{equation*}
	\ddot{\textbf{y}}_d = \frac{\partial}{\partial t} \dot{\textbf{y}}_d = \frac{\partial}{\partial t} \frac{\partial}{\partial t} \textbf{y}_d
\end{equation*}

This ends by calculating the weight parameters across Gaussians. Optimization methods such as locally weighted regression can be used, so that the forcing function matches the desired trajectory. In other words equation can be re-written as-

\begin{equation}
	\Sigma_t \psi_i(t)(f_d(t) - w_i (x(t) (g - y_0)))^2
\end{equation}

The solution\cite{vijayakumar2000locally} is given by:

\begin{equation}
	w_i = \frac{\textbf{s}^T \pmb{\psi}_i \textbf{f}_d}{\textbf{s}^T \pmb{\psi}_i \textbf{s}}
\end{equation}

where
\begin{equation*}
	\textbf{s} = \left( \begin{array}{c}x_{t_0}(g - y_0) \\ \vdots \\ x_{t_N}(g - y_0) \end{array} \right), \;\;\; \pmb{\psi}_i = \left( \begin{array}{ccc} \psi_i(t_0) & \dots & 0 \\ 0 & \ddots & 0 \\ 0 & \dots & \psi_i(t_n) \end{array} \right)
\end{equation*}

This way the DMP can be made to imitate the desired path.

\section{Overview of the System}
Robotic cloth manipulation task contains a dual arm humanoid robot Baxter. The complete setup is shown in figure \ref{setup}. We choose soft mannequin instead of a human for this preliminary experiment. Both the arms of mannequin are open and  given the support by a metallic stand, to avoid falling down the arms. The mannequin is positioned in such a way, so that it resides within the limits of work space of the Baxter robot. Also both the arms of mannequin are facing towards robot. A kinect v2 sensor is mounted on the LCD display of Baxter root. Kinect sensor can see the mannequin and clothing article. Before starting the experiment, the clothing article is put in arms of the baxter robot manually.

\begin{figure}
	\includegraphics[width=0.45\textwidth]{setup}
	\caption{Setup of Robotic cloth manipulation task}
	\label{setup}
\end{figure}

The Baxter robot is connected to a computer directly using Ethernet cable. It is controlled using Robot Operating System (ROS), one of the widely used tool by the researchers in robotics community. We used Baxter robot's API, which are available and supported by ROS \cite{fitzgerald2013developing} to command the robot. The Kinect sensor is also controlled by Open source Kinect API for ROS.

\begin{figure*}
	\includegraphics[width=\textwidth]{flowchart_conf}
	\caption{Work flow of Robotic cloth manipulation task. Initially a demonstration is performed by moving the Baxter arms in the appropriate trajectory. The demonstration is recorded and parameterized by DMP. Later posture of the mannequin is changed and accordingly the goal posture of DMP is modified. Now, the modified DMP can accommodate new posture.}
	\label{workflow}
\end{figure*}

\section{Experiments}
As per the formulation \ref{setup}, the DMP can learn by the demonstration. Hence we starts by performing a demonstration by holding the robot arm and move accordingly. During the demonstration, pose of the end-effector is recorded. The term pose collectively refers to position and orientation. Once the demonstration is finished, DMP is initialized using the recorded trajectory. Three DMP trajectories one for each coordinate axis are initialized for one arm. In this way, we have totally six DMP trajectories, which can control both the arms of Baxter robot. We performed following two experiments by using these trajectory- (a) Clothing task using position DMP (b) Failure detection using end-effector forces.

\subsection{Clothing task using position DMP}
The aim of this experiment is to put the clothing article on both the arms of mannequin by using DMP system. We use the position data to initialize the DMP trajectories, which are being used in this task. The posture of mannequin is changed by lifting the arms up or down. At this point, we use Kinect Sensor to get the 3D coordinates of the arm. Now we change the goal of DMP trajectories by using this information. The modified DMP can be acquired from equation 1.

\subsection{Failure detection using end-effector forces}
This experiment is designed to deal with failure cases. There can be many failure cases during the clothing task, such as the clothing article gets stuck into the fingers. In this experiment, we are using forces being applied on the end-effector of Baxter robot to detect the failure scenario. Appropriate action can be taken once the failure is detected.

\section{Results}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.

\begin{acks}
	The authors would like to thank Dr. Yuhua Li for providing the
	matlab code of  the \textit{BEPS} method.

	The authors would also like to thank the anonymous referees for
	their valuable comments and helpful suggestions. The work is
	supported by the \grantsponsor{GS501100001809}{National Natural
		Science Foundation of
		China}{http://dx.doi.org/10.13039/501100001809} under Grant
	No.:~\grantnum{GS501100001809}{61273304}
	and~\grantnum[http://www.nnsf.cn/youngscientsts]{GS501100001809}{Young
	Scientsts' Support Program}.

\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{sigproc}

\end{document}

### 2017-01-26 paper/images/inclination/inclination.tex
[major] add 1st draft

\documentclass{standalone}
%\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

\newcommand{\BoxWidth}{1.8cm}%
\tikzset{
    point/.style     = {coordinate},
    arrow/.style     = {thick, ->, >=stealth'},
    to/.style        = {->,>=stealth', shorten >=1pt, semithick, font=\footnotesize, draw=green},
    line/.style      = {line width=0.8mm, draw=red},
    darrow/.style     = { <->, line width=0.8mm, draw=red},
    decision/.style  = {draw, diamond, minimum width=\BoxWidth, minimum height=1cm, text centered, aspect=2, font=\footnotesize},
    process/.style   = {draw, rectangle, minimum width=\BoxWidth, minimum height=1cm, text centered, text width=\BoxWidth, font=\footnotesize},
    startstop/.style = {draw, rectangle, rounded corners, minimum width=\BoxWidth, minimum height=1cm,text centered, text width=\BoxWidth, font=\footnotesize},
    box/.style       = {draw, rectangle, minimum height = 1cm, minimum width = \BoxWidth, text centered, text width=\BoxWidth, ultra thin, draw=orange, fill=orange!30, font=\footnotesize},
    smallBox/.style       = {draw, rectangle, minimum height = 0.5cm, minimum width = 0.5cm, text centered, ultra thin, draw=black, fill=green!30, font=\small}
}

\pgfmathsetmacro{\ex}{0.85}
\pgfmathsetmacro{\ey}{0.60}

\begin{document}
\begin{tikzpicture}
	\node[anchor=south west,inner sep=0] (image) at (0,0,0) {\includegraphics[width=\linewidth]{mannequin}};
	\begin{scope}[x={(image.south east)},y={(image.north west)}]
		\iffalse
		%% Next four lines helps to locate the point needed by forming a grid
		\draw[help lines,xstep=.1,ystep=.1] (0,0) grid (1,1);
		\draw[help lines,xstep=.05,ystep=.05] (0,0) grid (1,1);
		\foreach \x in {0,1,...,9} {\node[anchor=north] at (\x/10,0) {0.\x}; }
		\foreach \y in {0,1,...,9} {\node[anchor=east] at (0,\y/10) {0.\y};}
		\fi
		\begin{scope}[x={(image.south east)},y={(image.north west)}]
			%\draw[to] (0.85,0.90) node[box,text width=3cm] {Baxter Robot} -- (0.62,0.82);
			\draw[line] (0.30,0.60) -- (\ex,\ey);
			\draw[line] (0.20,0.25) -- (\ex,\ey);
			%\draw[to] (0.25,0.35) node[box] {Location of contact point} -- (0.64,0.59);
			\draw[darrow](\ex,\ey) ++(-152:.2) arc (-152:-180:.2) node[xshift=-3cm, yshift=0.5cm, color=red, font=\huge] {\textbf{Angle of inclination ($\alpha$)}} ;
		\end{scope}
	\end{scope}
\end{tikzpicture}
\end{document}

### 2017-01-26 paper/paper.tex
[major] add 1st draft

@@
 
-\usepackage{booktabs} % For formal tables
+%\usepackage{booktabs} % For formal tables
+\usepackage{subcaption}
 
@@
 We have performed the experiments on soft mannequin instead of human.
-The result shows that DMPs are able to generalize the movement trajectory for the modified posture also.
+The result shows that DMPs are able to generalize the movement trajectory for the modified posture.
 \end{abstract}
@@
 
-\keywords{Robotic Clothing Assistance, Dynamic Movement Primitives (DMP)}
+\keywords{Robotic Clothing Assistance, Dynamic Movement Primitives (DMP), Human-Robot Interaction, Learning and Adaptive Systems}
 
@@
 
+\begin{figure}
+	\includegraphics[width=0.45\textwidth]{setup}
+	\caption{Setup of Robotic cloth manipulation task}
+	\label{setup}
+\end{figure}
+
 \section{Introduction}
+\label{introduction}
+Due to the demographic trend in developed countries, the robotic assistance in the filed of elderly care is in home environments growing \cite{broekens2009assistive}.
+Although there has been a significant number of research done in this field, robotic clothing assistance, one of the basic and important assistance activities in daily life of elderly as well as disabled people is yet an open field for research.
+While rigid object manipulation with robots has mainly relied on precise robot control, the deformable objects are rather require a complex control scheme.
+The clothing assistance is a challenging problem since robots must interact with non-rigid and highly deformable clothes, and with the assisted person whose posture can vary during the assistance.
 
-The \textit{proceedings} are the records of a conference\footnote{This
-is a footnote}.  ACM seeks
-to give these conference by-products a uniform, high-quality
-appearance.  To do this, ACM has some rigid requirements for the
-format of the proceedings documents: there is a specified format
-(balanced double columns), a specified set of fonts (Arial or
-Helvetica and Times Roman) in certain specified sizes, a specified
-live area, centered on the page, specified size of margins, specified
-column width and gutter size.
+In this study, we are investigating the applicability of using Dynamic Movement Primitives (DMP) as a task parameterization model for performing clothing assistance tasks.
+The robotic cloth manipulation task deals with putting the cloth on both the arms.
+The idea of using DMP is inspired from the fact that DMP can learn the complex task from the demonstration \cite{ijspeert2003learning, schaal2006dynamic, ijspeert2013dynamical} and thus reduce the manual efforts to design the controller from scratch or to fine-tune the controller parameters.
+We choose the dual arm Baxter robot in this research as it is safe and flexible by the design \cite{fitzgerald2013developing}.
+
+The rest of the paper is organized as follows.
+Section \ref{related_works}, gives a brief overview about the related literature in this field.
+Section \ref{dmp} introduces the mathematical formulation about Dynamic Movement Primitives.
+In Section \ref{system_overview}, we describe our system and various components used in the experiments.
+Section \ref{experiments} deals with the details about experiments performed.
+Section \ref{results} shows the experimental results.
+Finally we conclude in Section \ref{conclusions} with some future directions.
 
 \section{Related Works}
-Typically, the body of a paper is organized into a hierarchical
-structure, with numbered or unnumbered headings for sections,
-subsections, sub-subsections, and even smaller sections.  The command
-\texttt{{\char'134}section} that precedes this paragraph is part of
-such a hierarchy.\footnote{This is a footnote.} \LaTeX\ handles the
-numbering and placement of these headings for you, when you use the
-appropriate heading commands around the titles of the headings.  If
-you want a sub-subsection or smaller part to be unnumbered in your
-output, simply append an asterisk to the command name.  Examples of
-both numbered and unnumbered headings will appear throughout the
-balance of this sample document.
+\label{related_works}
+In this section, we provide brief overview of the related literature in this field.
+There has been significant number of research done in the field of Robotic Clothing Assistance.
+Colom{\'e} et al.
+\cite{colome2015friction} proposed a framework for Reinforcement Learning of Robotic Tasks in non-rigid environments.
+They performed the task of wrapping a scarf around the neck of a mannequin and used color based segmentation to distinguish mannequin, scarf and a mark placed on the nose of mannequin.
+The main focus of their work is to incorporate friction based model while performing clothing task.
+Gao et al.
+\cite{gao2015user, gao2016iterative} has focused on user upper-body modeling for personalized dressing by using top-view depth camera.
+Randomised decision forests was used to estimate user pose and proposed an online iterative path optimisation method to enable Baxter humanoid robot to assist human to wear a sleeveless jacket.
+Another interesting work by Kapusta et al.
+\cite{kapusta2016data} is focused towards designing a controller inspired from data-driven haptic perception.
+They classified the forces measured at robot's end effector by using hidden Markov models and performed the clothing task on hospital gown.
+Their focus was to classify force data for haptic perception with high accuracy.
+Klee et al.
+\cite{klee2015personalized} worked on personalized assistance for dressing a user, where they used vision module to monitor the human's motion.
+The robot request to user to move towards robot, monitors motion and puts hat on the user once users is rechable by the robot.
+Koganti et al.
+\cite{koganti2015cloth} proposed a framework for offline learning of cloth dynamics model using Gaussian Process Latent Variable Models (GP-LVM) by incorporating motion capture data and applying this model for the online tracking of human-cloth relationship using a depth sensor.
+They showed that the shared GP-LVM is able to learn reliable motion models of the T-shirt state for robotic clothing assistance tasks.
+Representing cloth state in low-dimensional field by using topology coordinates is another impressive work done by Tamei et al.
+\cite{tamei2011reinforcement}.
+They proposed Reinforcement Learning framework and demonstrated that the robot quickly learns a suitable arm motion for putting T-shirt into the mannequin's head.
+Yamazaki et al.
+\cite{yamazaki2013method, yamazaki2014bottom}  worked on bottom dressing by a Life-sized humanoid robot, where they recognize the cloth state by using  optical flow on the images acquired from single camera.
+They showed that the robot can pull a bottom clothing item along the subject's legs.
+
+Another related filed of research is Motor-skills Learning for Cloth Handling, in which Yamakawa et al.
+\cite{yamakawa2011dynamic} proposed a new strategy for dynamic manipulation of sheet-like flexible objects by a high-speed robot system.
+The system consists of two high-speed multi-fingered hands mounted on two sliders and a high-speed vision system.
+The proposed system learns the necessary motor skills from the demonstration performed by a human subject.
+They validated the robot trajectory obtained from the motion planning method was with simulation results.
+Another exciting work done by Mons{\'o} et al.
+\cite{monso2012pomdp}, where they proposed a probabilistic planner, based on Partially Observable Markov Decision Process (POMDP) approach, for reducing the inherent uncertainty of cloth sorting (isolation/extraction) task.
+Their approach relaxes the precision requirements of robot vision and manipulation.
+
+\begin{figure}
+	\includegraphics[width=0.45\textwidth]{psi}
+	\caption{$\psi$ activations and weighted summation of Gaussians}
+	\label{psi_activations}
+\end{figure}
 
 \section{Dynamic Movement Primitives}
-Dynamic Movement Primitives (DMP) aims at designing contoller for learning and generalization of Motor Skills by learning from demonstration \cite{ijspeert2013dynamical}.
-The controllers are based on nonlinear dynamical systems, and use locally weighted regression techniques to learn complex, discrete or rhythmic, movements demonstrated by a human subject.
+\label{dmp}
+Dynamic Movement Primitives (DMP) aims at designing contoller for learning and generalization of Motor Skills by learning from demonstration \cite{ijspeert2003learning}.
+The controllers are based on nonlinear dynamical systems, and use locally weighted regression techniques to learn complex, discrete or rhythmic, movements demonstrated by a human subject \cite{ijspeert2002movement}.
 These controllers can be considered to be discrete or rhythmic pattern generators which can replay and modulate the learned movements, while being robust against perturbations.
@@
 In this way, the forcing function $f$ is comprised of weighted summation of Gaussians, that are going to be activated as system converges to the goal as shown in figure \ref{psi_activations}.
-
-\begin{figure}
-	\includegraphics[width=0.45\textwidth]{psi}
-	\caption{$\psi$ activations and weighted summation of Gaussians}
-	\label{psi_activations}
-\end{figure}
 
@@
 This way the DMP can be made to imitate the desired path.
+However, this formulation of DMP suffers from critical issues when used in practical application, such as when the scaling term of $f$, $g-x_0$ if close to zero, a small change in $g$ may lead to huge acceleration and thus it may break the limits of robot.
+We used the improved version of DMP \cite{pastor2009learning} in this research.
 
 \section{Overview of the System}
+\label{system_overview}
 Robotic cloth manipulation task contains a dual arm humanoid robot Baxter.
@@
 
-\begin{figure}
-	\includegraphics[width=0.45\textwidth]{setup}
-	\caption{Setup of Robotic cloth manipulation task}
-	\label{setup}
-\end{figure}
-
 The Baxter robot is connected to a computer directly using Ethernet cable.
 It is controlled using Robot Operating System (ROS), one of the widely used tool by the researchers in robotics community.
-We used Baxter robot's API, which are available and supported by ROS \cite{fitzgerald2013developing} to command the robot.
+We used Baxter robot's API, which are available and supported by ROS to command the robot.
 The Kinect sensor is also controlled by Open source Kinect API for ROS.
@@
 \section{Experiments}
+\label{experiments}
 As per the formulation \ref{setup}, the DMP can learn by the demonstration.
@@
 Now we change the goal of DMP trajectories by using this information.
-The modified DMP can be acquired from equation 1.
+The modified DMP can be acquired as described in section \ref{dmp}.
 
@@
 \section{Results}
-This paragraph will end the body of this sample document.
-Remember that you might still have Acknowledgments or
-Appendices; brief samples of these
-follow.  There is still the Bibliography to deal with; and
-we will make a disclaimer about that here: with the exception
-of the reference to the \LaTeX\ book, the citations in
-this paper are to articles which have nothing to
-do with the present subject and are used as
-examples only.
+\label{results}
+A soft mannequin was used in order to perform the clothing task.
+A sleeveless tee shirt was used during the experiment and the task was to put the clothing article on both the arms as shown in figure \ref{various_posture}.
+Following subsections explains the results of the two experiments described above.
+
+\begin{figure}
+	\includegraphics[width=0.45\textwidth]{various_posture}
+	\caption{Various postures used in Clothing task}
+	\label{various_posture}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=0.45\textwidth]{trajectory}
+	\caption{Left arm trajectory of Baxter}
+	\label{trajectory}
+\end{figure}
+
+\subsection{Clothing task using position DMP}
+In this experiment, the initialized DMP was modified to accommodate the new posture by changing the goal state of the DMP.
+The generated trajectory was then run on the Baxter robot as shown in figure \ref{trajectory}.
+The newly generated DMP trajectory (shown in red color) was not only found well suited and capable of performing clothing task but also smooth compared to the original trajectory (shown in blue color).
+A video demonstartion of this experiment can be seen at YouTube\footnote{\url{http://youtu.be/Rb2JePazJjk}}.
+
+To eventuate this experiment, we performed it many times for various postures by keeping the arms at different-different height.
+During the experiment, we monitored the trajectory generated by DMP system.
+The accuracy measurement is shown in figure \ref{accuracy}.
+
+\begin{figure}
+	\centering
+	\begin{subfigure}{.2\textwidth}
+		\includegraphics[width=\linewidth]{inclination}
+	\end{subfigure}%
+	\begin{subfigure}{.26\textwidth}
+		\includegraphics[width=\linewidth]{accuracy}
+	\end{subfigure}
+	\caption{Accuracy measurement}
+	\label{accuracy}
+\end{figure}
+
+\subsection{Failure detection using end-effector forces}
+The clothing task has to deal with complex dynamics including manipulation of clothing article.
+The clothes are non-rigid, flexible and highly deformable objects, making the task more difficult to perform.
+During the clothing task, we observed the forces being applied at both the end-effector of Baxter robot.
+The trajectories were monitored and categorized into two \textit{success} and \textit{failure}.
+The mean of these two category is calculated and plotted as shown in figure \ref{position_force}.
+
+It is clearly visible from the figure \ref{position_force} that the applied forces are very different in nature in both the cases.
+Both of these applied forces are increasing from the beginning however the applied forces in case of \textit{failure} are much more higher than that of \textit{success}.
+Hence one can easily differentiate and detect the failure by using this information.
+
+\begin{figure}
+	\includegraphics[width=0.45\textwidth]{position_force}
+	\caption{Failure detection using end-effector forces}
+	\label{position_force}
+\end{figure}
 
 \section{Conclusions}
-This paragraph will end the body of this sample document.
-Remember that you might still have Acknowledgments or
-Appendices; brief samples of these
-follow.  There is still the Bibliography to deal with; and
-we will make a disclaimer about that here: with the exception
-of the reference to the \LaTeX\ book, the citations in
-this paper are to articles which have nothing to
-do with the present subject and are used as
-examples only.
+\label{conclusions}
+This paper presents an approach for robotic cloth manipulation for clothing assistance task using Dynamic Movement Primitives.
+A dual arm Baxter robot, soft mannequin and very thin sleeveless tee shirt were used in the task.
+The authors have also presented an approach for failure detection using forces being applied on the end-effector of the robot.
+Authors have used the Baxter APIs in order to get the forces, which are calculated by Baxter Dynamics Module.
+Though raw forces were very noisy in nature, but after applying median filter most of the noise was eliminated properly.
+
+We plan to extend our research to make the approach more robust by adding visual information and force information with DMP system in the future.
+Also there is a need of designing an adaptive controller for real time tracking to adapt and detect various failure scenarios.
+Therefore, in the future, a combination of robot vision and force data can provide the better estimation of cloth state.
 
 \begin{acks}
-	The authors would like to thank Dr. Yuhua Li for providing the
-	matlab code of  the \textit{BEPS} method.
-
-	The authors would also like to thank the anonymous referees for
-	their valuable comments and helpful suggestions. The work is
-	supported by the \grantsponsor{GS501100001809}{National Natural
-		Science Foundation of
-		China}{http://dx.doi.org/10.13039/501100001809} under Grant
-	No.:~\grantnum{GS501100001809}{61273304}
-	and~\grantnum[http://www.nnsf.cn/youngscientsts]{GS501100001809}{Young
-	Scientsts' Support Program}.
-
+	The authors would also like to thank the anonymous referees for their valuable comments and helpful suggestions.
+The work is supported by the \grantsponsor{GS501100001809}{National Natural Science Foundation of China}{http://dx.doi.org/10.13039/501100001809} under Grant No.:~\grantnum{GS501100001809}{61273304} and~\grantnum[http://www.nnsf.cn/youngscientsts]{GS501100001809}{Young Scientsts' Support Program}.
 \end{acks}
@@
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{sigproc}
+%\bibliographystyle{unsrt}
+\bibliography{air}
 

### 2017-01-27 paper/images/inclination/inclination.tex
[minor] add feedback NOT FINISHED YET

@@
     to/.style        = {->,>=stealth', shorten >=1pt, semithick, font=\footnotesize, draw=green},
-    line/.style      = {line width=0.8mm, draw=red},
-    darrow/.style     = { <->, line width=0.8mm, draw=red},
+    line/.style      = {line width=0.4mm, draw=blue},
+    darrow/.style     = { <->, line width=0.4mm, draw=blue},
     decision/.style  = {draw, diamond, minimum width=\BoxWidth, minimum height=1cm, text centered, aspect=2, font=\footnotesize},
@@
 		\begin{scope}[x={(image.south east)},y={(image.north west)}]
-			%\draw[to] (0.85,0.90) node[box,text width=3cm] {Baxter Robot} -- (0.62,0.82);
 			\draw[line] (0.30,0.60) -- (\ex,\ey);
 			\draw[line] (0.20,0.25) -- (\ex,\ey);
-			%\draw[to] (0.25,0.35) node[box] {Location of contact point} -- (0.64,0.59);
-			\draw[darrow](\ex,\ey) ++(-152:.2) arc (-152:-180:.2) node[xshift=-3cm, yshift=0.5cm, color=red, font=\huge] {\textbf{Angle of inclination ($\alpha$)}} ;
+			\draw[darrow](\ex,\ey) ++(-152:.2) arc (-152:-180:.2) node[xshift=-3cm, yshift=0.5cm, color=blue, font=\large] {Angle of inclination ($\alpha$)} ;
 		\end{scope}

### 2017-01-27 paper/paper.tex
[minor] add feedback NOT FINISHED YET

@@
 \documentclass[sigconf]{acmart}
-
-%\usepackage{booktabs} % For formal tables
 \usepackage{subcaption}
@@
 % DOI
-\acmDOI{10.475/123_4}
+\acmDOI{To_be_inserted_after_paper_is_accepted}
 
 % ISBN
-\acmISBN{123-4567-24-567/08/06}
+\acmISBN{000-0000-00-000/00/00}
 
 %Conference
-\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
-  Paso, Texas USA}
-\acmYear{1997}
-\copyrightyear{2016}
+\acmConference[AIR 2017]{Advances in Robotics}{June 28-July 02, 2017}{New Delhi, India}
+\acmYear{2017}
+\copyrightyear{2017}
 
@@
 
-%\author{Lawrence P. Leipuner}
-%\affiliation{
-%  \institution{Brookhaven Laboratories}
-%  \streetaddress{P.O. Box 5000}}
-%\email{lleipuner@researchlabs.org}
-%
-%\author{Sean Fogarty}
-%\affiliation{%
-%  \institution{NASA Ames Research Center}
-%  \city{Moffett Field}
-%  \state{California}
-%  \postcode{94035}}
-%\email{fogartys@amesres.org}
-%
-%\author{Charles Palmer}
-%\affiliation{%
-%  \institution{Palmer Research Laboratories}
-%  \streetaddress{8600 Datapoint Drive}
-%  \city{San Antonio}
-%  \state{Texas}
-%  \postcode{78229}}
-%\email{cpalmer@prl.com}
-%
-%\author{John Smith}
-%\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
-%\email{jsmith@affiliation.org}
-%
-%\author{Julius P.~Kumquat}
-%\affiliation{\institution{The Kumquat Consortium}}
-%\email{jpkumquat@consortium.net}
-%
-% The default list of authors is too long for headers}
-%\renewcommand{\shortauthors}{B. Trovato et al.}
-
+% images are stored inside images directory
 \graphicspath{{./images/}}
@@
 The robotic cloth manipulation task deals with putting the cloth on both the arms.
-The robot should do cooperative manipulation by holding the cloth.
-Also, there can be many failure scenarios as clothes are highly non-rigid.
-DMP can represent nonlinear motion with a set of differential equations.
-These equations can be adapted to generate any movement trajectory just by changing the goal parameter.
-The system consists of Baxter humanoid robot and Microsoft Kinect RGBD sensor for tracking the posture of hands.
-To perform the task, a demonstration is recorded by moving the Baxter arms in the appropriate trajectory.
-The recorded trajectory is parameterized by using DMP.
-Once the system is trained, new postures are accommodated by DMP.
-The cloth manipulation is done by Baxter humanoid robot which follows the trajectory generated by DMP.
+The clothing assistance is a challenging problem since robot must do cooperative manipulation by holding the cloth using both the arms while interacting with non-rigid and highly deformable clothes, and with the assisted person whose posture can vary during the assistance.
+The system consists of dual arm Baxter research robot and Microsoft Kinect V2 RGBD sensor for tracking the posture of arms.
+The cloth manipulation is done by Baxter robot which follows the trajectory generated by DMP system.
 We have performed the experiments on soft mannequin instead of human.
@@
 \begin{figure}
-	\includegraphics[width=0.45\textwidth]{setup}
+	\includegraphics[width=\linewidth]{setup}
 	\caption{Setup of Robotic cloth manipulation task}
-	\label{setup}
+	\label{fig:setup}
 \end{figure}
@@
 \section{Introduction}
-\label{introduction}
-Due to the demographic trend in developed countries, the robotic assistance in the filed of elderly care is in home environments growing \cite{broekens2009assistive}.
-Although there has been a significant number of research done in this field, robotic clothing assistance, one of the basic and important assistance activities in daily life of elderly as well as disabled people is yet an open field for research.
-While rigid object manipulation with robots has mainly relied on precise robot control, the deformable objects are rather require a complex control scheme.
-The clothing assistance is a challenging problem since robots must interact with non-rigid and highly deformable clothes, and with the assisted person whose posture can vary during the assistance.
+\label{sec:introduction}
+Due to the demographic trend in developed countries, the robotic assistance in the field of elderly care in home environment is growing \cite{broekens2009assistive}.
+Although there has been a significant number of research done in this field, the robotic clothing assistance is yet an open field for research.
+Not to mention that, it is one of the basic and important assistance activities in daily life of elderly as well as disabled people.
+While rigid object manipulation with robots has mainly relied on precise robot control, the deformable objects rather require complex control scheme.
+The clothing assistance is a challenging problem since robot is required to manage two difficulties: (a) robot must do cooperative manipulation by holding the cloth using both the arms while interacting with non-rigid and highly deformable clothes and (b) maintain safe human-robot interaction with the assisted person whose posture can vary during the assistance.
 
@@
 The robotic cloth manipulation task deals with putting the cloth on both the arms.
-The idea of using DMP is inspired from the fact that DMP can learn the complex task from the demonstration \cite{ijspeert2003learning, schaal2006dynamic, ijspeert2013dynamical} and thus reduce the manual efforts to design the controller from scratch or to fine-tune the controller parameters.
-We choose the dual arm Baxter robot in this research as it is safe and flexible by the design \cite{fitzgerald2013developing}.
+The idea of using DMP is inspired from the fact that DMP can learn complex task from the demonstration \cite{ijspeert2003learning, schaal2006dynamic, ijspeert2013dynamical} and thus reduce the manual efforts to design the controller from scratch or to fine-tune the controller parameters.
+We choose the dual arm Baxter robot in this research as it is safe and flexible by design \cite{fitzgerald2013developing}.
 
 The rest of the paper is organized as follows.
-Section \ref{related_works}, gives a brief overview about the related literature in this field.
-Section \ref{dmp} introduces the mathematical formulation about Dynamic Movement Primitives.
-In Section \ref{system_overview}, we describe our system and various components used in the experiments.
-Section \ref{experiments} deals with the details about experiments performed.
-Section \ref{results} shows the experimental results.
-Finally we conclude in Section \ref{conclusions} with some future directions.
+Section \ref{sec:related_works}, gives a brief overview about the related literature in this field.
+Section \ref{sec:dmp} introduces the mathematical formulation about Dynamic Movement Primitives.
+In Section \ref{sec:system_overview}, we describe our system and various components used in the experiments.
+Section \ref{sec:experiments} deals with the details about experiments performed.
+Section \ref{sec:results} shows the experimental results.
+Finally we conclude in Section \ref{sec:conclusions} with some future directions.
 
 \section{Related Works}
-\label{related_works}
+\label{sec:related_works}
 In this section, we provide brief overview of the related literature in this field.
@@
 Colom{\'e} et al.
-\cite{colome2015friction} proposed a framework for Reinforcement Learning of Robotic Tasks in non-rigid environments.
+\cite{colome2015friction} proposed a framework for Reinforcement Learning of robotic tasks in non-rigid environments.
 They performed the task of wrapping a scarf around the neck of a mannequin and used color based segmentation to distinguish mannequin, scarf and a mark placed on the nose of mannequin.
@@
 Yamazaki et al.
-\cite{yamazaki2013method, yamazaki2014bottom}  worked on bottom dressing by a Life-sized humanoid robot, where they recognize the cloth state by using  optical flow on the images acquired from single camera.
+\cite{yamazaki2013method, yamazaki2014bottom}  worked on bottom dressing by a life-sized humanoid robot, where they recognize the cloth state by using  optical flow on the images acquired from single camera.
 They showed that the robot can pull a bottom clothing item along the subject's legs.
 
-Another related filed of research is Motor-skills Learning for Cloth Handling, in which Yamakawa et al.
+Another related filed of research is motor-skills learning for Cloth Handling, in which Yamakawa et al.
 \cite{yamakawa2011dynamic} proposed a new strategy for dynamic manipulation of sheet-like flexible objects by a high-speed robot system.
@@
 \begin{figure}
-	\includegraphics[width=0.45\textwidth]{psi}
+	\includegraphics[width=\linewidth]{psi}
 	\caption{$\psi$ activations and weighted summation of Gaussians}
-	\label{psi_activations}
+	\label{fig:psi_activations}
 \end{figure}
@@
 \section{Dynamic Movement Primitives}
-\label{dmp}
-Dynamic Movement Primitives (DMP) aims at designing contoller for learning and generalization of Motor Skills by learning from demonstration \cite{ijspeert2003learning}.
+\label{sec:dmp}
+Dynamic Movement Primitives (DMP) aims at designing contoller for learning and generalization of motor skills by learning from demonstration \cite{ijspeert2003learning}.
 The controllers are based on nonlinear dynamical systems, and use locally weighted regression techniques to learn complex, discrete or rhythmic, movements demonstrated by a human subject \cite{ijspeert2002movement}.
@@
 \begin{equation}
-	\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y}) + f
+	\tau	 \dot{v} = K (g - x) -D v - K (g - x_0) s + K f(s)
+\end{equation}
+\begin{equation}
+	\tau	 \dot{x} = v
 \end{equation}
 
-The term $\alpha_y$ and $\beta_y$ are positive gain terms.
-$y$ is the system state and $g$ represents goal state.
-The nonlinear function $f$, which is also called as forcing term is defined over time, making the problem a well defined structure that can be solved in a straight-forward way.
-This system is termed as canonical dynamical system, denoted by $x$ and has very simple dynamics:
+The term $x$ and $v$ are position and velocity of the system respectively, $x_0$ and $g$ are start and goal position, $\tau$ is a scaling term, $K$ is spring constant and $D$ is damping factor.
+The nonlinear function $f$, which is also called as forcing term is a non-linear function to be learned to allow complex movements.
+The forcing function $f$ is chosen as
 
 \begin{equation}
-	\dot{x} = -\alpha_x x
+	f(s) = \frac{\Sigma_{i} w_i \psi_i(s)}{\Sigma_{i} \psi_i(s)} s
+	\label{eq:forcing_func}
 \end{equation}
 
-The forcing function $f$ is chosen as a function of canonical system:
-
+where $\psi_i$ is defined as Gaussian basis function as
 \begin{equation}
-	f(x,g) = \frac{\Sigma_{i=1}^N \psi_i w_i}{\Sigma_{i=1}^N \psi_i} x(g - y_0)
-	\label{forcing_func}
-\end{equation}
-
-with $N$ exponential basis functions $\psi_i$ and $y_0$ is the initial position of the system,
-
-\begin{equation}
-	\psi_i = \textrm{exp}\left( -h_i \left( x - c_i\right)^2 \right)
+	\psi_i = \textrm{exp}\left( -h_i \left( s - c_i\right)^2 \right)
 \end{equation}
@@
 where $h_i$ and $c_i$ are constants that determine, respectively, the width and centers of the basis functions.
-In this way, the forcing function $f$ is comprised of weighted summation of Gaussians, that are going to be activated as system converges to the goal as shown in figure \ref{psi_activations}.
+$w_i$ represents the weight defined for each Gaussian.
+The forcing function $f$ depends on phase variable $s$.
+Phase variable $s$ starts from 1 and monotonically decreases to 0, defined by equation below:
 
+\begin{equation}
+	\tau \dot{s} = - \alpha s
+\end{equation}
+
+where $\alpha$ is a positive gain term.
 Our goal is to design the forcing function that can learn from the demonstration and allows us to scale the movement defined by goal state $g$.
@@
 \begin{equation}
-	\textbf{f}_d = \ddot{\textbf{y}}_d - \alpha_y ( \beta_y (g - \textbf{y}) - \dot{\textbf{y}})
+	f_{target}(s) = \frac{D v + \tau \dot{v}}{K} - - (g - x) +  (g - x_0) s
 \end{equation}
 
-where desired acceleration $\ddot{\textbf{y}}_d$ can be calculated by double differentiating the position data as:
+where desired acceleration $\dot{v}(t)$ can be calculated by double differentiating the position data recorded from the demonstration as
 
-\begin{equation*}
-	\ddot{\textbf{y}}_d = \frac{\partial}{\partial t} \dot{\textbf{y}}_d = \frac{\partial}{\partial t} \frac{\partial}{\partial t} \textbf{y}_d
-\end{equation*}
+\begin{equation}
+	\dot{v}(t) = \frac{\partial}{\partial t} v(t) = \frac{\partial}{\partial t} \frac{\partial}{\partial t} x(t)
+\end{equation}
+
+The forcing function [\ref{eq:forcing_func}] is comprised of weighted summation of Gaussian that are going to be activated as system converges to the goal as shown in figure \ref{fig:psi_activations}.
+We want that forcing function matches the desired trajectory.
+In other words, we want $f_{target}$ to be as close as possible of $f$ as written below:
+
+\begin{equation}
+	J = \sum_{s} \left( f_{target}(s) - f(s) \right)^2
+\end{equation}
 
 This ends by calculating the weight parameters across Gaussians.
-Optimization methods such as locally weighted regression can be used, so that the forcing function matches the desired trajectory.
-In other words equation can be re-written as-
-
-\begin{equation}
-	\Sigma_t \psi_i(t)(f_d(t) - w_i (x(t) (g - y_0)))^2
-\end{equation}
-
-The solution\cite{vijayakumar2000locally} is given by:
-
-\begin{equation}
-	w_i = \frac{\textbf{s}^T \pmb{\psi}_i \textbf{f}_d}{\textbf{s}^T \pmb{\psi}_i \textbf{s}}
-\end{equation}
-
-where
-\begin{equation*}
-	\textbf{s} = \left( \begin{array}{c}x_{t_0}(g - y_0) \\ \vdots \\ x_{t_N}(g - y_0) \end{array} \right), \;\;\; \pmb{\psi}_i = \left( \begin{array}{ccc} \psi_i(t_0) & \dots & 0 \\ 0 & \ddots & 0 \\ 0 & \dots & \psi_i(t_n) \end{array} \right)
-\end{equation*}
-
-This way the DMP can be made to imitate the desired path.
-However, this formulation of DMP suffers from critical issues when used in practical application, such as when the scaling term of $f$, $g-x_0$ if close to zero, a small change in $g$ may lead to huge acceleration and thus it may break the limits of robot.
-We used the improved version of DMP \cite{pastor2009learning} in this research.
+Optimization methods such as locally weighted regression \cite{vijayakumar2000locally} can be used, so that the forcing function matches the desired trajectory.
+This way DMP can be made to imitate the desired path \cite{pastor2009learning}.
 
 \section{Overview of the System}
-\label{system_overview}
+\label{sec:system_overview}
 Robotic cloth manipulation task contains a dual arm humanoid robot Baxter.
-The complete setup is shown in figure \ref{setup}.
+Setup of the system is shown in figure \ref{fig:setup}.
 We choose soft mannequin instead of a human for this preliminary experiment.
@@
 The mannequin is positioned in such a way, so that it resides within the limits of work space of the Baxter robot.
-Also both the arms of mannequin are facing towards robot.
-A kinect v2 sensor is mounted on the LCD display of Baxter root.
-Kinect sensor can see the mannequin and clothing article.
-Before starting the experiment, the clothing article is put in arms of the baxter robot manually.
+Both the arms of mannequin are facing towards robot.
+A Kinect V2 \cite{microsoft2014kinect} sensor is mounted on LCD display of Baxter root.
+Kinect sensor can see the mannequin and clothing article and provides depth information, which is necessary for mannequin tracking.
+The clothing article is put in arms of Baxter robot manually before starting the experiment.
 
 The Baxter robot is connected to a computer directly using Ethernet cable.
-It is controlled using Robot Operating System (ROS), one of the widely used tool by the researchers in robotics community.
+It is controlled using Robot Operating System (ROS) \cite{quigley2009ros}, one of the widely used tool by the researchers in robotics community.
 We used Baxter robot's API, which are available and supported by ROS to command the robot.
-The Kinect sensor is also controlled by Open source Kinect API for ROS.
+The Kinect sensor is controlled by Open source Kinect API for ROS \cite{iai_kinect2, libfreenect2}.
 
 \begin{figure*}
-	\includegraphics[width=\textwidth]{flowchart_conf}
+	\includegraphics[width=\linewidth]{flowchart_conf}
 	\caption{Work flow of Robotic cloth manipulation task.
@@
 Now, the modified DMP can accommodate new posture.}
-	\label{workflow}
+	\label{fig:workflow}
 \end{figure*}
@@
 \section{Experiments}
-\label{experiments}
-As per the formulation \ref{setup}, the DMP can learn by the demonstration.
-Hence we starts by performing a demonstration by holding the robot arm and move accordingly.
+\label{sec:experiments}
+As per the formulation described in section \ref{sec:dmp}, DMP can learn by the demonstration.
+Therefore we start by performing a demonstration by holding the robot arm and move accordingly.
 During the demonstration, pose of the end-effector is recorded.
@@
 In this way, we have totally six DMP trajectories, which can control both the arms of Baxter robot.
-We performed following two experiments by using these trajectory- (a) Clothing task using position DMP (b) Failure detection using end-effector forces.
+We performed following two experiments by using these trajectory: (a) Clothing task using position DMP (b) Failure detection using end-effector forces.
 
@@
 Now we change the goal of DMP trajectories by using this information.
-The modified DMP can be acquired as described in section \ref{dmp}.
+The modified DMP can be acquired as described in section \ref{sec:dmp}.
 
@@
 \section{Results}
-\label{results}
+\label{sec:results}
 A soft mannequin was used in order to perform the clothing task.
-A sleeveless tee shirt was used during the experiment and the task was to put the clothing article on both the arms as shown in figure \ref{various_posture}.
+A sleeveless T-shirt was used during the experiment and the task was to put the clothing article on both the arms as shown in figure \ref{fig:various_posture}.
 Following subsections explains the results of the two experiments described above.
@@
 \begin{figure}
-	\includegraphics[width=0.45\textwidth]{various_posture}
-	\caption{Various postures used in Clothing task}
-	\label{various_posture}
+	\includegraphics[width=\linewidth]{inclination}
+	\caption{Angle of Inclination}
+	\label{fig:inclination}
 \end{figure}
@@
 \begin{figure}
-	\includegraphics[width=0.45\textwidth]{trajectory}
+	\includegraphics[width=\linewidth]{trajectory}
 	\caption{Left arm trajectory of Baxter}
-	\label{trajectory}
+	\label{fig:trajectory}
 \end{figure}
@@
 In this experiment, the initialized DMP was modified to accommodate the new posture by changing the goal state of the DMP.
-The generated trajectory was then run on the Baxter robot as shown in figure \ref{trajectory}.
+The generated trajectory was then run on the Baxter robot as shown in figure \ref{fig:trajectory}.
 The newly generated DMP trajectory (shown in red color) was not only found well suited and capable of performing clothing task but also smooth compared to the original trajectory (shown in blue color).
@@
 During the experiment, we monitored the trajectory generated by DMP system.
-The accuracy measurement is shown in figure \ref{accuracy}.
+The accuracy measurement is shown in figure \ref{fig:accuracy}.
 
 \begin{figure}
-	\centering
-	\begin{subfigure}{.2\textwidth}
-		\includegraphics[width=\linewidth]{inclination}
-	\end{subfigure}%
-	\begin{subfigure}{.26\textwidth}
 	\includegraphics[width=\linewidth]{accuracy}
-	\end{subfigure}
 	\caption{Accuracy measurement}
-	\label{accuracy}
+	\label{fig:accuracy}
 \end{figure}
@@
 The trajectories were monitored and categorized into two \textit{success} and \textit{failure}.
-The mean of these two category is calculated and plotted as shown in figure \ref{position_force}.
+The mean of these two category is calculated and plotted as shown in figure \ref{fig:position_force}.
 
-It is clearly visible from the figure \ref{position_force} that the applied forces are very different in nature in both the cases.
+It is clearly visible from the figure \ref{fig:position_force} that the applied forces are very different in nature in both the cases.
 Both of these applied forces are increasing from the beginning however the applied forces in case of \textit{failure} are much more higher than that of \textit{success}.
@@
 \begin{figure}
-	\includegraphics[width=0.45\textwidth]{position_force}
+	\includegraphics[width=\linewidth]{position_force}
 	\caption{Failure detection using end-effector forces}
-	\label{position_force}
+	\label{fig:position_force}
 \end{figure}
@@
 \section{Conclusions}
-\label{conclusions}
+\label{sec:conclusions}
 This paper presents an approach for robotic cloth manipulation for clothing assistance task using Dynamic Movement Primitives.
-A dual arm Baxter robot, soft mannequin and very thin sleeveless tee shirt were used in the task.
-The authors have also presented an approach for failure detection using forces being applied on the end-effector of the robot.
-Authors have used the Baxter APIs in order to get the forces, which are calculated by Baxter Dynamics Module.
+A dual arm Baxter robot, soft mannequin and very thin sleeveless T-shirt were used in the task.
+We have also presented an approach for failure detection using forces being applied on the end-effector of the robot.
+We have used the Baxter APIs in order to get the forces, which are calculated by Baxter Dynamics Module.
 Though raw forces were very noisy in nature, but after applying median filter most of the noise was eliminated properly.

### 2017-01-29 paper/images/flowchart/flowchart_conf.tex
[major] add 1st draft
[major] add v2

@@
 
-\begin{tikzpicture}[every node/.style={transform shape}, thick, >=latex, node distance=1cm]
+\begin{tikzpicture}[every node/.style={transform shape}, thick, >=latex, node distance=0.5cm]
 	\node[basic box = blue, header = Teaching Phase] (teaching) {
-		\includegraphics[width=\scaling]{teaching}%\\
+		\includegraphics[height=\scaling]{teaching}%\\
 		%A demonstration is performed by moving the \\
@@
 		%Baxter Left Arm Trajectory\\
-		\includegraphics[width=\scaling]{dmp}%\\
+		\includegraphics[height=\scaling]{dmp_init}%\\
 		%Recorded trajectory is parameterized by DMP
@@
 
-	\node[east below = of teaching, basic box = green, header = Testing Phase] (testing) {
+	\node[north right = of dmp, basic box = green, header = Testing Phase] (testing) {
 		%Modified Posture\\
-		\includegraphics[width=\scaling]{testing}%\\
+		\includegraphics[height=\scaling]{testing}%\\
 		%DMP can accomodate new posture
@@
 		%DMP Trajectory\\
-		\includegraphics[width=\scaling]{dmp_new}
+		\includegraphics[height=\scaling]{dmp_mod}
 	};
@@
 	\path[ultra thick, blue,  ->](teaching) edge[->] (dmp);
-	\path[ultra thick, orange, ->](dmp) edge[->] (testing);
+	\path[ultra thick, orange,->](dmp) edge[->] (testing);
 	\path[ultra thick, green, ->](testing) edge[->] (generalization);

### 2017-01-29 paper/images/inclination/inclination.tex
[major] add v2

@@
 \documentclass{standalone}
-%\usepackage{siunitx}
 \usepackage{graphicx}
@@
 
-\newcommand{\BoxWidth}{1.8cm}%
+\newcommand*{\BoxWidth}{4cm}%
 \tikzset{
-    point/.style     = {coordinate},
-    arrow/.style     = {thick, ->, >=stealth'},
-    to/.style        = {->,>=stealth', shorten >=1pt, semithick, font=\footnotesize, draw=green},
+    to/.style     = {->},
     line/.style   = {line width=0.4mm, draw=blue},
-    darrow/.style     = { <->, line width=0.4mm, draw=blue},
-    decision/.style  = {draw, diamond, minimum width=\BoxWidth, minimum height=1cm, text centered, aspect=2, font=\footnotesize},
-    process/.style   = {draw, rectangle, minimum width=\BoxWidth, minimum height=1cm, text centered, text width=\BoxWidth, font=\footnotesize},
-    startstop/.style = {draw, rectangle, rounded corners, minimum width=\BoxWidth, minimum height=1cm,text centered, text width=\BoxWidth, font=\footnotesize},
-    box/.style       = {draw, rectangle, minimum height = 1cm, minimum width = \BoxWidth, text centered, text width=\BoxWidth, ultra thin, draw=orange, fill=orange!30, font=\footnotesize},
-    smallBox/.style       = {draw, rectangle, minimum height = 0.5cm, minimum width = 0.5cm, text centered, ultra thin, draw=black, fill=green!30, font=\small}
+    darrow/.style = {<->, line width=0.4mm, draw=blue},
+    box/.style    = {draw, rectangle, minimum height = 1cm, minimum width = \BoxWidth, text centered, text width=\BoxWidth, ultra thin, draw=black, fill=blue!10, font=\large}
 }
@@
 			\draw[line] (0.20,0.25) -- (\ex,\ey);
-			\draw[darrow](\ex,\ey) ++(-152:.2) arc (-152:-180:.2) node[xshift=-3cm, yshift=0.5cm, color=blue, font=\large] {Angle of inclination ($\alpha$)} ;
+			\draw[darrow](\ex,\ey) ++(-152:.2) arc (-152:-180:.2);
+			\draw[to](0.40,0.65) node[box]{Angle of inclination} to [out=-90,in=200] (0.65,0.55);
 		\end{scope}

### 2017-01-29 paper/paper.tex
[major] add v2

@@
 \affiliation{%
-	\institution{Institute for Clarity in Documentation}
-	\streetaddress{P.O. Box 1212}
-	\city{Dublin}
-	\state{Ohio}
-	\postcode{43017-6221}
+	\institution{Kyushu Institute of Technology}
+	\city{Kitakyushu}
+	\state{Fukuoka}
+	\country{Japan}
 }
@@
 \affiliation{%
-	\institution{Institute for Clarity in Documentation}
-	\streetaddress{P.O. Box 1212}
-	\city{Dublin}
-	\state{Ohio}
-	\postcode{43017-6221}
+	\institution{Nara Institute of Science and Technology}
+	\city{Ikoma}
+	\state{Nara}
+	\country{Japan}
 }
@@
 \author{Tomohiro Shibata}
-\authornote{This author is the
-one who did all the really hard work.}
+\authornote{This author is the one who did all the really hard work.}
 \affiliation{%
-	\institution{The Th{\o}rv{\"a}ld Group}
-	\streetaddress{1 Th{\o}rv{\"a}ld Circle}
-	\city{Hekla}
-	\country{Iceland}}
+	\institution{Kyushu Institute of Technology}
+	\city{Kitakyushu}
+	\state{Fukuoka}
+	\country{Japan}
+}
 \email{tom@brain.kyutech.ac.jp}
@@
 
-\keywords{Robotic Clothing Assistance, Dynamic Movement Primitives (DMP), Human-Robot Interaction, Learning and Adaptive Systems}
+\keywords{Robotic Clothing Assistance, Dynamic Movement Primitives (DMP), Human-Robot Interaction, Learning and Adaptive Systems, Learning from Demonstration}
 
@@
 In Section \ref{sec:system_overview}, we describe our system and various components used in the experiments.
-Section \ref{sec:experiments} deals with the details about experiments performed.
-Section \ref{sec:results} shows the experimental results.
+Section \ref{sec:experiments} deals with the details about experiments performed and their results.
 Finally we conclude in Section \ref{sec:conclusions} with some future directions.
@@
 In this section, we provide brief overview of the related literature in this field.
-There has been significant number of research done in the field of Robotic Clothing Assistance.
+There has been significant number of research done in the field of Robotic Clothing Assistance by using vision system.
+Klee et al.
+\cite{klee2015personalized} worked on personalized assistance for dressing a user, where they used vision module to monitor the human's motion.
+The robot request to user to move towards robot, monitors motion and puts hat on the user once users is rechable by the robot.
+Yamazaki et al.
+\cite{yamazaki2013method, yamazaki2014bottom}  worked on bottom dressing by a life-sized humanoid robot, where they recognize the cloth state by using  optical flow on the images acquired from single camera.
+They showed that the robot can pull a bottom clothing item along the subject's legs.
+Yamakawa et al.
+\cite{yamakawa2011dynamic} proposed a new strategy for dynamic manipulation of sheet-like flexible objects by a high-speed robot system.
+The system consists of two high-speed multi-fingered hands mounted on two sliders and a high-speed vision system.
+The proposed system learns the necessary motor skills from the demonstration performed by a human subject.
+They validated the robot trajectory obtained from the motion planning method was with simulation results.
+
+The robotic cloth handling is challending.
+Unlike rigid object manipulation using robots, which has mainly relied on precise robot control, the deformable objects rather require complex control scheme.
+Many researchers have used vision informtion with combination of techniques such as motor skills learning using Reinforcement Learning.
 Colom{\'e} et al.
@@
 Their focus was to classify force data for haptic perception with high accuracy.
-Klee et al.
-\cite{klee2015personalized} worked on personalized assistance for dressing a user, where they used vision module to monitor the human's motion.
-The robot request to user to move towards robot, monitors motion and puts hat on the user once users is rechable by the robot.
 Koganti et al.
@@
 They proposed Reinforcement Learning framework and demonstrated that the robot quickly learns a suitable arm motion for putting T-shirt into the mannequin's head.
-Yamazaki et al.
-\cite{yamazaki2013method, yamazaki2014bottom}  worked on bottom dressing by a life-sized humanoid robot, where they recognize the cloth state by using  optical flow on the images acquired from single camera.
-They showed that the robot can pull a bottom clothing item along the subject's legs.
-
-Another related filed of research is motor-skills learning for Cloth Handling, in which Yamakawa et al.
-\cite{yamakawa2011dynamic} proposed a new strategy for dynamic manipulation of sheet-like flexible objects by a high-speed robot system.
-The system consists of two high-speed multi-fingered hands mounted on two sliders and a high-speed vision system.
-The proposed system learns the necessary motor skills from the demonstration performed by a human subject.
-They validated the robot trajectory obtained from the motion planning method was with simulation results.
 Another exciting work done by Mons{\'o} et al.
@@
 Their approach relaxes the precision requirements of robot vision and manipulation.
+
+The problem of robotic clothing assistance not only depends on tracking the cloth dynamics but also the motor skills required to perform the task.
+A combination of such techniques are encouraged.
+However we see that there has been a lot of gap when compared it to the practical use cases in elderly care.
+The most important point should be the learning rate of the task.
+We believe that \textit{Learning from Demonstration} framework are quick to learn in cases which involve complex task specific dynamics.
+The problem of putting sleeveless T-shirt into the arms of mannequin is close to the practical use case.
+Therefore, we are putting our efforts to solve it.
 
@@
 \end{figure}
+
+\begin{figure*}
+	\includegraphics[width=\linewidth]{flowchart_conf}
+	\caption{Work flow of Robotic cloth manipulation task.
+Initially a demonstration is performed by moving the Baxter arms in the appropriate trajectory.
+The demonstration is recorded and parameterized by DMP.
+Later posture of the mannequin is changed and accordingly the goal posture of DMP is modified.
+Now, the modified DMP can accommodate new posture.}
+	\label{fig:workflow}
+\end{figure*}
 
@@
 \label{sec:system_overview}
+As per the formulation described in section \ref{sec:dmp}, DMP can learn from demonstration.
+Therefore we start by performing a demonstration by holding the robot arm as shown in figure \ref{fig:workflow}.
+This is referred as ``Teaching Phase'', since in this phase, we are teaching skills to robot to perform the task.
+During the demonstration, pose trajectory of the end-effector is recorded using Baxter API and stored in a file.
+The term pose collectively refers to position and orientation.
+Once the demonstration is finished, DMP is initialized using the recorded trajectory file.
+This is termed as ``Learn Trajectory'' phase.
+In this phase, recorded trajectory is parameterized by DMP system.
+The parameterized DMP can represents all the characteristics of original trajectory.
+Here, three DMP systems, one for each coordinate axis i.e., $x$, $y$ and $z$ are initialized for one arm.
+In this way, we have total six DMP systems, which can control both the arms of Baxter robot.
+In ``Testing Phase'', we change the posture of mannequin by lifting the arms up or down.
+At this point, we use Kinect Sensor to get the 3D coordinates of the arm.
+We change the goal of DMP trajectories by using this information.
+In this way, we have generalised DMP system, which can adapt modified posture referred as ``DMP Generalization''.
+
+\begin{figure}
+	\includegraphics[width=\linewidth]{all_traj}
+	\caption{Left arm trajectory of Baxter}
+	\label{fig:trajectory}
+\end{figure}
+
+\section{Experiments}
+\label{sec:experiments}
 Robotic cloth manipulation task contains a dual arm humanoid robot Baxter.
@@
 The Kinect sensor is controlled by Open source Kinect API for ROS \cite{iai_kinect2, libfreenect2}.
+We performed following two experiments to validate our approach: (a) Clothing task using position DMP (b) Failure detection using end-effector forces.
 
-\begin{figure*}
-	\includegraphics[width=\linewidth]{flowchart_conf}
-	\caption{Work flow of Robotic cloth manipulation task.
-Initially a demonstration is performed by moving the Baxter arms in the appropriate trajectory.
-The demonstration is recorded and parameterized by DMP.
-Later posture of the mannequin is changed and accordingly the goal posture of DMP is modified.
-Now, the modified DMP can accommodate new posture.}
-	\label{fig:workflow}
-\end{figure*}
-
-\section{Experiments}
-\label{sec:experiments}
-As per the formulation described in section \ref{sec:dmp}, DMP can learn by the demonstration.
-Therefore we start by performing a demonstration by holding the robot arm and move accordingly.
-During the demonstration, pose of the end-effector is recorded.
-The term pose collectively refers to position and orientation.
-Once the demonstration is finished, DMP is initialized using the recorded trajectory.
-Three DMP trajectories one for each coordinate axis are initialized for one arm.
-In this way, we have totally six DMP trajectories, which can control both the arms of Baxter robot.
-We performed following two experiments by using these trajectory: (a) Clothing task using position DMP (b) Failure detection using end-effector forces.
+\begin{figure}
+	\includegraphics[width=0.7\linewidth]{inclination}
+	\caption{Angle of Inclination}
+	\label{fig:inclination}
+\end{figure}
 
@@
 
-\subsection{Failure detection using end-effector forces}
-This experiment is designed to deal with failure cases.
-There can be many failure cases during the clothing task, such as the clothing article gets stuck into the fingers.
-In this experiment, we are using forces being applied on the end-effector of Baxter robot to detect the failure scenario.
-Appropriate action can be taken once the failure is detected.
-
-\section{Results}
-\label{sec:results}
-A soft mannequin was used in order to perform the clothing task.
-A sleeveless T-shirt was used during the experiment and the task was to put the clothing article on both the arms as shown in figure \ref{fig:various_posture}.
-Following subsections explains the results of the two experiments described above.
-
-\begin{figure}
-	\includegraphics[width=\linewidth]{inclination}
-	\caption{Angle of Inclination}
-	\label{fig:inclination}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[width=\linewidth]{trajectory}
-	\caption{Left arm trajectory of Baxter}
-	\label{fig:trajectory}
-\end{figure}
-
-\subsection{Clothing task using position DMP}
 In this experiment, the initialized DMP was modified to accommodate the new posture by changing the goal state of the DMP.
@@
 
-To eventuate this experiment, we performed it many times for various postures by keeping the arms at different-different height.
+To eventuate this experiment, we performed it many times for various angle of inclination by keeping the arms at different-different height as shown in figure \ref{fig:inclination}.
 During the experiment, we monitored the trajectory generated by DMP system.
@@
 \subsection{Failure detection using end-effector forces}
+This experiment is designed to deal with failure cases.
+There can be many failure cases during the clothing task, such as the clothing article gets stuck into the fingers.
+In this experiment, we are using forces being applied on the end-effector of Baxter robot to detect the failure scenario.
+Appropriate action can be taken once the failure is detected.
+
 The clothing task has to deal with complex dynamics including manipulation of clothing article.
@@
 The mean of these two category is calculated and plotted as shown in figure \ref{fig:position_force}.
+This is the average profile over several success and failure trajectories for different postures of the mannequin.
 
 It is clearly visible from the figure \ref{fig:position_force} that the applied forces are very different in nature in both the cases.
-Both of these applied forces are increasing from the beginning however the applied forces in case of \textit{failure} are much more higher than that of \textit{success}.
+Both of these forces are increasing from the beginning however forces in case of \textit{failure} are much more higher than that of \textit{success}.
 Hence one can easily differentiate and detect the failure by using this information.

### 2017-01-29 paper/images/trajectories/all_traj.py

@@ -1,0 +1,41 @@
+# -*- coding: utf-8 -*-
+import numpy as np
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+
+# define index for plotting
+time=0
+poselinear_left_x=1;   poselinear_left_y=2;  poselinear_left_z=3
+poselinear_right_x=8; poselinear_right_y=9; poselinear_right_z=10
+
+# load csv tarjectories
+org_tra = np.loadtxt('org_traj.csv', delimiter=',', skiprows=1)
+org_dmp = np.loadtxt('org_dmp.csv', delimiter=',', skiprows=1)
+mod_dmp = np.loadtxt('mod_dmp.csv', delimiter=',', skiprows=1)
+
+org_tra = org_tra[:, range(15)]
+org_dmp = org_dmp[:, range(15)]
+mod_dmp = mod_dmp[:, range(15)]
+
+#mpl.rcParams['legend.fontsize'] = 10
+
+fig = plt.figure()
+ax = fig.gca(projection='3d')
+ax.plot( org_tra[:, poselinear_left_x], 
+         org_tra[:, poselinear_left_y], 
+         org_tra[:, poselinear_left_z], label='Original', c='b', lw=1)
+ax.plot( org_dmp[:, poselinear_left_x], 
+         org_dmp[:, poselinear_left_y], 
+         org_dmp[:, poselinear_left_z], label='DMP', c='g')
+ax.plot( mod_dmp[:, poselinear_left_x], 
+         mod_dmp[:, poselinear_left_y], 
+         mod_dmp[:, poselinear_left_z], label='Modified DMP', c='r')
+
+#ax.set_title('Left Arm Trajectory', y=1.1)
+ax.set_xlabel('x $(m)$')
+ax.set_ylabel('y $(m)$')
+ax.set_zlabel('z $(m)$')
+ax.legend(loc='upper right')
+plt.savefig("all_traj.pdf", bbox_inches='tight')
+plt.show()

### 2017-01-29 paper/images/trajectories/dmp_init.py

@@ -1,0 +1,41 @@
+# -*- coding: utf-8 -*-
+import numpy as np
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+
+# define index for plotting
+time=0
+poselinear_left_x=1;   poselinear_left_y=2;  poselinear_left_z=3
+poselinear_right_x=8; poselinear_right_y=9; poselinear_right_z=10
+
+# load csv tarjectories
+org_tra = np.loadtxt('org_traj.csv', delimiter=',', skiprows=1)
+org_dmp = np.loadtxt('org_dmp.csv', delimiter=',', skiprows=1)
+mod_dmp = np.loadtxt('mod_dmp.csv', delimiter=',', skiprows=1)
+
+org_tra = org_tra[:, range(15)]
+org_dmp = org_dmp[:, range(15)]
+mod_dmp = mod_dmp[:, range(15)]
+
+#mpl.rcParams['legend.fontsize'] = 10
+
+fig = plt.figure()
+ax = fig.gca(projection='3d')
+ax.plot( org_tra[:, poselinear_left_x], 
+         org_tra[:, poselinear_left_y], 
+         org_tra[:, poselinear_left_z], label='Original', c='b', lw=1)
+ax.plot( org_dmp[:, poselinear_left_x], 
+         org_dmp[:, poselinear_left_y], 
+         org_dmp[:, poselinear_left_z], label='DMP', c='g')
+#ax.plot( mod_dmp[:, poselinear_left_x], 
+#         mod_dmp[:, poselinear_left_y], 
+#         mod_dmp[:, poselinear_left_z], label='New DMP', c='r')
+
+#ax.set_title('Left Arm Trajectory', y=1.1)
+ax.set_xlabel('x $(m)$')
+ax.set_ylabel('y $(m)$')
+ax.set_zlabel('z $(m)$')
+ax.legend(loc='upper right')
+plt.savefig("dmp_init.pdf", bbox_inches='tight')
+plt.show()

### 2017-01-29 paper/images/trajectories/dmp_mod.py

@@ -1,0 +1,41 @@
+# -*- coding: utf-8 -*-
+import numpy as np
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+
+# define index for plotting
+time=0
+poselinear_left_x=1;   poselinear_left_y=2;  poselinear_left_z=3
+poselinear_right_x=8; poselinear_right_y=9; poselinear_right_z=10
+
+# load csv tarjectories
+org_tra = np.loadtxt('org_traj.csv', delimiter=',', skiprows=1)
+org_dmp = np.loadtxt('org_dmp.csv', delimiter=',', skiprows=1)
+mod_dmp = np.loadtxt('mod_dmp.csv', delimiter=',', skiprows=1)
+
+org_tra = org_tra[:, range(15)]
+org_dmp = org_dmp[:, range(15)]
+mod_dmp = mod_dmp[:, range(15)]
+
+#mpl.rcParams['legend.fontsize'] = 10
+
+fig = plt.figure()
+ax = fig.gca(projection='3d')
+#ax.plot( org_tra[:, poselinear_left_x], 
+#         org_tra[:, poselinear_left_y], 
+#         org_tra[:, poselinear_left_z], label='Original', c='b', lw=1)
+ax.plot( org_dmp[:, poselinear_left_x], 
+         org_dmp[:, poselinear_left_y], 
+         org_dmp[:, poselinear_left_z], label='DMP', c='g')
+ax.plot( mod_dmp[:, poselinear_left_x], 
+         mod_dmp[:, poselinear_left_y], 
+         mod_dmp[:, poselinear_left_z], label='Modified DMP', c='r')
+
+#ax.set_title('Left Arm Trajectory', y=1.1)
+ax.set_xlabel('x $(m)$')
+ax.set_ylabel('y $(m)$')
+ax.set_zlabel('z $(m)$')
+ax.legend(loc='upper right')
+plt.savefig("dmp_mod.pdf", bbox_inches='tight')
+plt.show()

### 2017-01-29 paper/images/improved_DMP/cs.py
[minor] add scripts for generating plots of DMP

@@ -1,0 +1,92 @@
+'''
+Copyright (C) 2013 Travis DeWolf
+
+This program is free software: you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation, either version 3 of the License, or
+(at your option) any later version.
+
+This program is distributed in the hope that it will be useful,
+but WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+GNU General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program.  If not, see <http://www.gnu.org/licenses/>.
+'''
+
+import numpy as np
+
+class CanonicalSystem(object):
+    """
+    Implementation of the canonical dynamical system as described in 
+    Dr. Stefan Schaal's (2002) paper"""
+
+    def __init__(self, dt, pattern='discrete'):
+        """
+        Default values from Schaal (2012)
+        
+        dt float: the timestep
+        pattern string: either 'discrete' or 'rhythmic'
+        """
+        self.ax = 1.0
+
+        self.pattern = pattern
+        if pattern == 'discrete':
+            self.step = self.step_discrete
+            self.run_time = 1.0 
+        elif pattern == 'rhythmic':
+            self.step = self.step_rhythmic
+            self.run_time = 2*np.pi
+        else:
+            raise Exception('Invalid pattern type specified: \
+                Please specify rhythmic or discrete.')
+
+        self.dt = dt
+        self.timesteps = int(self.run_time / self.dt)
+
+        self.reset_state()
+
+    def rollout(self, **kwargs):
+        """Generate x for open loop movements.
+        """
+        if kwargs.has_key('tau'):
+            timesteps = int(self.timesteps / kwargs['tau'])
+        else: 
+            timesteps = self.timesteps
+        self.x_track = np.zeros(timesteps)
+        
+        self.reset_state()
+        for t in range(timesteps):
+            self.x_track[t] = self.x 
+            self.step(**kwargs)
+
+        return self.x_track
+
+    def reset_state(self):
+        """Reset the system state"""
+        self.x = 1.0
+        
+    def step_discrete(self, tau=1.0, error_coupling=1.0):
+        """Generate a single step of x for discrete
+        (potentially closed) loop movements. 
+        Decaying from 1 to 0 according to dx = -ax*x.
+        
+        tau float: gain on execution time
[…]

### 2017-01-29 paper/images/improved_DMP/dmp.py

@@ -1,0 +1,351 @@
+#src: https://github.com/dgerod/more-dmps
+import numpy as np
+from cs import CanonicalSystem
+
+class TdwFormulation(object):
+
+    def __init__(self, ay=None, by=None):
+        # Parameters as defined in Schaal 2012
+        if ay is None: ay = 25.
+        self.ay = ay
+        if by is None: by = ay/4.
+        self.by = by
+
+    def acceleration(self, x, dx, start, goal, tau, f, s):
+        return (self.ay *  (self.by * (goal-x) - dx/tau) + (goal-start)*f) * tau
+
+    def fs(self, x, dx, ddx, start, goal, tau, s):
+        return (ddx - self.ay * (self.by * (goal-x) - dx) / (goal-start))
+
+class OriginalFormulation(object):
+
+    def __init__(self, K=100., D=None):
+        self.K = K
+        if D is None:
+            D = 2.0 * np.sqrt(self.K)
+        self.D = D
+
+    def acceleration(self, x, dx, start, goal, tau, f, s):
+        return (self.K*(goal-x) - self.D*dx + (goal-start)*f) / tau
+
+    def fs(self, x, dx, ddx, start, goal, tau, s):
+        return (tau*ddx - self.K*(goal-x) + self.D*dx) / (goal-start)
+
+class ImprovedFormulation(object):
+
+    def __init__(self, K=100., D=None):
+        self.K = K
+        if D is None:
+            D = 2.0 * np.sqrt(self.K)
+        self.D = D
+
+    def acceleration(self, x, dx, start, goal, tau, f, s):
+        return (self.K*(goal-x) - self.D*dx - self.K*(goal-start)*s + self.K*f) / tau
+
+    def fs(self, x, dx, ddx, start, goal, tau, s):
+        return ((tau**2*ddx + self.D*dx*tau) / self.K) - (goal-x) + (goal-start)*s
+
+# -----------------------------------------------------------------------------
+
+class DMPs_discrete(object):
+
+    def __init__(self, dims, bfs, ts=None, dt=.01,
+                 y0=0, goal=1, w=None,
+                 ay=None, by=None, **kwargs):
+        '''
+        dims int: number of dynamic motor primitives
+        bfs int: number of basis functions per DMP
+        dt float: timestep for simulation
+        y0 list: initial state of DMPs
+        goal list: goal state of DMPs
+        w list: tunable parameters, control amplitude of basis functions
[…]

### 2017-01-29 paper/images/improved_DMP/example.py

@@ -1,0 +1,30 @@
+import numpy as np
+import matplotlib.pylab as plt
+from dmp import DMPs_discrete, ImprovedFormulation
+
+x = np.linspace(0, np.pi/2, 200)
+pose = np.sin(x)
+
+goal = np.array([1.5])
+dt = 1.0/pose.shape[0]
+nbfs = 100
+
+improvedDmp = DMPs_discrete(dims=1, bfs=nbfs, ts=ImprovedFormulation(),dt=dt)
+improvedDmp.learn(y_des=pose.T)
+improvedDmp.set_goal_state(goal)
+
+improvedDmp_y, improvedDmp_dy, improvedDmp_ddy = improvedDmp.plan()
+
+plt.figure(1)
+plt.plot(pose, label='Actual')
+plt.plot(improvedDmp_y, label='DMP')
+plt.legend(loc='upper right')
+plt.title('Trajectories')
+plt.figure(2)
+plt.plot(improvedDmp.w.T)
+plt.title('DMP Weights')
+plt.figure(3)
+plt.plot(improvedDmp.f_desired)
+plt.title('Desired Force')
+
+plt.show()

### 2017-01-29 paper/images/improved_DMP/temp.py

@@ -1,0 +1,52 @@
+import numpy as np
+import matplotlib.pylab as plt
+from dmp import DMPs_discrete, ImprovedFormulation
+
+x = np.linspace(0, 2*np.pi, 500)
+pose = np.sin(x)
+
+goal = np.array([0.5])
+dt = 1.0/pose.shape[0]
+nbfs = 100
+
+num_bfs = [10, 20, 50, 100, 500]
+
+for ii, nbfs in enumerate(num_bfs):
+    improvedDmp = DMPs_discrete(dims=1, bfs=nbfs, ts=ImprovedFormulation(),dt=dt)
+    improvedDmp.learn(y_des=pose.T)
+    improvedDmp.set_goal_state(goal)
+
+    improvedDmp_y, improvedDmp_dy, improvedDmp_ddy = improvedDmp.plan()
+
+    plt.figure(1)
+    plt.plot(improvedDmp_y)
+
+    plt.figure(2)
+    plt.plot(improvedDmp.w.T)
+
+
+plt.figure(1)
+plt.plot(pose,lw=2)
+plt.legend(['%i BFs' % i for i in num_bfs], loc='lower right')
+plt.title('Actual Trajectory Vs DMP')
+
+plt.figure(2)
+plt.legend(['%i BFs' % i for i in num_bfs], loc='lower right')
+plt.title('DMP Weights')
+
+'''
+plt.figure(3)
+plt.plot(improvedDmp.f_desired, label='desired')
+plt.plot(improvedDmp.f_predicted, label='predicted')
+plt.legend(loc='upper right')
+plt.title('Desired Force')
+
+plt.figure(4)
+plt.plot(improvedDmp_dy, label='vel')
+plt.legend(loc='upper right')
+
+plt.figure(5)
+plt.plot(improvedDmp_ddy, label='acc')
+plt.legend(loc='upper right')
+'''
+plt.show()

### 2017-01-30 paper/paper.tex
[major] add more comments from Nishanth

@@
 Primitives}
-\titlenote{Produces the permission block, and copyright information}
+%\titlenote{Produces the permission block, and copyright information}
 %\subtitle{Extended Abstract}
@@
 \author{Ravi P. Joshi}
-\authornote{Dr.~Trovato insisted his name be first.}
-\orcid{1234-5678-9012}
+\authornote{Ravi P. Joshi is with Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Fukuoka, Japan}
 \affiliation{%
-	\institution{Kyushu Institute of Technology}
-	\city{Kitakyushu}
-	\state{Fukuoka}
-	\country{Japan}
+%	\institution{Kyushu Institute of Technology}
+%	\city{Kitakyushu}
+%	\state{Fukuoka}
+%	\country{Japan}
 }
@@
 \author{Nishanth Koganti}
-\authornote{The secretary disavows any knowledge of this author's actions.}
+\authornote{Nishanth Koganti is with Graduate School of Information Science, Nara Institute of Science and Technology, Nara, Japan and Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Fukuoka, Japan}
 \affiliation{%
-	\institution{Nara Institute of Science and Technology}
-	\city{Ikoma}
-	\state{Nara}
-	\country{Japan}
+%	\institution{Nara Institute of Science and Technology}
+%	\city{Ikoma}
+%	\state{Nara}
+%	\country{Japan}
 }
@@
 \author{Tomohiro Shibata}
-\authornote{This author is the one who did all the really hard work.}
+\authornote{Tomohiro Shibata is with Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Fukuoka, Japan}
 \affiliation{%
-	\institution{Kyushu Institute of Technology}
-	\city{Kitakyushu}
-	\state{Fukuoka}
-	\country{Japan}
+%	\institution{Kyushu Institute of Technology}
+%	\city{Kitakyushu}
+%	\state{Fukuoka}
+%	\country{Japan}
 }
@@
 \begin{abstract}
-	The need of robotic clothing assistance in the field of assistive robotics is growing, as it is one of the most basic activities in daily life of elderly and disabled people.
+	The need of robotic clothing assistance in the field of assistive robotics is growing, as it is one of the most basic activities in the daily life of elderly and disabled people.
 In this study, we are investigating the applicability of using Dynamic Movement Primitives (DMP) as a task parameterization model for performing clothing assistance tasks.
@@
 \label{sec:introduction}
-Due to the demographic trend in developed countries, the robotic assistance in the field of elderly care in home environment is growing \cite{broekens2009assistive}.
+Due to the demographic trend in developed countries, the robotic assistance in the field of elderly care in the home environment is growing \cite{broekens2009assistive}.
 Although there has been a significant number of research done in this field, the robotic clothing assistance is yet an open field for research.
-Not to mention that, it is one of the basic and important assistance activities in daily life of elderly as well as disabled people.
+Not to mention that it is one of the basic and important assistance activities in the daily life of elderly as well as disabled people.
 While rigid object manipulation with robots has mainly relied on precise robot control, the deformable objects rather require complex control scheme.
-The clothing assistance is a challenging problem since robot is required to manage two difficulties: (a) robot must do cooperative manipulation by holding the cloth using both the arms while interacting with non-rigid and highly deformable clothes and (b) maintain safe human-robot interaction with the assisted person whose posture can vary during the assistance.
+The clothing assistance is a challenging problem since the robot is required to manage two difficulties: (a) the robot must do cooperative manipulation by holding the cloth using both the arms while interacting with non-rigid and highly deformable clothes and (b) maintain safe human-robot interaction with the assisted person whose posture can vary during the assistance.
 
@@
 The robotic cloth manipulation task deals with putting the cloth on both the arms.
-The idea of using DMP is inspired from the fact that DMP can learn complex task from the demonstration \cite{ijspeert2003learning, schaal2006dynamic, ijspeert2013dynamical} and thus reduce the manual efforts to design the controller from scratch or to fine-tune the controller parameters.
+The idea of using DMP is inspired by the fact that DMP can learn complex task from the demonstration \cite{ijspeert2003learning, schaal2006dynamic, ijspeert2013dynamical} and thus reduce the manual efforts to design the controller from scratch or to fine-tune the controller parameters.
 We choose the dual arm Baxter robot in this research as it is safe and flexible by design \cite{fitzgerald2013developing}.
@@
 The rest of the paper is organized as follows.
-Section \ref{sec:related_works}, gives a brief overview about the related literature in this field.
+Section \ref{sec:related_works}, gives a brief overview of the related literature in this field.
 Section \ref{sec:dmp} introduces the mathematical formulation about Dynamic Movement Primitives.
 In Section \ref{sec:system_overview}, we describe our system and various components used in the experiments.
-Section \ref{sec:experiments} deals with the details about experiments performed and their results.
+Section \ref{sec:experiments} deals with the details of experiments performed and their results.
 Finally we conclude in Section \ref{sec:conclusions} with some future directions.
@@
 \label{sec:related_works}
-In this section, we provide brief overview of the related literature in this field.
-There has been significant number of research done in the field of Robotic Clothing Assistance by using vision system.
+There has been a significant number of research done in the field of Robotic Clothing Assistance by using vision system.
 Klee et al.
 \cite{klee2015personalized} worked on personalized assistance for dressing a user, where they used vision module to monitor the human's motion.
-The robot request to user to move towards robot, monitors motion and puts hat on the user once users is rechable by the robot.
+The robot request to a user to move towards the robot, monitors motion and puts a hat on the user once users is reachable by the robot.
+They haven't considered human and cloth interaction.
 Yamazaki et al.
-\cite{yamazaki2013method, yamazaki2014bottom}  worked on bottom dressing by a life-sized humanoid robot, where they recognize the cloth state by using  optical flow on the images acquired from single camera.
+\cite{yamazaki2013method, yamazaki2014bottom}  worked on bottom dressing by a life-sized humanoid robot, where they recognize the cloth state by using optical flow on the images acquired from a single camera.
 They showed that the robot can pull a bottom clothing item along the subject's legs.
+They did not handle large occlusions.
 Yamakawa et al.
@@
 They validated the robot trajectory obtained from the motion planning method was with simulation results.
+They worked on fast cloth state tracking but it is not related to robotic clothing assistance.
 
-The robotic cloth handling is challending.
+The robotic cloth handling is challenging.
 Unlike rigid object manipulation using robots, which has mainly relied on precise robot control, the deformable objects rather require complex control scheme.
-Many researchers have used vision informtion with combination of techniques such as motor skills learning using Reinforcement Learning.
+Many researchers have used vision information with the combination of techniques such as motor skills learning using Reinforcement Learning.
 Colom{\'e} et al.
@@
 Gao et al.
-\cite{gao2015user, gao2016iterative} has focused on user upper-body modeling for personalized dressing by using top-view depth camera.
-Randomised decision forests was used to estimate user pose and proposed an online iterative path optimisation method to enable Baxter humanoid robot to assist human to wear a sleeveless jacket.
+\cite{gao2015user, gao2016iterative} have focused on user upper-body modeling for personalized dressing by using top-view depth camera.
+Randomized decision forests were used to estimate user pose and proposed an online iterative path optimization method to enable Baxter humanoid robot to assist human in wearing a sleeveless jacket.
 Another interesting work by Kapusta et al.
 \cite{kapusta2016data} is focused towards designing a controller inspired from data-driven haptic perception.
-They classified the forces measured at robot's end effector by using hidden Markov models and performed the clothing task on hospital gown.
+They classified the forces measured at robot's end effector by using hidden Markov models and performed the clothing task on the hospital gown.
 Their focus was to classify force data for haptic perception with high accuracy.
@@
 They proposed Reinforcement Learning framework and demonstrated that the robot quickly learns a suitable arm motion for putting T-shirt into the mannequin's head.
-Another exciting work done by Mons{\'o} et al.
+Another exciting work was done by Mons{\'o} et al.
 \cite{monso2012pomdp}, where they proposed a probabilistic planner, based on Partially Observable Markov Decision Process (POMDP) approach, for reducing the inherent uncertainty of cloth sorting (isolation/extraction) task.
@@
 The problem of robotic clothing assistance not only depends on tracking the cloth dynamics but also the motor skills required to perform the task.
-A combination of such techniques are encouraged.
-However we see that there has been a lot of gap when compared it to the practical use cases in elderly care.
+A combination of such techniques is encouraged.
+However, we see that there has been a large gap when compared it to the practical use cases in elderly care.
 The most important point should be the learning rate of the task.
 We believe that \textit{Learning from Demonstration} framework are quick to learn in cases which involve complex task specific dynamics.
-The problem of putting sleeveless T-shirt into the arms of mannequin is close to the practical use case.
+The problem of putting sleeveless T-shirt into the arms of the mannequin is close to the practical use case.
 Therefore, we are putting our efforts to solve it.
@@
 \begin{figure}
-	\includegraphics[width=\linewidth]{psi}
-	\caption{$\psi$ activations and weighted summation of Gaussians}
+	\includegraphics[width=\linewidth]{gaussian_kernels}
+	\includegraphics[width=\linewidth]{weighted_summation}
+	\caption{$\psi(s)$ activations and weighted summation of Gaussians}
 	\label{fig:psi_activations}
@@
 	\includegraphics[width=\linewidth]{flowchart_conf}
-	\caption{Work flow of Robotic cloth manipulation task.
-Initially a demonstration is performed by moving the Baxter arms in the appropriate trajectory.
+	\caption{Workflow of Robotic cloth manipulation task.
+Initially, a demonstration is performed by moving the Baxter arms in the appropriate trajectory.
 The demonstration is recorded and parameterized by DMP.
-Later posture of the mannequin is changed and accordingly the goal posture of DMP is modified.
+Later on, posture of the mannequin is changed and accordingly the goal posture of DMP is modified.
 Now, the modified DMP can accommodate new posture.}
@@
 \label{sec:dmp}
-Dynamic Movement Primitives (DMP) aims at designing contoller for learning and generalization of motor skills by learning from demonstration \cite{ijspeert2003learning}.
-The controllers are based on nonlinear dynamical systems, and use locally weighted regression techniques to learn complex, discrete or rhythmic, movements demonstrated by a human subject \cite{ijspeert2002movement}.
+Dynamic Movement Primitives (DMP) aims at designing controller for learning and generalization of motor skills by learning from demonstration \cite{ijspeert2003learning}.
+The controllers are based on nonlinear dynamical systems and use locally weighted regression techniques to learn complex, discrete or rhythmic, movements demonstrated by a human subject \cite{ijspeert2002movement}.
 These controllers can be considered to be discrete or rhythmic pattern generators which can replay and modulate the learned movements, while being robust against perturbations.
 
-The basic idea behind DMP formulation is to use an analytically well-understood dynamical system and add a nonlinear terms, so that it produces the desired behavior \cite{ijspeert2013dynamical}.
+The basic idea behind DMP formulation is to use an analytically well-understood dynamical system and add a nonlinear term, so that it produces the desired behavior \cite{ijspeert2013dynamical}.
 Formally, the system is defined by a damped spring model as below:
@@
 \label{sec:system_overview}
+In this section, we provide a brief overview of the system.
 As per the formulation described in section \ref{sec:dmp}, DMP can learn from demonstration.
@@
 In this phase, recorded trajectory is parameterized by DMP system.
-The parameterized DMP can represents all the characteristics of original trajectory.
+The parameterized DMP can represent all the characteristics of original trajectory.
 Here, three DMP systems, one for each coordinate axis i.e., $x$, $y$ and $z$ are initialized for one arm.
@@
 We change the goal of DMP trajectories by using this information.
-In this way, we have generalised DMP system, which can adapt modified posture referred as ``DMP Generalization''.
+In this way, we have generalized DMP system, which can adapt modified posture referred as ``DMP Generalization''.
 
@@
 Both the arms of mannequin are open and given the support by a metallic stand, to avoid falling down the arms.
-The mannequin is positioned in such a way, so that it resides within the limits of work space of the Baxter robot.
+The mannequin is positioned in such a way so that it resides within the limits of workspace of the Baxter robot.
 Both the arms of mannequin are facing towards robot.
@@
 The Baxter robot is connected to a computer directly using Ethernet cable.
-It is controlled using Robot Operating System (ROS) \cite{quigley2009ros}, one of the widely used tool by the researchers in robotics community.
-We used Baxter robot's API, which are available and supported by ROS to command the robot.
+It is controlled using Robot Operating System (ROS) \cite{quigley2009ros}, one of the widely used tools by the researchers in the robotics community.
+We used Baxter robot's API, which is available and supported by ROS to command the robot.
 The Kinect sensor is controlled by Open source Kinect API for ROS \cite{iai_kinect2, libfreenect2}.
@@
 The newly generated DMP trajectory (shown in red color) was not only found well suited and capable of performing clothing task but also smooth compared to the original trajectory (shown in blue color).
-A video demonstartion of this experiment can be seen at YouTube\footnote{\url{http://youtu.be/Rb2JePazJjk}}.
+A video demonstration of this experiment can be seen at YouTube\footnote{\url{http://youtu.be/Rb2JePazJjk}}.
 
@@
 This experiment is designed to deal with failure cases.
-There can be many failure cases during the clothing task, such as the clothing article gets stuck into the fingers.
+There can be many failure cases during the clothing task, such as clothing article gets stuck into the fingers, sleeve getting stuck on the arms, sleeve not entering the arm but entirely missing etc.
 In this experiment, we are using forces being applied on the end-effector of Baxter robot to detect the failure scenario.
@@
 The trajectories were monitored and categorized into two \textit{success} and \textit{failure}.
-The mean of these two category is calculated and plotted as shown in figure \ref{fig:position_force}.
+The mean of these two categories is calculated and plotted as shown in figure \ref{fig:position_force}.
 This is the average profile over several success and failure trajectories for different postures of the mannequin.
@@
 It is clearly visible from the figure \ref{fig:position_force} that the applied forces are very different in nature in both the cases.
-Both of these forces are increasing from the beginning however forces in case of \textit{failure} are much more higher than that of \textit{success}.
+Both of these forces are increasing from the beginning, however, forces in case of \textit{failure} are much higher than that of \textit{success}.
 Hence one can easily differentiate and detect the failure by using this information.
@@
 This paper presents an approach for robotic cloth manipulation for clothing assistance task using Dynamic Movement Primitives.
-A dual arm Baxter robot, soft mannequin and very thin sleeveless T-shirt were used in the task.
+A dual arm Baxter robot, soft mannequin, and very thin sleeveless T-shirt were used in the task.
 We have also presented an approach for failure detection using forces being applied on the end-effector of the robot.
@@
 We plan to extend our research to make the approach more robust by adding visual information and force information with DMP system in the future.
-Also there is a need of designing an adaptive controller for real time tracking to adapt and detect various failure scenarios.
+Also, there is a need for designing an adaptive controller for real-time tracking to adapt and detect various failure scenarios.
 Therefore, in the future, a combination of robot vision and force data can provide the better estimation of cloth state.

### 2017-01-30 paper/images/improved_DMP/compare_DMPs.py

@@ -1,0 +1,36 @@
+import numpy as np
+import matplotlib.pylab as plt
+from dmp import DMPs_discrete, TdwFormulation, OriginalFormulation, ImprovedFormulation
+
+x = np.linspace(0, np.pi/2, 200)
+poses = np.sin(x)
+
+goal = np.array([1.5])
+dt = 1.0/poses.shape[0]
+nbfs = 100
+
+tdwFormulationDmp = DMPs_discrete(dims=1, bfs=nbfs, ts=TdwFormulation(), dt=dt)
+tdwFormulationDmp.learn(y_des=poses.T)
+tdwFormulationDmp.set_goal_state(goal)
+
+originalFormulationDmp = DMPs_discrete(dims=1, bfs=nbfs, ts=OriginalFormulation(), dt=dt)
+originalFormulationDmp.learn(y_des=poses.T)
+originalFormulationDmp.set_goal_state(goal)
+
+improvedFormulationDmp = DMPs_discrete(dims=1, bfs=nbfs, ts=ImprovedFormulation(),dt=dt)
+improvedFormulationDmp.learn(y_des=poses.T)
+improvedFormulationDmp.set_goal_state(goal)
+
+tdwFormulationDmp_y, tdwFormulationDmp_dy, tdwFormulationDmp_ddy = tdwFormulationDmp.plan()
+originalFormulationDmp_y, originalFormulationDmp_dy, originalFormulationDmp_ddy = originalFormulationDmp.plan()
+improvedFormulationDmp_y, improvedFormulationDmp_dy, improvedFormulationDmp_ddy = improvedFormulationDmp.plan()
+
+plt.figure(1)
+plt.plot(poses, label='Actual Trajectory')
+plt.plot(tdwFormulationDmp_y, '--', label='DMP [Tdw Formulation]')
+plt.plot(originalFormulationDmp_y, label='DMP [Original Formulation]')
+plt.plot(improvedFormulationDmp_y, label='DMP [Improved Formulation]')
+plt.legend(loc='upper left')
+plt.grid(True)
+plt.title('Comparison between various DMP Formulations (DMP.goal=%.1f)' % goal[0])
+plt.show()

### 2017-01-30 paper/images/improved_DMP/example.py

@@ -7,7 +7,9 @@ pose = np.sin(x)
 
 goal = np.array([1.5])
 dt = 1.0/pose.shape[0]
-nbfs = 100
+nbfs = 10
+
+delta_t = 0.001
 
 improvedDmp = DMPs_discrete(dims=1, bfs=nbfs, ts=ImprovedFormulation(),dt=dt)
 improvedDmp.learn(y_des=pose.T)
@@ -16,15 +18,15 @@ improvedDmp.set_goal_state(goal)
 improvedDmp_y, improvedDmp_dy, improvedDmp_ddy = improvedDmp.plan()
 
 plt.figure(1)
-plt.plot(pose, label='Actual')
-plt.plot(improvedDmp_y, label='DMP')
-plt.legend(loc='upper right')
-plt.title('Trajectories')
-plt.figure(2)
-plt.plot(improvedDmp.w.T)
+x = np.array(range(improvedDmp.w.T.shape[0]))
+pose = pose[::20]
+improvedDmp_y = improvedDmp_y[::20]
+
+plt.bar(x, improvedDmp.w.T)
+plt.plot(x, pose, label='Actual')
+plt.plot(x, improvedDmp_y, label='DMP')
+
+plt.legend(loc='upper left')
 plt.title('DMP Weights')
-plt.figure(3)
-plt.plot(improvedDmp.f_desired)
-plt.title('Desired Force')
 
 plt.show()

### 2017-02-09 paper/images/failure_scenarios/failure_scenario_1.tex
[minor] image text changed to sans-serif

--- 2017-01-29 paper/images/inclination/inclination.tex
@@
 \usepackage{tikz}
-\usetikzlibrary{shapes.geometric, arrows}
-
-\newcommand*{\BoxWidth}{4cm}%
-\tikzset{
-    to/.style     = {->},
-    line/.style   = {line width=0.4mm, draw=blue},
-    darrow/.style = {<->, line width=0.4mm, draw=blue},
-    box/.style    = {draw, rectangle, minimum height = 1cm, minimum width = \BoxWidth, text centered, text width=\BoxWidth, ultra thin, draw=black, fill=blue!10, font=\large}
-}
-
-\pgfmathsetmacro{\ex}{0.85}
-\pgfmathsetmacro{\ey}{0.60}
+\usetikzlibrary{shapes.geometric}
 
@@
 \begin{tikzpicture}
-	\node[anchor=south west,inner sep=0] (image) at (0,0,0) {\includegraphics[width=\linewidth]{mannequin}};
+	\node[anchor=south west,inner sep=0] (image) at (0,0,0) {\includegraphics[width=\linewidth]{1}};
 	\begin{scope}[x={(image.south east)},y={(image.north west)}]
 		\iffalse
-			%% Next four lines helps to locate the point needed by forming a grid
+		% Next four lines helps to locate the point needed by forming a grid
 		\draw[help lines,xstep=.1,ystep=.1] (0,0) grid (1,1);
@@
 		\begin{scope}[x={(image.south east)},y={(image.north west)}]
-			\draw[line] (0.30,0.60) -- (\ex,\ey);
-			\draw[line] (0.20,0.25) -- (\ex,\ey);
-			\draw[darrow](\ex,\ey) ++(-152:.2) arc (-152:-180:.2);
-			\draw[to](0.40,0.65) node[box]{Angle of inclination} to [out=-90,in=200] (0.65,0.55);
+			\draw (0.45,0.23) node[ellipse, ultra thick, draw=red,minimum height=80pt,minimum width=150pt] {};
 		\end{scope}

### 2017-02-09 paper/images/failure_scenarios/failure_scenario_2.tex
[minor] image text changed to sans-serif

--- 2017-02-09 paper/images/failure_scenarios/failure_scenario_1.tex
@@
 \begin{tikzpicture}
-	\node[anchor=south west,inner sep=0] (image) at (0,0,0) {\includegraphics[width=\linewidth]{1}};
+	\node[anchor=south west,inner sep=0] (image) at (0,0,0) {\includegraphics[width=\linewidth]{2}};
 	\begin{scope}[x={(image.south east)},y={(image.north west)}]
@@
 		\begin{scope}[x={(image.south east)},y={(image.north west)}]
-			\draw (0.45,0.23) node[ellipse, ultra thick, draw=red,minimum height=80pt,minimum width=150pt] {};
+			\draw (0.48,0.2) node[ellipse, ultra thick, draw=red,minimum height=80pt,minimum width=150pt] {};
 		\end{scope}

### 2017-02-09 paper/images/inclination/inclination.tex
[minor] image text changed to sans-serif

@@
 
-\newcommand*{\BoxWidth}{4cm}%
 \tikzset{
-    to/.style     = {->},
-    line/.style   = {line width=0.4mm, draw=blue},
-    darrow/.style = {<->, line width=0.4mm, draw=blue},
-    box/.style    = {draw, rectangle, minimum height = 1cm, minimum width = \BoxWidth, text centered, text width=\BoxWidth, ultra thin, draw=black, fill=blue!10, font=\large}
+    to/.style     = {->, line width=0.4mm},
+    line/.style   = {line width=0.6mm, draw=blue},
+    darrow/.style = {<-, line width=0.6mm, draw=blue},
+    box/.style    = {draw, rectangle, rounded corners, minimum height = 3cm, text centered, text width=5cm, fill=white, font=\Huge\sffamily}
 }
@@
 			\draw[darrow](\ex,\ey) ++(-152:.2) arc (-152:-180:.2);
-			\draw[to](0.40,0.65) node[box]{Angle of inclination} to [out=-90,in=200] (0.65,0.55);
+			\draw[to](0.22,0.65) node[box]{Angle of Inclination} to [out=-40,in=200] (0.65,0.55);
 		\end{scope}

### 2017-02-09 paper/paper.tex
[major] add more comments from Nishanth
[minor] image text changed to sans-serif

@@
 Primitives}
-%\titlenote{Produces the permission block, and copyright information}
-%\subtitle{Extended Abstract}
-%\subtitlenote{The full version of the author's guide is available as
-%  \texttt{acmart.pdf} document}
 
@@
 \authornote{Ravi P. Joshi is with Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Fukuoka, Japan}
-\affiliation{%
-%	\institution{Kyushu Institute of Technology}
-%	\city{Kitakyushu}
-%	\state{Fukuoka}
-%	\country{Japan}
-}
+\affiliation{}
 \email{joshi-ravi-prakash@edu.brain.kyutech.ac.jp}
@@
 \authornote{Nishanth Koganti is with Graduate School of Information Science, Nara Institute of Science and Technology, Nara, Japan and Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Fukuoka, Japan}
-\affiliation{%
-%	\institution{Nara Institute of Science and Technology}
-%	\city{Ikoma}
-%	\state{Nara}
-%	\country{Japan}
-}
+\affiliation{}
 \email{nishanth-k@is.naist.jp}
@@
 \authornote{Tomohiro Shibata is with Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Fukuoka, Japan}
-\affiliation{%
-%	\institution{Kyushu Institute of Technology}
-%	\city{Kitakyushu}
-%	\state{Fukuoka}
-%	\country{Japan}
-}
+\affiliation{}
 \email{tom@brain.kyutech.ac.jp}
@@
 \begin{abstract}
-	The need of robotic clothing assistance in the field of assistive robotics is growing, as it is one of the most basic activities in the daily life of elderly and disabled people.
-In this study, we are investigating the applicability of using Dynamic Movement Primitives (DMP) as a task parameterization model for performing clothing assistance tasks.
-The robotic cloth manipulation task deals with putting the cloth on both the arms.
-The clothing assistance is a challenging problem since robot must do cooperative manipulation by holding the cloth using both the arms while interacting with non-rigid and highly deformable clothes, and with the assisted person whose posture can vary during the assistance.
+	The need of robotic clothing assistance in the field of assistive robotics is growing, as it is one of the most basic activities in daily life of elderly and disabled people.
+In this study, we are investigating the applicability of using Dynamic Movement Primitives (DMP) as a task parameterization model for performing clothing assistance task.
+Robotic cloth manipulation task deals with putting a clothing article on both the arms.
+The clothing assistance is a challenging problem since robot must do cooperative manipulation by holding the cloth using both the arms while interacting with non-rigid and highly deformable clothes, and with the assisted person whose posture can vary during assistance.
 The system consists of dual arm Baxter research robot and Microsoft Kinect V2 RGBD sensor for tracking the posture of arms.
-The cloth manipulation is done by Baxter robot which follows the trajectory generated by DMP system.
-We have performed the experiments on soft mannequin instead of human.
-The result shows that DMPs are able to generalize the movement trajectory for the modified posture.
+The cloth manipulation is done by Baxter robot which follows trajectory generated by DMP system.
+We have performed experiments on soft mannequin instead of human.
+Result shows that DMPs are able to generalize movement trajectory for modified posture.
 \end{abstract}
 
-%
 % The code below should be generated by the tool at
 % http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below.
-%
 \begin{CCSXML}
@@
 	<concept>
-	<concept_id>10010520.10010553.10010562</concept_id>
-	<concept_desc>Computer systems organization~Embedded systems</concept_desc>
+	<concept_id>10010147.10010178.10010213.10010215</concept_id>
+	<concept_desc>Computing methodologies~Motion path planning</concept_desc>
 	<concept_significance>500</concept_significance>
@@
 	<concept>
-	<concept_id>10010520.10010575.10010755</concept_id>
-	<concept_desc>Computer systems organization~Redundancy</concept_desc>
-	<concept_significance>300</concept_significance>
-	</concept>
-	<concept>
-	<concept_id>10010520.10010553.10010554</concept_id>
-	<concept_desc>Computer systems organization~Robotics</concept_desc>
-	<concept_significance>100</concept_significance>
-	</concept>
-	<concept>
-	<concept_id>10003033.10003083.10003095</concept_id>
-	<concept_desc>Networks~Network reliability</concept_desc>
+	<concept_id>10010147.10010178.10010213.10010214</concept_id>
+	<concept_desc>Computing methodologies~Computational control theory</concept_desc>
 	<concept_significance>100</concept_significance>
@@
 
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
-
-% We no longer use \terms command
-%\terms{Theory}
+\ccsdesc[500]{Computing methodologies~Motion path planning}
+\ccsdesc[100]{Computing methodologies~Computational control theory}
 
@@
 	\includegraphics[width=\linewidth]{setup}
-	\caption{Setup of Robotic cloth manipulation task}
+	\caption{Setup of robotic cloth manipulation task}
 	\label{fig:setup}
@@
 \label{sec:introduction}
-Due to the demographic trend in developed countries, the robotic assistance in the field of elderly care in the home environment is growing \cite{broekens2009assistive}.
-Although there has been a significant number of research done in this field, the robotic clothing assistance is yet an open field for research.
-Not to mention that it is one of the basic and important assistance activities in the daily life of elderly as well as disabled people.
-While rigid object manipulation with robots has mainly relied on precise robot control, the deformable objects rather require complex control scheme.
-The clothing assistance is a challenging problem since the robot is required to manage two difficulties: (a) the robot must do cooperative manipulation by holding the cloth using both the arms while interacting with non-rigid and highly deformable clothes and (b) maintain safe human-robot interaction with the assisted person whose posture can vary during the assistance.
+Due to the demographic trend in developed countries, robotic assistance in the field of elderly care in home environment is growing \cite{broekens2009assistive}.
+Although there has been a significant number of research done in this field, robotic clothing assistance is yet an open field for research.
+Not to mention that it is one of the basic and important assistance activities in daily life of elderly as well as disabled people.
+While rigid object manipulation with robots has mainly relied on precise robot control, deformable objects rather require complex control scheme.
+The clothing assistance is a challenging problem since robot is required to manage two difficulties: (a) robot must do cooperative manipulation by holding cloth using both the arms while interacting with non-rigid and highly deformable cloth and (b) maintain safe human-robot interaction with the assisted person whose posture can vary during assistance.
 
-In this study, we are investigating the applicability of using Dynamic Movement Primitives (DMP) as a task parameterization model for performing clothing assistance tasks.
-The robotic cloth manipulation task deals with putting the cloth on both the arms.
-The idea of using DMP is inspired by the fact that DMP can learn complex task from the demonstration \cite{ijspeert2003learning, schaal2006dynamic, ijspeert2013dynamical} and thus reduce the manual efforts to design the controller from scratch or to fine-tune the controller parameters.
-We choose the dual arm Baxter robot in this research as it is safe and flexible by design \cite{fitzgerald2013developing}.
+In this study, we are investigating the applicability of using Dynamic Movement Primitives (DMP) as a task parameterization model for performing clothing assistance task.
+Robotic cloth manipulation task deals with putting a clothing article on both the arms.
+The idea of using DMP is inspired by the fact that DMP can learn complex task from the demonstration \cite{ijspeert2003learning, schaal2006dynamic, ijspeert2013dynamical} and thus reduce the manual efforts to design a controller from scratch or to fine-tune various controller parameters.
+We choose dual arm Baxter robot in this research as it is safe and flexible by design \cite{fitzgerald2013developing}.
 
-The rest of the paper is organized as follows.
-Section \ref{sec:related_works}, gives a brief overview of the related literature in this field.
-Section \ref{sec:dmp} introduces the mathematical formulation about Dynamic Movement Primitives.
-In Section \ref{sec:system_overview}, we describe our system and various components used in the experiments.
-Section \ref{sec:experiments} deals with the details of experiments performed and their results.
-Finally we conclude in Section \ref{sec:conclusions} with some future directions.
+Rest of the paper is organized as follows.
+Section \ref{sec:related_works}, gives brief overview of related literature in this field.
+In Section \ref{sec:method}, we introduce mathematical formulation about DMP followed by describing proposed method and its workflow.
+Section \ref{sec:experiments} deals with details of various experiments performed and their results.
+The discussion about experiments is presented in section \ref{sec:discussion}.
+Finally we conclude in section \ref{sec:conclusions} with some future directions.
 
@@
 \label{sec:related_works}
-There has been a significant number of research done in the field of Robotic Clothing Assistance by using vision system.
+There has been a significant number of research done in the field of robotic clothing assistance by using vision system.
 Klee et al.
-\cite{klee2015personalized} worked on personalized assistance for dressing a user, where they used vision module to monitor the human's motion.
-The robot request to a user to move towards the robot, monitors motion and puts a hat on the user once users is reachable by the robot.
+\cite{klee2015personalized} worked on personalized assistance for dressing a user.
+The robot request user to move towards robot, monitors motion using vision module and puts a hat on user once users is reachable by the robot.
 They haven't considered human and cloth interaction.
@@
 \cite{yamazaki2013method, yamazaki2014bottom}  worked on bottom dressing by a life-sized humanoid robot, where they recognize the cloth state by using optical flow on the images acquired from a single camera.
-They showed that the robot can pull a bottom clothing item along the subject's legs.
 They did not handle large occlusions.
@@
 \cite{yamakawa2011dynamic} proposed a new strategy for dynamic manipulation of sheet-like flexible objects by a high-speed robot system.
-The system consists of two high-speed multi-fingered hands mounted on two sliders and a high-speed vision system.
-The proposed system learns the necessary motor skills from the demonstration performed by a human subject.
-They validated the robot trajectory obtained from the motion planning method was with simulation results.
+The proposed system learns necessary motor skills from demonstration performed by a human subject.
 They worked on fast cloth state tracking but it is not related to robotic clothing assistance.
 
-The robotic cloth handling is challenging.
-Unlike rigid object manipulation using robots, which has mainly relied on precise robot control, the deformable objects rather require complex control scheme.
-Many researchers have used vision information with the combination of techniques such as motor skills learning using Reinforcement Learning.
+Robotic cloth handling is challenging.
+Unlike rigid object manipulation using robots, which has mainly relied on precise robot control, deformable objects rather require complex control scheme.
+Many researchers have used vision information with combination of techniques such as motor skills learning using Reinforcement Learning.
 Colom{\'e} et al.
-\cite{colome2015friction} proposed a framework for Reinforcement Learning of robotic tasks in non-rigid environments.
-They performed the task of wrapping a scarf around the neck of a mannequin and used color based segmentation to distinguish mannequin, scarf and a mark placed on the nose of mannequin.
-The main focus of their work is to incorporate friction based model while performing clothing task.
+\cite{colome2015friction} proposed a framework for Reinforcement Learning of robotic tasks in non-rigid environments by incorporating friction based model.
 Gao et al.
-\cite{gao2015user, gao2016iterative} have focused on user upper-body modeling for personalized dressing by using top-view depth camera.
-Randomized decision forests were used to estimate user pose and proposed an online iterative path optimization method to enable Baxter humanoid robot to assist human in wearing a sleeveless jacket.
+\cite{gao2015user, gao2016iterative} have focused on user upper-body modeling for personalized dressing by using top-view depth camera with the help of randomized decision forests to estimate user pose.
+They proposed an online iterative path optimization method to enable Baxter robot to assist human in wearing a sleeveless jacket.
 Another interesting work by Kapusta et al.
 \cite{kapusta2016data} is focused towards designing a controller inspired from data-driven haptic perception.
-They classified the forces measured at robot's end effector by using hidden Markov models and performed the clothing task on the hospital gown.
+They classified the forces measured at robot's end effector by using hidden Markov models and performed clothing task using hospital gown.
 Their focus was to classify force data for haptic perception with high accuracy.
 Koganti et al.
-\cite{koganti2015cloth} proposed a framework for offline learning of cloth dynamics model using Gaussian Process Latent Variable Models (GP-LVM) by incorporating motion capture data and applying this model for the online tracking of human-cloth relationship using a depth sensor.
-They showed that the shared GP-LVM is able to learn reliable motion models of the T-shirt state for robotic clothing assistance tasks.
-Representing cloth state in low-dimensional field by using topology coordinates is another impressive work done by Tamei et al.
+\cite{koganti2015cloth} proposed a framework for offline learning of cloth dynamics model using Gaussian Process Latent Variable Models (GP-LVM) by incorporating motion capture data and applying this model for online tracking of human-cloth relationship using a depth sensor.
+They showed that shared GP-LVM is able to learn reliable motion models of the T-shirt state for clothing task.
+Representing cloth state in low-dimensional field by using topology coordinates is another impressive work by Tamei et al.
 \cite{tamei2011reinforcement}.
-They proposed Reinforcement Learning framework and demonstrated that the robot quickly learns a suitable arm motion for putting T-shirt into the mannequin's head.
+They proposed Reinforcement Learning framework and demonstrated that robot quickly learns a suitable arm motion for putting T-shirt into the mannequin's head.
 Another exciting work was done by Mons{\'o} et al.
@@
 
-The problem of robotic clothing assistance not only depends on tracking the cloth dynamics but also the motor skills required to perform the task.
+The problem of robotic clothing assistance not only depends on tracking cloth dynamics but also motor skills required to perform the task.
 A combination of such techniques is encouraged.
 However, we see that there has been a large gap when compared it to the practical use cases in elderly care.
-The most important point should be the learning rate of the task.
-We believe that \textit{Learning from Demonstration} framework are quick to learn in cases which involve complex task specific dynamics.
-The problem of putting sleeveless T-shirt into the arms of the mannequin is close to the practical use case.
+The most important point should be learning rate of the task.
+We believe that \textit{Learning from Demonstration} frameworks are quick to learn in cases which involve complex task specific dynamics.
+The problem of putting sleeveless T-shirt into the arms of mannequin is close to the practical use case.
 Therefore, we are putting our efforts to solve it.
@@
 	\includegraphics[width=\linewidth]{flowchart_conf}
-	\caption{Workflow of Robotic cloth manipulation task.
-Initially, a demonstration is performed by moving the Baxter arms in the appropriate trajectory.
-The demonstration is recorded and parameterized by DMP.
-Later on, posture of the mannequin is changed and accordingly the goal posture of DMP is modified.
-Now, the modified DMP can accommodate new posture.}
+	\caption{Workflow of robotic cloth manipulation task.
+Initially, a demonstration is performed by moving Baxter arms in appropriate trajectory.
+This demonstration is recorded and parameterized by DMP.
+Later on, posture of the mannequin is changed and accordingly goal parameter of DMP is modified.
+Now, modified DMP can accommodate new posture.}
 	\label{fig:workflow}
@@
 
-\section{Dynamic Movement Primitives}
+\section{Method}
+\label{sec:method}
+Robotic cloth manipulation task deals with putting a clothing article on both the arms.
+We are using DMP framework to learn this complex task from demonstration and thus reduce the manual efforts to design the controller from scratch.
+We choose dual arm Baxter robot in this research.
+Following subsections explain about underlying DMP framework followed by the proposed method.
+
+\subsection{Dynamic Movement Primitives}
 \label{sec:dmp}
 Dynamic Movement Primitives (DMP) aims at designing controller for learning and generalization of motor skills by learning from demonstration \cite{ijspeert2003learning}.
-The controllers are based on nonlinear dynamical systems and use locally weighted regression techniques to learn complex, discrete or rhythmic, movements demonstrated by a human subject \cite{ijspeert2002movement}.
-These controllers can be considered to be discrete or rhythmic pattern generators which can replay and modulate the learned movements, while being robust against perturbations.
+The controller is based on nonlinear dynamical system and use locally weighted regression techniques to learn complex, discrete or rhythmic, movements demonstrated by a human subject \cite{ijspeert2002movement}.
+The controller can be considered to be discrete or rhythmic pattern generator which can replay and modulate the learned movements, while being robust against perturbations.
 
 The basic idea behind DMP formulation is to use an analytically well-understood dynamical system and add a nonlinear term, so that it produces the desired behavior \cite{ijspeert2013dynamical}.
-Formally, the system is defined by a damped spring model as below:
+Formally, it is defined by a damped spring model as below:
 
@@
 
-where $h_i$ and $c_i$ are constants that determine, respectively, the width and centers of the basis functions.
-$w_i$ represents the weight defined for each Gaussian.
-The forcing function $f$ depends on phase variable $s$.
-Phase variable $s$ starts from 1 and monotonically decreases to 0, defined by equation below:
+where $h_i$ and $c_i$ are constants that determine, respectively, width and centers of basis functions.
+$w_i$ represents weight defined for each Gaussian.
+Forcing function $f$ depends on phase variable $s$.
+Phase variable $s$ starts from $1$ and monotonically decreases to $0$, defined by equation below:
 
@@
 where $\alpha$ is a positive gain term.
-Our goal is to design the forcing function that can learn from the demonstration and allows us to scale the movement defined by goal state $g$.
-In other words, we want to setup the system which can follow a specified path.
+Our goal is to design a forcing function that can learn from demonstration and allows us to scale the movement defined by goal state $g$.
+In other words, we want to setup a system which can follow specified path.
 The forcing term can be redefined as:
@@
 
-where desired acceleration $\dot{v}(t)$ can be calculated by double differentiating the position data recorded from the demonstration as
+where desired acceleration $\dot{v}(t)$ can be calculated by double differentiating position data recorded from demonstration as
 
@@
 
-The forcing function [\ref{eq:forcing_func}] is comprised of weighted summation of Gaussian that are going to be activated as system converges to the goal as shown in figure \ref{fig:psi_activations}.
+The forcing function [\ref{eq:forcing_func}] is comprised of weighted summation of Gaussian that are going to be activated as system converges to goal as shown in figure \ref{fig:psi_activations}.
 We want that forcing function matches the desired trajectory.
@@
 
-This ends by calculating the weight parameters across Gaussians.
-Optimization methods such as locally weighted regression \cite{vijayakumar2000locally} can be used, so that the forcing function matches the desired trajectory.
-This way DMP can be made to imitate the desired path \cite{pastor2009learning}.
+This ends by calculating weight parameters across Gaussians.
+Optimization methods such as locally weighted regression \cite{vijayakumar2000locally} can be used, so that forcing function matches desired trajectory.
+This way DMP can be made to imitate desired path \cite{pastor2009learning}.
 
-\section{Overview of the System}
+\subsection{Robotic Cloth Manipulation using DMP}
 \label{sec:system_overview}
-In this section, we provide a brief overview of the system.
+In this section, we provide brief overview of our system.
 As per the formulation described in section \ref{sec:dmp}, DMP can learn from demonstration.
-Therefore we start by performing a demonstration by holding the robot arm as shown in figure \ref{fig:workflow}.
+Therefore we start by performing a demonstration by holding robot arm as shown in figure \ref{fig:workflow}.
 This is referred as ``Teaching Phase'', since in this phase, we are teaching skills to robot to perform the task.
-During the demonstration, pose trajectory of the end-effector is recorded using Baxter API and stored in a file.
+During the demonstration, pose trajectory of end-effector is recorded using Baxter API and stored in a file.
 The term pose collectively refers to position and orientation.
-Once the demonstration is finished, DMP is initialized using the recorded trajectory file.
+Once the demonstration is finished, DMP is initialized using recorded trajectory file.
 This is termed as ``Learn Trajectory'' phase.
@@
 In this way, we have total six DMP systems, which can control both the arms of Baxter robot.
-In ``Testing Phase'', we change the posture of mannequin by lifting the arms up or down.
-At this point, we use Kinect Sensor to get the 3D coordinates of the arm.
-We change the goal of DMP trajectories by using this information.
+In ``Testing Phase'', we change the posture of mannequin by lifting arms up or down.
+At this point, we use Kinect Sensor to get the 3D coordinates of arm.
+Before using Kinect Sensor, it is very important to do Kinect-Baxter calibration, so that 3D coordinates are translated from Kinect space to Baxter space.
+We change goal parameter of DMP trajectories by using this information.
 In this way, we have generalized DMP system, which can adapt modified posture referred as ``DMP Generalization''.
@@
 Robotic cloth manipulation task contains a dual arm humanoid robot Baxter.
-Setup of the system is shown in figure \ref{fig:setup}.
-We choose soft mannequin instead of a human for this preliminary experiment.
-Both the arms of mannequin are open and given the support by a metallic stand, to avoid falling down the arms.
-The mannequin is positioned in such a way so that it resides within the limits of workspace of the Baxter robot.
+Setup of our system is shown in figure \ref{fig:setup}.
+We choose soft mannequin instead of a human for this experiment.
+Both the arms of mannequin are open and given support by a metallic stand, to avoid falling down the arms.
+Mannequin is positioned in such a way so that it resides within limits of workspace of Baxter robot.
 Both the arms of mannequin are facing towards robot.
-A Kinect V2 \cite{microsoft2014kinect} sensor is mounted on LCD display of Baxter root.
+A Kinect V2 \cite{microsoft2014kinect} sensor is mounted on LCD display of Baxter robot.
 Kinect sensor can see the mannequin and clothing article and provides depth information, which is necessary for mannequin tracking.
-The clothing article is put in arms of Baxter robot manually before starting the experiment.
+The clothing article is put in the arms of Baxter robot manually before starting experiment.
 
-The Baxter robot is connected to a computer directly using Ethernet cable.
-It is controlled using Robot Operating System (ROS) \cite{quigley2009ros}, one of the widely used tools by the researchers in the robotics community.
+Baxter robot is connected to a computer directly using Ethernet cable.
+It is controlled using Robot Operating System (ROS) \cite{quigley2009ros}, one of the widely used tools by the researchers in robotics community.
 We used Baxter robot's API, which is available and supported by ROS to command the robot.
-The Kinect sensor is controlled by Open source Kinect API for ROS \cite{iai_kinect2, libfreenect2}.
+Kinect sensor is controlled by open source Kinect API for ROS \cite{iai_kinect2, libfreenect2}.
 We performed following two experiments to validate our approach: (a) Clothing task using position DMP (b) Failure detection using end-effector forces.
 
-\begin{figure}
-	\includegraphics[width=0.7\linewidth]{inclination}
-	\caption{Angle of Inclination}
-	\label{fig:inclination}
-\end{figure}
+\subsection{Clothing task using position DMP}
+The aim of this experiment is to put sleeveless T-shirt on both the arms of mannequin by using DMP system.
+We use position data to initialize DMP trajectories, which are being used in this task.
+The posture of mannequin is changed by lifting arms up or down.
+At this point, we use Kinect Sensor to get 3D coordinates of arms.
+Now we change goal parameter of DMP trajectories by using this information.
+Modified DMP can be acquired by rolling out DMP system as described in section \ref{sec:dmp}.
 
-\subsection{Clothing task using position DMP}
-The aim of this experiment is to put the clothing article on both the arms of mannequin by using DMP system.
-We use the position data to initialize the DMP trajectories, which are being used in this task.
-The posture of mannequin is changed by lifting the arms up or down.
-At this point, we use Kinect Sensor to get the 3D coordinates of the arm.
-Now we change the goal of DMP trajectories by using this information.
-The modified DMP can be acquired as described in section \ref{sec:dmp}.
-
-In this experiment, the initialized DMP was modified to accommodate the new posture by changing the goal state of the DMP.
-The generated trajectory was then run on the Baxter robot as shown in figure \ref{fig:trajectory}.
-The newly generated DMP trajectory (shown in red color) was not only found well suited and capable of performing clothing task but also smooth compared to the original trajectory (shown in blue color).
+In this experiment, the initialized DMP was modified to accommodate new posture by changing goal parameter of DMP.
+The generated trajectory was then run on Baxter robot as shown in figure \ref{fig:trajectory}.
+Newly generated DMP trajectory (shown in red color) was not only found well suited and capable of performing clothing task but also smooth compared to original trajectory (shown in blue color).
 A video demonstration of this experiment can be seen at YouTube\footnote{\url{http://youtu.be/Rb2JePazJjk}}.
 
-To eventuate this experiment, we performed it many times for various angle of inclination by keeping the arms at different-different height as shown in figure \ref{fig:inclination}.
-During the experiment, we monitored the trajectory generated by DMP system.
+To evaluate this experiment, we performed it many times and monitored trajectory generated by DMP system.
+We defined angle of inclination as the angle between arm of mannequin and horizontal axis.
+The angle of inclination is defined in clockwise direction, hence it is $+ve$ when arms are inclined upward, similarly it is $-ve$ when arms are inclined downward.
+It was changed by keeping arms at different-different height.
 The accuracy measurement is shown in figure \ref{fig:accuracy}.
+It was observed that DMP system was able to generate the appropriate trajectory for a range of $20^\circ$ and it never failed in this range.
+However, as we keep on going far away from the original posture, success rate starts declining and finally reached to $0$.
 
 \begin{figure}
-	\includegraphics[width=\linewidth]{accuracy}
+	\centering
+	\begin{subfigure}{.35\linewidth}
+		\includegraphics[width=\linewidth]{inclination}
+	\end{subfigure}%
+	\begin{subfigure}{.65\linewidth}
+		\includegraphics[width=\linewidth]{success_rate}
+	\end{subfigure}
 	\caption{Accuracy measurement}
@@
 This experiment is designed to deal with failure cases.
-There can be many failure cases during the clothing task, such as clothing article gets stuck into the fingers, sleeve getting stuck on the arms, sleeve not entering the arm but entirely missing etc.
-In this experiment, we are using forces being applied on the end-effector of Baxter robot to detect the failure scenario.
+There can be many failure cases during the task, such as clothing article gets stuck into the fingers, sleeve getting stuck on the arms, sleeve not entering the arm but entirely missing etc, as shown in figure \ref{fig:failure_scenarios}.
+In this experiment, we are using forces being applied on the end-effector of Baxter robot to detect failure scenario.
 Appropriate action can be taken once the failure is detected.
@@
 The clothing task has to deal with complex dynamics including manipulation of clothing article.
-The clothes are non-rigid, flexible and highly deformable objects, making the task more difficult to perform.
-During the clothing task, we observed the forces being applied at both the end-effector of Baxter robot.
-The trajectories were monitored and categorized into two \textit{success} and \textit{failure}.
+Clothes are non-rigid, flexible and highly deformable objects, making the task more difficult to perform.
+During the task, we observed forces being applied at both the end-effector of Baxter robot.
+Trajectories were monitored and categorized into two \textit{success} and \textit{failure}.
 The mean of these two categories is calculated and plotted as shown in figure \ref{fig:position_force}.
@@
 \begin{figure}
-	\includegraphics[width=\linewidth]{position_force}
+	\includegraphics[width=.9\linewidth]{position_force}
 	\caption{Failure detection using end-effector forces}
@@
 \end{figure}
+
+\begin{figure}
+	\centering
+	\begin{subfigure}{.4\linewidth}
+		\includegraphics[width=.98\linewidth]{failure_scenario_1}
+	\end{subfigure}%
+	\begin{subfigure}{.4\linewidth}
+		\includegraphics[width=.98\linewidth]{failure_scenario_2}
+	\end{subfigure}
+	\begin{subfigure}{.4\linewidth}
+		\includegraphics[width=.98\linewidth]{failure_scenario_3}
+	\end{subfigure}%
+	\begin{subfigure}{.4\linewidth}
+		\includegraphics[width=.98\linewidth]{failure_scenario_4}
+	\end{subfigure}
+	\caption{Various Failure Scenarios}
+	\label{fig:failure_scenarios}
+\end{figure}
+
+\section{Discussion}
+\label{sec:discussion}
+The clothing assistance task deals with manipulation of highly deformable clothing article, which inherits complex dynamics.
+Failure can be detected by observing end-effector forces.
+The shape of clothing article keeps on changing during each trail, which affects the task settings.
+We noticed that there can be many failure scenarios such as clothing article gets stuck into the fingers, sleeve getting stuck on the arms, sleeve not entering the arm but entirely missing etc.
+The other reason of failure can be position based DMP system.
+DMP system was initialized by position data while ignoring the orientation of end-effector.
+The orientation was kept same as it was in original trajectory.
 
@@
 A dual arm Baxter robot, soft mannequin, and very thin sleeveless T-shirt were used in the task.
-We have also presented an approach for failure detection using forces being applied on the end-effector of the robot.
+We have also presented an approach for failure detection using forces being applied on end-effector of the robot.
 We have used the Baxter APIs in order to get the forces, which are calculated by Baxter Dynamics Module.
@@
 
-We plan to extend our research to make the approach more robust by adding visual information and force information with DMP system in the future.
+We plan to extend our research to make the approach more robust by adding visual information and force information with DMP system in near future.
 Also, there is a need for designing an adaptive controller for real-time tracking to adapt and detect various failure scenarios.
-Therefore, in the future, a combination of robot vision and force data can provide the better estimation of cloth state.
+DMP system also needs to be improved to incorporate orientation information of end-effector.
+Therefore, in the future, a combination of robot vision and force data can provide better estimation of cloth state.
 

### 2017-02-10 paper/paper.tex
[major] add v3

@@
 % DOI
-\acmDOI{To_be_inserted_after_paper_is_accepted}
+\acmDOI{to_be_inserted_after_paper_is_accepted}
 
@@
 \begin{abstract}
-	The need of robotic clothing assistance in the field of assistive robotics is growing, as it is one of the most basic activities in daily life of elderly and disabled people.
+	The need of robotic clothing assistance in the field of assistive robotics is growing, as it is one of the most basic and essential assistance activities in daily life of elderly and disabled people.
 In this study, we are investigating the applicability of using Dynamic Movement Primitives (DMP) as a task parameterization model for performing clothing assistance task.
 Robotic cloth manipulation task deals with putting a clothing article on both the arms.
-The clothing assistance is a challenging problem since robot must do cooperative manipulation by holding the cloth using both the arms while interacting with non-rigid and highly deformable clothes, and with the assisted person whose posture can vary during assistance.
-The system consists of dual arm Baxter research robot and Microsoft Kinect V2 RGBD sensor for tracking the posture of arms.
-The cloth manipulation is done by Baxter robot which follows trajectory generated by DMP system.
+Robot trajectory varies significantly for various postures and also there can be various failure scenarios while doing cooperative manipulation with non-rigid and highly deformable clothing article.
 We have performed experiments on soft mannequin instead of human.
@@
 Although there has been a significant number of research done in this field, robotic clothing assistance is yet an open field for research.
-Not to mention that it is one of the basic and important assistance activities in daily life of elderly as well as disabled people.
+It is one of the basic and essential assistance activities in daily life of elderly as well as disabled people.
 While rigid object manipulation with robots has mainly relied on precise robot control, deformable objects rather require complex control scheme.
-The clothing assistance is a challenging problem since robot is required to manage two difficulties: (a) robot must do cooperative manipulation by holding cloth using both the arms while interacting with non-rigid and highly deformable cloth and (b) maintain safe human-robot interaction with the assisted person whose posture can vary during assistance.
+Clothing assistance is a challenging problem since robot is required to manage two difficulties: (a) robot must do cooperative manipulation by holding cloth using both the arms while interacting with non-rigid and highly deformable cloth and (b) maintain safe human-robot interaction with the assisted person whose posture can vary during assistance.
 
@@
 \label{sec:related_works}
-There has been a significant number of research done in the field of robotic clothing assistance by using vision system.
+There has been significant research done in the field of robotic clothing assistance by using vision system.
 Klee et al.
@@
 A combination of such techniques is encouraged.
-However, we see that there has been a large gap when compared it to the practical use cases in elderly care.
+However, we see that there has been a large gap when compared to the practical use cases in elderly care.
 The most important point should be learning rate of the task.
@@
 	\caption{Workflow of robotic cloth manipulation task.
-Initially, a demonstration is performed by moving Baxter arms in appropriate trajectory.
+Initially, a kinesthetic demonstration is performed with the robot controlled in gravity compensation mode.
 This demonstration is recorded and parameterized by DMP.
-Later on, posture of the mannequin is changed and accordingly goal parameter of DMP is modified.
+Later on, posture of the mannequin is changed and accordingly start and goal parameter of DMP is modified.
 Now, modified DMP can accommodate new posture.}
@@
 
-\subsection{Robotic Cloth Manipulation using DMP}
+\subsection{Robotic cloth manipulation using DMP}
 \label{sec:system_overview}
@@
 As per the formulation described in section \ref{sec:dmp}, DMP can learn from demonstration.
-Therefore we start by performing a demonstration by holding robot arm as shown in figure \ref{fig:workflow}.
+Therefore we start by performing a kinesthetic demonstration with the robot controlled in gravity compensation mode as shown in figure \ref{fig:workflow}.
 This is referred as ``Teaching Phase'', since in this phase, we are teaching skills to robot to perform the task.
 During the demonstration, pose trajectory of end-effector is recorded using Baxter API and stored in a file.
-The term pose collectively refers to position and orientation.
-Once the demonstration is finished, DMP is initialized using recorded trajectory file.
+The term pose collectively refers to position as cartesian position $p = (p_x, p_y, p_z) \in \mathbb{R}^3$ and orientation as quaternion $q = (q_x, q_y, q_z, q_w) \in \mathbb{R}^4$.
+Once the demonstration is finished, DMP is parameterized using recorded trajectory file.
 This is termed as ``Learn Trajectory'' phase.
-In this phase, recorded trajectory is parameterized by DMP system.
 The parameterized DMP can represent all the characteristics of original trajectory.
@@
 In this way, we have total six DMP systems, which can control both the arms of Baxter robot.
-In ``Testing Phase'', we change the posture of mannequin by lifting arms up or down.
-At this point, we use Kinect Sensor to get the 3D coordinates of arm.
-Before using Kinect Sensor, it is very important to do Kinect-Baxter calibration, so that 3D coordinates are translated from Kinect space to Baxter space.
-We change goal parameter of DMP trajectories by using this information.
+In ``Testing Phase'', we change the posture of mannequin by changing the angle of inclination as shown in figure \ref{fig:accuracy}.
+At this point, we use Kinect Sensor to get the 3D coordinates of wrist and shoulder of mannequin.
+We change start and goal parameter of DMP trajectories by using this information.
 In this way, we have generalized DMP system, which can adapt modified posture referred as ``DMP Generalization''.
+Before using Kinect Sensor, it is extremely important to do Kinect-Baxter calibration, so that 3D coordinates are translated from Kinect space to Baxter space.
+For Kinect-Baxter calibration, we collect a dataset of points observed by Baxter and Kinect.
+Then we use absolute orientation calibration \citep{umeyama1991least} to align the frames of reference.
+
+We have divided the complete trajectory into two parts: (a) The reaching part, which refers to the trajectory starts from home position of robot and ends till hands of mannequin (b) the clothing part, which refers to the trajectory starts from hands of mannequin and reaches upto shoulder nearly.
+The reaching part can be performed through simple position based controller but for the clothing phase, we need to train DMP since this part changes drastically between postures and can be prone to failure.
 
@@
 We use position data to initialize DMP trajectories, which are being used in this task.
-The posture of mannequin is changed by lifting arms up or down.
-At this point, we use Kinect Sensor to get 3D coordinates of arms.
-Now we change goal parameter of DMP trajectories by using this information.
+The posture of mannequin is changed.
+At this point, we use Kinect Sensor to get 3D coordinates of wrist and shoulder of mannequin.
+Now we change start and goal parameter of DMP trajectories by using this information.
 Modified DMP can be acquired by rolling out DMP system as described in section \ref{sec:dmp}.
 
-In this experiment, the initialized DMP was modified to accommodate new posture by changing goal parameter of DMP.
+In this experiment, the initialized DMP was modified to accommodate new posture by changing start and goal parameter of DMP.
 The generated trajectory was then run on Baxter robot as shown in figure \ref{fig:trajectory}.
@@
 The mean of these two categories is calculated and plotted as shown in figure \ref{fig:position_force}.
-This is the average profile over several success and failure trajectories for different postures of the mannequin.
+Force value is the norm of force applied in all three cartesian directions.
+This is the average profile over several \textit{success} and \textit{failure} trajectories for different postures of left arm of mannequin.
 
@@
 The shape of clothing article keeps on changing during each trail, which affects the task settings.
+That is why, a trajectory which was able to preform successfully in the past, doesn't work later sometimes.
 We noticed that there can be many failure scenarios such as clothing article gets stuck into the fingers, sleeve getting stuck on the arms, sleeve not entering the arm but entirely missing etc.
+Proposed failure detection method by using force information can detect failures when clothing article is stuck tightly.
 The other reason of failure can be position based DMP system.
-DMP system was initialized by position data while ignoring the orientation of end-effector.
+Orientation plays a major role in the task however DMP system was initialized by position data while ignoring the orientation of end-effector.
 The orientation was kept same as it was in original trajectory.

### 2017-02-10 paper/images/inclination/inclination_minus.tex
[minor] add v3.0

--- 2017-02-09 paper/images/inclination/inclination.tex
@@
-\documentclass{standalone}
+\documentclass[tikz]{standalone}
 \usepackage{graphicx}
-\usepackage{tikz}
 \usetikzlibrary{shapes.geometric, arrows}
@@
     line/.style = {line width=0.6mm, draw=blue},
-    darrow/.style = {<-, line width=0.6mm, draw=blue},
-    box/.style    = {draw, rectangle, rounded corners, minimum height = 3cm, text centered, text width=5cm, fill=white, font=\Huge\sffamily}
+    box/.style  = {draw, rectangle, rounded corners, minimum height = 2.5cm, text centered, text width=4.5cm, fill=white, font=\Huge\sffamily}
 }
 
-\pgfmathsetmacro{\ex}{0.85}
+\pgfmathsetmacro{\ex}{0.70}
 \pgfmathsetmacro{\ey}{0.60}
@@
 \begin{tikzpicture}
-	\node[anchor=south west,inner sep=0] (image) at (0,0,0) {\includegraphics[width=\linewidth]{mannequin}};
+	\node[anchor=south west,inner sep=0] (image) at (0,0,0) {\includegraphics[width=\linewidth]{down}};
 	\begin{scope}[x={(image.south east)},y={(image.north west)}]
@@
 		\begin{scope}[x={(image.south east)},y={(image.north west)}]
-			\draw[line] (0.30,0.60) -- (\ex,\ey);
-			\draw[line] (0.20,0.25) -- (\ex,\ey);
-			\draw[darrow](\ex,\ey) ++(-152:.2) arc (-152:-180:.2);
-			\draw[to](0.22,0.65) node[box]{Angle of Inclination} to [out=-40,in=200] (0.65,0.55);
+			\draw[line] (0.10,0.60) -- (\ex,\ey);
+			\draw[line] (0.15,0.30) -- (\ex,\ey);
+			\draw[to, draw=blue](\ex,\ey) ++(180:.35) arc (180:208:.35);
+			\draw[to](0.20,0.75) node[box]{Angle of Inclination} to [out=270,in=180] (0.36,0.50);
 		\end{scope}

### 2017-02-10 paper/images/inclination/inclination_plus.tex
[minor] add v3.0

--- 2017-02-10 paper/images/inclination/inclination_minus.tex
@@
-\documentclass[tikz]{standalone}
+\documentclass{standalone}
 \usepackage{graphicx}
+\usepackage{tikz}
 \usetikzlibrary{shapes.geometric, arrows}
@@
     line/.style   = {line width=0.6mm, draw=blue},
+    darrow/.style = {<-, line width=0.6mm, draw=blue},
     box/.style    = {draw, rectangle, rounded corners, minimum height = 2.5cm, text centered, text width=4.5cm, fill=white, font=\Huge\sffamily}
@@
 \begin{tikzpicture}
-	\node[anchor=south west,inner sep=0] (image) at (0,0,0) {\includegraphics[width=\linewidth]{down}};
+	\node[anchor=south west,inner sep=0] (image) at (0,0,0) {\includegraphics[width=\linewidth]{up}};
 	\begin{scope}[x={(image.south east)},y={(image.north west)}]
@@
 			\draw[line] (0.10,0.60) -- (\ex,\ey);
-			\draw[line] (0.15,0.30) -- (\ex,\ey);
-			\draw[to, draw=blue](\ex,\ey) ++(180:.35) arc (180:208:.35);
-			\draw[to](0.20,0.75) node[box]{Angle of Inclination} to [out=270,in=180] (0.36,0.50);
+			\draw[line] (0.10,0.76) -- (\ex,\ey);
+			\draw[to, draw=blue](\ex,\ey) ++(180:.35) arc (180:165.5:.35);
+			\draw[to](0.22,0.45) node[box]{Angle of Inclination} to [out=90,in=180] (0.35,0.65);
 		\end{scope}

### 2017-02-11 paper/paper.tex
[minor] add v3.0
[major] add v4

@@
 In this way, we have total six DMP systems, which can control both the arms of Baxter robot.
-In ``Testing Phase'', we change the posture of mannequin by changing the angle of inclination as shown in figure \ref{fig:accuracy}.
+In ``Testing Phase'', we change the posture of mannequin by changing the angle of inclination as shown in figure \ref{fig:inclination}.
 At this point, we use Kinect Sensor to get the 3D coordinates of wrist and shoulder of mannequin.
@@
 
-We have divided the complete trajectory into two parts: (a) The reaching part, which refers to the trajectory starts from home position of robot and ends till hands of mannequin (b) the clothing part, which refers to the trajectory starts from hands of mannequin and reaches upto shoulder nearly.
+We have divided the complete trajectory into two parts: (a) The reaching part, which refers to the trajectory starts from home position of robot and ends till hands of mannequin (b) the clothing part, which refers to the trajectory starts from hands of mannequin and reaches up to shoulder nearly.
 The reaching part can be performed through simple position based controller but for the clothing phase, we need to train DMP since this part changes drastically between postures and can be prone to failure.
@@
 We defined angle of inclination as the angle between arm of mannequin and horizontal axis.
-The angle of inclination is defined in clockwise direction, hence it is $+ve$ when arms are inclined upward, similarly it is $-ve$ when arms are inclined downward.
-It was changed by keeping arms at different-different height.
+The angle of inclination is defined in clockwise direction, hence it is +ve when arms are inclined upward, similarly it is -ve when arms are inclined downward as shown in figure \ref{fig:inclination}.
+It was changed by keeping arms at various heights.
+The angle of inclination for horizontal  orientation is refereed as 0 degree.
+For each angle of inclination, we performed the experiment 6 times.
+We then changed the angle of inclination by 5 degree step size and followed the same steps as described above.
+We stopped this experiment, once we noticed a huge degradation in success rate, such as success rate close to zero.
 The accuracy measurement is shown in figure \ref{fig:accuracy}.
@@
 	\centering
-	\begin{subfigure}{.35\linewidth}
-		\includegraphics[width=\linewidth]{inclination}
+	\begin{subfigure}{.5\linewidth}
+		\includegraphics[width=.9\linewidth]{inclination_plus}
+	    \caption{Positive angle}
 	\end{subfigure}%
-	\begin{subfigure}{.65\linewidth}
+	\begin{subfigure}{.5\linewidth}
+		\includegraphics[width=.9\linewidth]{inclination_minus}
+	    \caption{Negative angle}
+	\end{subfigure}
+	\caption{Angle of Inclination}
+	\label{fig:inclination}
+\end{figure}
+
+\begin{figure}
+	\centering
 	\includegraphics[width=\linewidth]{success_rate}
-	\end{subfigure}
 	\caption{Accuracy measurement}
@@
 The shape of clothing article keeps on changing during each trail, which affects the task settings.
-That is why, a trajectory which was able to preform successfully in the past, doesn't work later sometimes.
+That is why, a trajectory which was able to preform successfully in the past, does not work later sometimes.
 We noticed that there can be many failure scenarios such as clothing article gets stuck into the fingers, sleeve getting stuck on the arms, sleeve not entering the arm but entirely missing etc.

### 2017-02-20 paper/paper.tex
[minor] add acknowledgement section

@@
 \begin{acks}
-	The authors would also like to thank the anonymous referees for their valuable comments and helpful suggestions.
-The work is supported by the \grantsponsor{GS501100001809}{National Natural Science Foundation of China}{http://dx.doi.org/10.13039/501100001809} under Grant No.:~\grantnum{GS501100001809}{61273304} and~\grantnum[http://www.nnsf.cn/youngscientsts]{GS501100001809}{Young Scientsts' Support Program}.
+	This work was supported in part by the Grant-in-Aid for Scientific Research from Japan Society for the Promotion of Science (No. 16H01749).
 \end{acks}

### 2017-05-17 paper/paper_backup.tex
[major] add double blind paper and review comments

--- 2017-02-20 paper/paper.tex
@@
 % ISBN
-\acmISBN{000-0000-00-000/00/00}
+\acmISBN{1-58113-000-0/00/0010}
 
@@
 \begin{equation}
-	\dot{v}(t) = \frac{\partial}{\partial t} v(t) = \frac{\partial}{\partial t} \frac{\partial}{\partial t} x(t)
+	\dot{v}(t) = \frac{\partial v}{\partial t} = \frac{\partial^2 x}{\partial t^2}
 \end{equation}
@@
 
-To evaluate this experiment, we performed it many times and monitored trajectory generated by DMP system.
+To evaluate this experiment, we performed it 9 times for each angle of inclination and monitored trajectory generated by DMP system.
 We defined angle of inclination as the angle between arm of mannequin and horizontal axis.
@@
 Force value is the norm of force applied in all three cartesian directions.
-This is the average profile over several \textit{success} and \textit{failure} trajectories for different postures of left arm of mannequin.
+This is the average profile over 6 \textit{success} and \textit{failure} trajectories for different postures of left arm of mannequin.
 

### 2017-05-26 double_blind/reviews.tex
[major] add camera ready format

\documentclass{article}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{longtable}
\usepackage[cmex10]{amsmath}
\usepackage[pdftex]{graphicx}
\usepackage[margin=0.75in]{geometry}

\begin{document}
\begin{table}
	\centering
	\caption{Review comments and response of the paper submitted to AIR 2017}
	\begin{tabular}{ |c|p{9cm}|p{5cm}| }
		\hline
		\textbf{Reviewer}  & \textbf{Comment}                                                                                                                                                                                                                                                                                                                                                                                                           & \textbf{Response}                                                                                                                           \\ \hline\hline
		\multirow{4}{*}{1} & Please explain the terms of equations 1 and 2 clearly. If you open the brackets of equation 1 then Kg and -Kg will cancel? This means that goal position does not have any effect? The damping term is scaled by the scaling term. Is it a variable variable K and D case? If equation 1 is for a dynamical system defined by F=Mass X accn then mass given by the scaling term cannot be a variable (must be a constant). & \textit{More description added.}                                                                                                            \\ \cline{2-3}
		                   & AS only three coordinates (x,y,z) of the wrist are considered does the wrist roll,pitch and yaw have no part in the orientation of the griper for holding the cloth?                                                                                                                                                                                                                                                       & \textit{Orientation of the end-effector is not considered as a part of DMP system and                                                       
		kept same as it was at the time of ``Teaching Phase''. This description has been added.}  \\ \cline{2-3}
		                   & Angle of inclination is defined in 2D and not as a 3D angle, is it sufficient?                                                                                                                                                                                                                                                                                                                                             & \textit{More description added.}                                                                                                            \\ \cline{2-3}
		                   & Why is the trajectory in Fig 4 not smooth? I would imagine that human trajectories would be smooth?                                                                                                                                                                                                                                                                                                                        & \textit{Disagree. Human demonstrations need not be smooth especially when the task setting is complicated. Hence no changes has been done.} \\ \hline
		\multirow{7}{*}{2} & The contribution of the paper need to be stated more explicitly                                                                                                                                                                                                                                                                                                                                                            & \textit{More description added.}                                                                                                            \\ \cline{2-3}
		                   & In Eqn(1), K was considered as spring constant. However, the same constant is used as coefficient for non- linear function. Need to clarify this                                                                                                                                                                                                                                                                           & \textit{K is not spring constant but it acts like spring constant. This description has been added.}                                                                                                                          \\ \cline{2-3}
		                   & Para next to Equ 5 is not clear "In other words, we want to setup a system which can follow specified path. The forcing term can be redefined as:"                                                                                                                                                                                                                                                                         & \textit{Sentence rephrased.}                                                                                                                \\ \cline{2-3}
		                   & Modified DMP has not been discussed anywhere in the paper except in figure 3.                                                                                                                                                                                                                                                                                                                                              & \textit{More description added.}                                                                                                            \\ \cline{2-3}
		                   & The flow in figure 3 is misleading. Is it correct to have DMP generalization after Testing Phase?                                                                                                                                                                                                                                                                                                                          & \textit{Testing and DMP generalization are swapped.}                                                                                        \\ \cline{2-3}
		                   & In 4.1, it was mentioned as "At this point, we use Kinect Sensor to get 3D coordinates of wrist and shoulder of mannequin." how it could be possible without using any markers to recognize wrist and shoulder of mannequin.                                                                                                                                                                                               & \textit{More description added.}                                                                                                            \\ \cline{2-3}
		                   & In figure 4, it would have been meaningful if the reference coordinate frame is shown.                                                                                                                                                                                                                                                                                                                                     & \textit{Reference frame added.}                                                                                                             \\ \hline
		\multirow{3}{*}{3} & End-effector forces may be shown through a diagram or through some description.                                                                                                                                                                                                                                                                                                                                            & \textit{Description added.}                                                                                                                 \\ \cline{2-3}
		                   & Figure 5 is referred before figure 4. Please make the necessary changes, if required.                                                                                                                                                                                                                                                                                                                                      & \textit{Fixed.}                                                                                                                             \\ \cline{2-3}
		                   & Figure 4 and 7 needs more clarity on the significance of the plots. Little description can be added in the captions itself.                                                                                                                                                                                                                                                                                                & \textit{Description added.}                                                                                                                 \\ \hline
	\end{tabular}
\end{table}

%\section*{Other comments such as Typos}
%\begin{itemize}
%	\item ``DMP can learn complex task from the demonstration [7, 8, 16] and thus reduce the manual efforts to design a controller from scratch or to fine-tune various
%	      controller parameters. We choose dual arm Baxter robot in this research as'' Repeated twice.
%	\item[] \textit{Fixed.}
%	      
%	\item Equ (6) has double negative
%	\item[] \textit{Fixed.}
%	      
%	\item Section 5, line 5 typo 'perform'
%	\item[] \textit{Fixed.}
%	      
%	\item Formatting need to be checked
%	\item[] \textit{We are following Latex Template.}
%\end{itemize}
\end{document}

### 2017-05-26 paper/images/flowchart/flowchart_conf.tex
[minor] image text changed to sans-serif
[major] add camera ready format

@@
 
+% set sans-serif http://tex.stackexchange.com/a/4888
+\tikzstyle{every picture}+=[font=\sffamily]
 \def \scaling {3.5cm}
@@
 
-	\node[north right = of dmp, basic box = green, header = Testing Phase] (testing) {
+	\node[north right = of dmp, basic box = red, header = DMP Generalization] (generalization){
+		%DMP Trajectory\\
+		\includegraphics[height=\scaling]{dmp_mod}
+	};
+
+	\node[north right = of generalization, basic box = green, header = Testing Phase] (testing) {
 		%Modified Posture\\
@@
 
-	\node[north right = of testing, basic box = red, header = DMP Generalization] (generalization){
-		%DMP Trajectory\\
-		\includegraphics[height=\scaling]{dmp_mod}
-	};
-
 	\path[ultra thick, blue,  ->](teaching) edge[->] (dmp);
-	\path[ultra thick, orange,->](dmp) edge[->] (testing);
-	\path[ultra thick, green, ->](testing) edge[->] (generalization);
+	\path[ultra thick, orange,->](dmp) edge[->] (generalization);
+	\path[ultra thick, green, ->](generalization) edge[->] (testing);
 \end{tikzpicture}

### 2017-05-26 paper/paper.tex
[major] add camera ready format

@@
 Primitives}
+
+%\author{Anonymous Author 1}
+%\affiliation{}
+%\email{anonymous_author_1@email.com}
+
+%\author{Anonymous Author 2}
+%\affiliation{}
+%\email{anonymous_author_2@email.com}
+
+%\author{Anonymous Author 3}
+%\affiliation{}
+%\email{anonymous_author_3@email.com}
 
@@
 While rigid object manipulation with robots has mainly relied on precise robot control, deformable objects rather require complex control scheme.
-Clothing assistance is a challenging problem since robot is required to manage two difficulties: (a) robot must do cooperative manipulation by holding cloth using both the arms while interacting with non-rigid and highly deformable cloth and (b) maintain safe human-robot interaction with the assisted person whose posture can vary during assistance.
+Clothing assistance is a challenging problem since robot is required to manage two difficulties: (a) robot must do cooperative manipulation by holding clothing article using both the arms while interacting with non-rigid and highly deformable clothing article and (b) maintain safe human-robot interaction with the assisted person whose posture can vary during assistance.
 
+Trajectory variability for clothing assistance is large for different environmental conditions.
+We need to parametrize the task efficiently so that generalization can be acheived quickly.
 In this study, we are investigating the applicability of using Dynamic Movement Primitives (DMP) as a task parameterization model for performing clothing assistance task.
@@
 In Section \ref{sec:method}, we introduce mathematical formulation about DMP followed by describing proposed method and its workflow.
-Section \ref{sec:experiments} deals with details of various experiments performed and their results.
+Section \ref{sec:experiments} deals with details of various experiments performed and corresponding results.
 The discussion about experiments is presented in section \ref{sec:discussion}.
-Finally we conclude in section \ref{sec:conclusions} with some future directions.
+Finally we conclude in section \ref{sec:conclusions} with future directions.
 
@@
 \cite{klee2015personalized} worked on personalized assistance for dressing a user.
-The robot request user to move towards robot, monitors motion using vision module and puts a hat on user once users is reachable by the robot.
-They haven't considered human and cloth interaction.
+The robot requests user to move towards robot, monitors motion using vision module and puts a hat on user once user is reachable by the robot.
+They haven't considered human and clothing article interaction.
 Yamazaki et al.
-\cite{yamazaki2013method, yamazaki2014bottom}  worked on bottom dressing by a life-sized humanoid robot, where they recognize the cloth state by using optical flow on the images acquired from a single camera.
+\cite{yamazaki2013method, yamazaki2014bottom}  worked on bottom dressing by a life-sized humanoid robot, where they recognize the cloth state by using optical flow on images acquired from a single camera.
 They did not handle large occlusions.
@@
 \cite{kapusta2016data} is focused towards designing a controller inspired from data-driven haptic perception.
-They classified the forces measured at robot's end effector by using hidden Markov models and performed clothing task using hospital gown.
+They classified the forces measured at robot's end-effector by using hidden Markov models and performed clothing task using hospital gown.
 Their focus was to classify force data for haptic perception with high accuracy.
@@
 
-The problem of robotic clothing assistance not only depends on tracking cloth dynamics but also motor skills required to perform the task.
+The problem of robotic clothing assistance not only depends on tracking cloth dynamics but also on motor skills required to perform the task.
 A combination of such techniques is encouraged.
@@
 The problem of putting sleeveless T-shirt into the arms of mannequin is close to the practical use case.
-Therefore, we are putting our efforts to solve it.
+Therefore, we are putting our efforts to solve it by investigating the generalization ability of DMP to varying postures of mannequin.
 
@@
 This demonstration is recorded and parameterized by DMP.
-Later on, posture of the mannequin is changed and accordingly start and goal parameter of DMP is modified.
-Now, modified DMP can accommodate new posture.}
+Later on, posture of the mannequin is changed.
+Accordingly start and goal parameter of initial DMP are modified.
+Now, the modified DMP can accommodate new posture.}
 	\label{fig:workflow}
@@
 Robotic cloth manipulation task deals with putting a clothing article on both the arms.
-We are using DMP framework to learn this complex task from demonstration and thus reduce the manual efforts to design the controller from scratch.
-We choose dual arm Baxter robot in this research.
+We have chosen DMP framework to learn this complex task from demonstration and and used a dual arm Baxter robot in this research.
 Following subsections explain about underlying DMP framework followed by the proposed method.
@@
 Dynamic Movement Primitives (DMP) aims at designing controller for learning and generalization of motor skills by learning from demonstration \cite{ijspeert2003learning}.
-The controller is based on nonlinear dynamical system and use locally weighted regression techniques to learn complex, discrete or rhythmic, movements demonstrated by a human subject \cite{ijspeert2002movement}.
+The controller is based on nonlinear dynamical system and uses Locally Weighted Regression (LWR) techniques to learn complex, discrete or rhythmic movements demonstrated by a human subject \cite{ijspeert2002movement}.
 The controller can be considered to be discrete or rhythmic pattern generator which can replay and modulate the learned movements, while being robust against perturbations.
@@
 
-The term $x$ and $v$ are position and velocity of the system respectively, $x_0$ and $g$ are start and goal position, $\tau$ is a scaling term, $K$ is spring constant and $D$ is damping factor.
+The term $x$ and $v$ are position and velocity of the system respectively, $x_0$ and $g$ are start and goal position, $\tau$ is a scaling term, $K$ acts like spring constant and $D$ is damping factor chosen in a way such that system is critically damped.
+The term $K (g - x_0) s$ is necessary for avoiding sudden jump at the beginning of a movement.
 The nonlinear function $f$, which is also called as forcing term is a non-linear function to be learned to allow complex movements.
@@
 Our goal is to design a forcing function that can learn from demonstration and allows us to scale the movement defined by goal state $g$.
-In other words, we want to setup a system which can follow specified path.
+So that the system can follow a specified path.
 The forcing term can be redefined as:
@@
 \begin{equation}
-	f_{target}(s) = \frac{D v + \tau \dot{v}}{K} - - (g - x) +  (g - x_0) s
+	f_{target}(s) = \frac{D v + \tau \dot{v}}{K} - (g - x) +  (g - x_0) s
 \end{equation}
@@
 \begin{equation}
-	\dot{v}(t) = \frac{\partial}{\partial t} v(t) = \frac{\partial}{\partial t} \frac{\partial}{\partial t} x(t)
+	\dot{v}(t) = \frac{\partial v}{\partial t} = \frac{\partial^2 x}{\partial t^2}
 \end{equation}
 
-The forcing function [\ref{eq:forcing_func}] is comprised of weighted summation of Gaussian that are going to be activated as system converges to goal as shown in figure \ref{fig:psi_activations}.
+The forcing function in eq.
+(\ref{eq:forcing_func}) is comprised of weighted summation of Gaussian that are going to be activated as system converges to goal as shown in figure \ref{fig:psi_activations}.
 We want that forcing function matches the desired trajectory.
@@
 This ends by calculating weight parameters across Gaussians.
-Optimization methods such as locally weighted regression \cite{vijayakumar2000locally} can be used, so that forcing function matches desired trajectory.
+Optimization methods such as LWR \cite{vijayakumar2000locally} can be used, so that forcing function matches desired trajectory.
 This way DMP can be made to imitate desired path \cite{pastor2009learning}.
@@
 In this way, we have total six DMP systems, which can control both the arms of Baxter robot.
+The orientation of the end-effector is not considered as a part of DMP system and kept same as it was at the time of ``Teaching Phase''.
 In ``Testing Phase'', we change the posture of mannequin by changing the angle of inclination as shown in figure \ref{fig:inclination}.
-At this point, we use Kinect Sensor to get the 3D coordinates of wrist and shoulder of mannequin.
-We change start and goal parameter of DMP trajectories by using this information.
-In this way, we have generalized DMP system, which can adapt modified posture referred as ``DMP Generalization''.
+At this point, we use Kinect Sensor to get the 3D coordinates of wrist and shoulder of mannequin by clicking on real-time point cloud acquired using Kinect Sensor.
+We change start and goal parameter of DMP system by using this information.
+In this way, we have modified DMP system, which can adapt modified posture referred as ``DMP Generalization''.
 Before using Kinect Sensor, it is extremely important to do Kinect-Baxter calibration, so that 3D coordinates are translated from Kinect space to Baxter space.
@@
 
-We have divided the complete trajectory into two parts: (a) The reaching part, which refers to the trajectory starts from home position of robot and ends till hands of mannequin (b) the clothing part, which refers to the trajectory starts from hands of mannequin and reaches up to shoulder nearly.
-The reaching part can be performed through simple position based controller but for the clothing phase, we need to train DMP since this part changes drastically between postures and can be prone to failure.
+We have divided the complete trajectory into two parts: (a) The reaching part, which refers to the trajectory starts from home position of robot and ends till fingers of mannequin (b) the clothing part, which refers to the trajectory starts from fingers of mannequin and reaches up to shoulder nearly.
+The reaching part can be performed through simple position based controller but for the clothing part, we need to use DMP system since this part changes drastically between postures and can be prone to failures.
 
 \begin{figure}
-	\includegraphics[width=\linewidth]{all_traj}
-	\caption{Left arm trajectory of Baxter}
-	\label{fig:trajectory}
+	\centering
+	\begin{subfigure}{.5\linewidth}
+		\includegraphics[width=.9\linewidth]{inclination_plus}
+		\caption{Positive angle}
+	\end{subfigure}%
+	\begin{subfigure}{.5\linewidth}
+		\includegraphics[width=.9\linewidth]{inclination_minus}
+		\caption{Negative angle}
+	\end{subfigure}
+	\caption{Angle of Inclination measures the bending of arms w.r.t. horizontal line in two-dimensional space.}
+	\label{fig:inclination}
 \end{figure}
@@
 We choose soft mannequin instead of a human for this experiment.
-Both the arms of mannequin are open and given support by a metallic stand, to avoid falling down the arms.
+Both the arms of mannequin are open and given support by a metallic stand, to avoid falling down.
 Mannequin is positioned in such a way so that it resides within limits of workspace of Baxter robot.
@@
 The aim of this experiment is to put sleeveless T-shirt on both the arms of mannequin by using DMP system.
-We use position data to initialize DMP trajectories, which are being used in this task.
+We use position data to initialize DMP system, which is being used in this task.
 The posture of mannequin is changed.
 At this point, we use Kinect Sensor to get 3D coordinates of wrist and shoulder of mannequin.
-Now we change start and goal parameter of DMP trajectories by using this information.
-Modified DMP can be acquired by rolling out DMP system as described in section \ref{sec:dmp}.
+Now we change start and goal parameter of initial DMP system by using this information.
+Modified DMP can be acquired by rolling out initial DMP system as described in section \ref{sec:dmp}.
 
-In this experiment, the initialized DMP was modified to accommodate new posture by changing start and goal parameter of DMP.
-The generated trajectory was then run on Baxter robot as shown in figure \ref{fig:trajectory}.
-Newly generated DMP trajectory (shown in red color) was not only found well suited and capable of performing clothing task but also smooth compared to original trajectory (shown in blue color).
+In this experiment, the DMP was modified to accommodate new posture by changing start and goal parameter of initial DMP system.
+The generated trajectory from modified DMP system was then run on Baxter robot as shown in figure \ref{fig:trajectory}.
+Newly generated DMP trajectory (shown in red color) was not only found well suited and capable of performing clothing task but also smoother compared to demonstrated trajectory (shown in blue color).
 A video demonstration of this experiment can be seen at YouTube\footnote{\url{http://youtu.be/Rb2JePazJjk}}.
 
-To evaluate this experiment, we performed it many times and monitored trajectory generated by DMP system.
+To evaluate this experiment, we performed it 9 times for each angle of inclination and monitored trajectory generated by DMP system.
 We defined angle of inclination as the angle between arm of mannequin and horizontal axis.
@@
 \begin{figure}
-	\centering
-	\begin{subfigure}{.5\linewidth}
-		\includegraphics[width=.9\linewidth]{inclination_plus}
-	    \caption{Positive angle}
-	\end{subfigure}%
-	\begin{subfigure}{.5\linewidth}
-		\includegraphics[width=.9\linewidth]{inclination_minus}
-	    \caption{Negative angle}
-	\end{subfigure}
-	\caption{Angle of Inclination}
-	\label{fig:inclination}
+	\includegraphics[width=\linewidth]{all_traj}
+	\caption{Left arm trajectory of Baxter.
+The unit of axis is in meter.
+The demonstration trajectory is noisy due to sensor noise.
+The fluctuations in trajectory are dominating across y axis.
+However y axis is least spread among all three axis.}
+	\label{fig:trajectory}
 \end{figure}
@@
 This experiment is designed to deal with failure cases.
-There can be many failure cases during the task, such as clothing article gets stuck into the fingers, sleeve getting stuck on the arms, sleeve not entering the arm but entirely missing etc, as shown in figure \ref{fig:failure_scenarios}.
-In this experiment, we are using forces being applied on the end-effector of Baxter robot to detect failure scenario.
+There can be many failure cases during the task, such as clothing article gets stuck into the fingers, sleeve getting stuck on the arms, sleeve is not entering in the arm but entirely missing etc, as shown in figure \ref{fig:failure_scenarios}.
+In this experiment, we are using forces being applied on the end-effector of Baxter robot to detect failure scenarios.
 Appropriate action can be taken once the failure is detected.
@@
 Trajectories were monitored and categorized into two \textit{success} and \textit{failure}.
-The mean of these two categories is calculated and plotted as shown in figure \ref{fig:position_force}.
+The mean of these two categories is calculated individually and plotted as shown in figure \ref{fig:position_force}.
 Force value is the norm of force applied in all three cartesian directions.
-This is the average profile over several \textit{success} and \textit{failure} trajectories for different postures of left arm of mannequin.
+This is the average profile over 6 \textit{success} and \textit{failure} trajectories for different postures of left arm of mannequin.
 
 It is clearly visible from the figure \ref{fig:position_force} that the applied forces are very different in nature in both the cases.
-Both of these forces are increasing from the beginning, however, forces in case of \textit{failure} are much higher than that of \textit{success}.
-Hence one can easily differentiate and detect the failure by using this information.
+Both of these forces start increasing from the beginning.
+However, forces in case of \textit{failure} are much higher than that of \textit{success}.
+Hence one can easily differentiate and detect failures by using this information.
 
@@
 	\includegraphics[width=.9\linewidth]{position_force}
-	\caption{Failure detection using end-effector forces}
+	\caption{Failure detection using end-effector forces recorded during the task.
+Each trajectory is computed by calculating the mean.
+The force value is norm of force applied in all three cartesian directions.}
 	\label{fig:position_force}
@@
 		\includegraphics[width=.98\linewidth]{failure_scenario_1}
+		%\caption{}
 	\end{subfigure}%
@@
 		\includegraphics[width=.98\linewidth]{failure_scenario_2}
+		%\caption{}
 	\end{subfigure}
@@
 		\includegraphics[width=.98\linewidth]{failure_scenario_3}
+		%\caption{}
 	\end{subfigure}%
@@
 		\includegraphics[width=.98\linewidth]{failure_scenario_4}
+		%\caption{}
 	\end{subfigure}
-	\caption{Various Failure Scenarios}
+	\caption{Various failure scenarios showing how a clothing article is difficult to manipulate because of inherent non-rigid and flexible nature.}
 	\label{fig:failure_scenarios}
@@
 The shape of clothing article keeps on changing during each trail, which affects the task settings.
-That is why, a trajectory which was able to preform successfully in the past, does not work later sometimes.
-We noticed that there can be many failure scenarios such as clothing article gets stuck into the fingers, sleeve getting stuck on the arms, sleeve not entering the arm but entirely missing etc.
+That is why, a trajectory which was able to perform the task successfully, may not work later.
+We noticed that there can be many failure scenarios such as clothing article gets stuck into the fingers, sleeve is getting stuck on the arms, sleeve is not entering in the arm and entirely missing etc.
 Proposed failure detection method by using force information can detect failures when clothing article is stuck tightly.
-The other reason of failure can be position based DMP system.
-Orientation plays a major role in the task however DMP system was initialized by position data while ignoring the orientation of end-effector.
-The orientation was kept same as it was in original trajectory.
+The other reason of failure can reside in position based DMP system.
+The orientation plays a major role in this task, however DMP system was initialized by position data while ignoring the orientation of end-effector.
+The orientation was kept same as it was in demonstrated trajectory.
 
@@
 
-We plan to extend our research to make the approach more robust by adding visual information and force information with DMP system in near future.
-Also, there is a need for designing an adaptive controller for real-time tracking to adapt and detect various failure scenarios.
+We plan to extend our research to make the approach more robust by adding visual information and force information with DMP system in future.
+Also, there is a need for designing an adaptive controller for real-time tracking of mannequin to adapt and detect various failure scenarios.
 DMP system also needs to be improved to incorporate orientation information of end-effector.
-Therefore, in the future, a combination of robot vision and force data can provide better estimation of cloth state.
+Therefore, in the future, a combination of robot vision and force data can provide better estimation of cloth state for the task.
 

### 2017-05-26 paper/images/trajectories/all_traj.py

@@ -3,6 +3,20 @@ import numpy as np
 import matplotlib as mpl
 import matplotlib.pyplot as plt
 from mpl_toolkits.mplot3d import Axes3D
+from matplotlib.patches import FancyArrowPatch
+from mpl_toolkits.mplot3d import proj3d
+import matplotlib.ticker as ticker
+
+class Arrow3D(FancyArrowPatch):
+    def __init__(self, xs, ys, zs, *args, **kwargs):
+        FancyArrowPatch.__init__(self, (0, 0), (0, 0), *args, **kwargs)
+        self._verts3d = xs, ys, zs
+
+    def draw(self, renderer):
+        xs3d, ys3d, zs3d = self._verts3d
+        xs, ys, zs = proj3d.proj_transform(xs3d, ys3d, zs3d, renderer.M)
+        self.set_positions((xs[0], ys[0]), (xs[1], ys[1]))
+        FancyArrowPatch.draw(self, renderer)
 
 # define index for plotting
 time=0
@@ -24,18 +38,52 @@ fig = plt.figure()
 ax = fig.gca(projection='3d')
 ax.plot( org_tra[:, poselinear_left_x], 
          org_tra[:, poselinear_left_y], 
-         org_tra[:, poselinear_left_z], label='Original', c='b', lw=1)
+         org_tra[:, poselinear_left_z], label='Demonstration', c='b', lw=1)
 ax.plot( org_dmp[:, poselinear_left_x], 
          org_dmp[:, poselinear_left_y], 
-         org_dmp[:, poselinear_left_z], label='DMP', c='g')
+         org_dmp[:, poselinear_left_z], label='Initial DMP', c='g')
 ax.plot( mod_dmp[:, poselinear_left_x], 
          mod_dmp[:, poselinear_left_y], 
          mod_dmp[:, poselinear_left_z], label='Modified DMP', c='r')
 
+start_x=0.50; x_width=0.10
+start_y=0.03; y_width=0.04
+start_z=-0.1; z_width=0.10
+
+a = Arrow3D([start_x-0.01, start_x + x_width], [start_y, start_y], [start_z, start_z], mutation_scale=15, lw=1, arrowstyle="->")
[…]

### 2017-05-26 paper/images/trajectories/dmp_init.py

@@ -24,10 +24,10 @@ fig = plt.figure()
 ax = fig.gca(projection='3d')
 ax.plot( org_tra[:, poselinear_left_x], 
          org_tra[:, poselinear_left_y], 
-         org_tra[:, poselinear_left_z], label='Original', c='b', lw=1)
+         org_tra[:, poselinear_left_z], label='Demonstration', c='b', lw=1)
 ax.plot( org_dmp[:, poselinear_left_x], 
          org_dmp[:, poselinear_left_y], 
-         org_dmp[:, poselinear_left_z], label='DMP', c='g')
+         org_dmp[:, poselinear_left_z], label='Initial DMP', c='g')
 #ax.plot( mod_dmp[:, poselinear_left_x], 
 #         mod_dmp[:, poselinear_left_y], 
 #         mod_dmp[:, poselinear_left_z], label='New DMP', c='r')

### 2017-05-26 paper/images/trajectories/dmp_mod.py

@@ -27,7 +27,7 @@ ax = fig.gca(projection='3d')
 #         org_tra[:, poselinear_left_z], label='Original', c='b', lw=1)
 ax.plot( org_dmp[:, poselinear_left_x], 
          org_dmp[:, poselinear_left_y], 
-         org_dmp[:, poselinear_left_z], label='DMP', c='g')
+         org_dmp[:, poselinear_left_z], label='Initial DMP', c='g')
 ax.plot( mod_dmp[:, poselinear_left_x], 
          mod_dmp[:, poselinear_left_y], 
          mod_dmp[:, poselinear_left_z], label='Modified DMP', c='r')

### 2017-05-27 double_blind/reviews.tex
[major] add comments from sensei

@@
 		                   & Angle of inclination is defined in 2D and not as a 3D angle, is it sufficient?
-& \textit{More description added.}                                                                                                            \\ \cline{2-3}
+& \textit{Agree that 2D angle is not sufficient.
+However in this study we considered the adaptability to 2D.
+Caption of the figure was modified accordingly.}                                                                                                            \\ \cline{2-3}
 		                   & Why is the trajectory in Fig 4 not smooth?
@@
 		                   & Modified DMP has not been discussed anywhere in the paper except in figure 3.
-& \textit{More description added.}                                                                                                            \\ \cline{2-3}
+& \textit{It seems that the reviewer was getting confused with ``Modified'' keyword.
+Hence a new keyword ``Initial DMP'' is introduced.
+Now, the paper contains ``Initial DMP'' and ``Modified DMP''.
+This has been updated in the paper.}                                                                                                            \\ \cline{2-3}
 		                   & The flow in figure 3 is misleading.
@@
 		\multirow{3}{*}{3} & End-effector forces may be shown through a diagram or through some description.
-& \textit{Description added.}                                                                                                                 \\ \cline{2-3}
+& \textit{Caption of the figure was modified accordingly.}                                                                                                                 \\ \cline{2-3}
 		                   & Figure 5 is referred before figure 4.

### 2017-05-27 paper/paper.tex
[major] add comments from sensei

@@
 \author{Ravi P. Joshi}
-\authornote{Ravi P. Joshi is with Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Fukuoka, Japan}
+\authornote{Ravi P. Joshi is with Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Kitakyushu, Japan}
 \affiliation{}
@@
 \author{Nishanth Koganti}
-\authornote{Nishanth Koganti is with Graduate School of Information Science, Nara Institute of Science and Technology, Nara, Japan and Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Fukuoka, Japan}
+\authornote{Nishanth Koganti is with Graduate School of Information Science, Nara Institute of Science and Technology, Nara, Japan and Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Kitakyushu, Japan}
 \affiliation{}
@@
 \author{Tomohiro Shibata}
-\authornote{Tomohiro Shibata is with Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Fukuoka, Japan}
+\authornote{Tomohiro Shibata is with Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Kitakyushu, Japan}
 \affiliation{}
@@
 The idea of using DMP is inspired by the fact that DMP can learn complex task from the demonstration \cite{ijspeert2003learning, schaal2006dynamic, ijspeert2013dynamical} and thus reduce the manual efforts to design a controller from scratch or to fine-tune various controller parameters.
-We choose dual arm Baxter robot in this research as it is safe and flexible by design \cite{fitzgerald2013developing}.
+We choose dual arm Baxter robot (Rethink robotics) in this research as it is safe and flexible by design \cite{fitzgerald2013developing}.
 

### 2017-06-16 presentation/presentation.tex
[major] add presentation

\documentclass[aspectratio=43,11pt,xcolor={dvipsnames}]{beamer}
\usetheme{Madrid}
\usecolortheme{seahorse}
\usefonttheme{serif}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algpseudocode}
\hypersetup{pdfpagemode=FullScreen}
\usepackage{calc}
\usepackage[normalem]{ulem}% to striketrhourhg text
\usepackage{subcaption}
\usepackage{caption}
\captionsetup[figure]{labelformat=empty}% we don't need 'Figure' lable
\usepackage{smartdiagram}
\usesmartdiagramlibrary{additions}

\usepackage[style=verbose,backend=bibtex]{biblatex}
\renewcommand*{\bibfont}{\tiny}%font size for reference slide
\addbibresource{bibfile.bib}

%\setbeamerfont{author}{size=\footcitesize}
%\setbeamerfont{institute}{size=\tiny}
\setbeamertemplate{navigation symbols}{}
\renewcommand{\footnotesize}{\tiny}

\title[AIR 2017]{Robotic cloth manipulation for clothing assistance task using Dynamic Movement Primitives}
\author[Ravi P. Joshi]{Ravi P. Joshi$^a$, Nishanth Koganti$^{a,b}$, and Tomohiro Shibata$^a$}
\institute[]{\tiny{$^a$ Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Kitakyushu, Japan\\$^b$ Graduate School of Information Science, Nara Institute of Science and Technology, Nara, Japan}}

\date[]{{June 28, 2017}}
%\date[]{}

% all the graphics are placed inside images folder
\graphicspath{{./images/}}

\titlegraphic{\includegraphics[scale=0.08]{kyutech} \hskip1cm \includegraphics[scale=0.08]{naist}}

%src: https://tex.stackexchange.com/a/248147
\defbeamertemplate{title page}{noinstitute}[1][]
{
  \vbox{}
  \vfill
  \begingroup
    \centering
    \vskip3em\par
    \begin{beamercolorbox}[sep=4pt,center,#1]{title}
      \usebeamerfont{title}\inserttitle\par%
      \ifx\insertsubtitle\@empty%
      \else%
        \vskip0.1em%
        {\usebeamerfont{subtitle}\usebeamercolor[fg]{subtitle}\insertsubtitle\par}%
      \fi%     
    \end{beamercolorbox}%
    \vskip0em\par
    \begin{beamercolorbox}[sep=8pt,center,#1]{author}
      \usebeamerfont{author}\insertauthor
    \end{beamercolorbox}
    \begin{beamercolorbox}[sep=8pt,center,#1]{institute}
      \usebeamerfont{date}\insertinstitute
    \end{beamercolorbox}\vskip0.1em
    \begin{beamercolorbox}[sep=8pt,center,#1]{date}
      \usebeamerfont{date}\insertdate
    \end{beamercolorbox}\vskip0.1em
    {\usebeamercolor[fg]{titlegraphic}\inserttitlegraphic\par}
  \endgroup
  \vfill
}

\makeatletter
\setbeamertemplate{title page}[noinstitute][colsep=-4bp,rounded=true,shadow=\beamer@themerounded@shadow]
\makeatother

\begin{document}
{
  \usebackgroundtemplate{\includegraphics[width=\paperwidth]{background.pdf}}
  \setbeamertemplate{footline}{} 
  \begin{frame}
    \titlepage
  \end{frame}
}
\addtocounter{framenumber}{-1}

%\begin{frame}[noframenumbering]
%	\titlepage
%\end{frame}

\begin{frame}[noframenumbering]{Outline}
	\tableofcontents
\end{frame}

\section{Introduction}
\begin{frame}{Introduction}
	\linespread{1.6}

	\begin{itemize}
		\item Clothing assistance is a basic and important assistance activity in the daily life of the elderly and disabled people
		\item Need of robotic clothing assistance is growing
	\end{itemize}

	\vskip 1em
	\begin{block}{Major challenges involved}
		\begin{itemize}
			\item Close interaction of the robot with non-rigid clothing article
			\item Safe human-robot interaction
			\item Accurate estimation of human-cloth relationship
		\end{itemize}
	\end{block}
\end{frame}

\section{Related Works}
\begin{frame}{Related Works}

	\vskip -1em
	\begin{columns}[t]
		\begin{column}{0.5\textwidth}
			Towner \textit{et al.}\footnotemark, ~Identifying and manipulating clothing article by dual-arm robot
			{\scriptsize
				\begin{itemize}
					\item[\color{green}{\checkmark}] Used Hidden Markov Model for tracking
					\item[\color{green}{\checkmark}] Triangulated mesh model for simulating clothing article
					\item[\color{red}{$\times$}] Simple manipulations such as gripping using one arm only
				\end{itemize}
			}
			\vskip 0.5em
			\centering{
				\includegraphics[height=2.5cm]{towner_2011}
			}
		\end{column}

		\begin{column}{0.5\textwidth}
			Tamei \textit{et al.}\footnotemark, ~Clothing assistance with dual-arm robot
			{\scriptsize
				\begin{itemize}
					\item[\color{green}{\checkmark}] Used Reinforcement
					      learning (RL)
					\item[\color{green}{\checkmark}] Topology coordinates for human and cloth extremities relationship
					\item[\color{red}{$\times$}] Limited generalization capability for new postures
				\end{itemize}
			}
			\vskip 0.5em
			\centering{
				\includegraphics[height=2.5cm]{tamei_2011}
			}
		\end{column}
	\end{columns}

	\addtocounter{footnote}{-1}
	\footcitetext{cusumano2011bringing}
	\stepcounter{footnote}
	\footcitetext{tamei2011reinforcement}
\end{frame}

\section{Dynamic Movement Primitives}
\begin{frame}{Dynamic Movement Primitives (DMP)}
	%\linespread{1.2}

	\begin{exampleblock}{DMP in a nutshell}
		\begin{itemize}
			\item It is used for generating a control signal to guide the real system\footnotemark
			\item It can represent \textit{nonlinear} motion with a set of differential equations
		\end{itemize}
	\end{exampleblock}

	%	We start with point attractor dynamics\footcite{ijspeert2002movement} \hskip1em $\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y})$

	%	\vskip -1em
	%	\begin{equation}
	%		\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y})
	%		\label{eq:attractor}
	%	\end{equation}
	%	\vskip -0.5em

	%	\vskip 1em
	%	Now add a forcing term $f$ on eq(\ref{eq:attractor}) that will let us to modify this trajectory
	The system is defined as
	\vskip -1em
	\begin{equation}
		\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y}) + f
		\label{eq:attractor_with_f}
	\end{equation}
	%\vskip -0.5em
	{\small
		where:
		\vskip -0.6em
		\begin{itemize}
			\itemsep-0.2em
			\item $y$ is system state and $g$ is goal state
			\item $\alpha$ and $\beta$ are gain terms
			\item $f$ is nonlinear function defined over time
		\end{itemize}
	}

	\begin{exampleblock}{}
		$f$ is a function of \textit{canonical system}, denoted by $x$ as $\dot{x} = -\alpha_x x$
	\end{exampleblock}

	\footcitetext{schaal2006dynamic}
\end{frame}

\begin{frame}{Forcing function $f$}
	$f$ is defined as
	\begin{equation}
		f(x,g) = \frac{\Sigma_{i=1}^N \psi_i w_i}{\Sigma_{i=1}^N \psi_i} x(g - y_0)
		\label{eq:cs_with_f}
	\end{equation}

	where:
	\begin{itemize}
		\item $y_0$ is the initial state of the system
		\item $w_i$ is a weighting for a given basis function $\psi_i$
		\item $\psi_i = \textrm{exp}\left( -h_i \left( x - c_i\right)^2 \right)$ is Gaussian with mean $c_i$ and variance $h_i$
	\end{itemize}

	\vskip -1em
	\begin{columns}
		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[height=2.1cm]{psi_activation}
				\vskip -0.3em
				\caption{$\psi$ Activation}
			\end{figure}
		\end{column}

		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[height=2.1cm]{weighted_summation}
				\vskip -0.3em
				\caption{Weighted Summation}
			\end{figure}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Imitating a desired path}
	\linespread{1.4}
	The desired forcing term $f$ which affects the system acceleration, is written as
	\vskip -1.5em
	\begin{equation}
		\textbf{f}_d = \ddot{\textbf{y}}_d - \alpha_y ( \beta_y (g - \textbf{y}) - \dot{\textbf{y}})
		\label{eq:imitate_f}
	\end{equation}
	\vskip -0.5em
	{\small
		where 
		\vskip -1em
		\begin{itemize}
			\item $\textbf{y}_d$ is desired trajectory, given by $\ddot{\textbf{y}}_d = \frac{\partial}{\partial t} \dot{\textbf{y}}_d = \frac{\partial}{\partial t} \frac{\partial}{\partial t} \textbf{y}_d$
		\end{itemize}
	}
	\vskip-0.5em
	\begin{exampleblock}{}
		Choose the weights over the basis functions i.e., minimize\footnotemark
		\vskip-2em
		\begin{equation}
			\Sigma_t \psi_i(t) \left[ f_d(t) - w_i \left\lbrace x(t) (g - y_0)\right\rbrace\right]^2
			\label{eq:minize_fd}
		\end{equation}
	\end{exampleblock}
	\vskip-0.5em
	\begin{figure}
		\includegraphics[width=0.8\textwidth]{imitate_path}
	\end{figure}
	\vskip-1.5em
	\footcitetext{schaal2002scalable}
\end{frame}

\section{Setup and Experiment}
\begin{frame}{Workflow of \textit{Robotic cloth manipulation} task}
	\vskip -0.5em
	\begin{figure}
		\includegraphics[width=0.85\textwidth]{flowchart_beamer_hd}
	\end{figure}
\end{frame}

\begin{frame}{Setup}
	\begin{figure}
		\includegraphics[width=\textwidth]{setup}
	\end{figure}
\end{frame}

\section{Results}
\begin{frame}{Results}
	\begin{columns}[b]
		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{various_posture}
				\caption{Old \& modified posture of mannequin}
			\end{figure}
		\end{column}

		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{trajectory}
				\caption{Left arm trajectories of Baxter Robot}
			\end{figure}
		\end{column}
	\end{columns}

	\vskip 1em
	\centering{
		\href{run:./videos/video.mp4}{\beamerbutton{Video demonstration}}
	}
\end{frame}

\section{Conclusion and Discussion}
\begin{frame}{Conclusion and Discussion}
	\linespread{1.5}

	\begin{itemize}
		\item Result shows that DMPs are able to generalize the movement trajectory
		\item The converted trajectory from Cartesian Space to Joint Space was not smooth in some regions
		      \begin{itemize}
		      	\item It was calculated using \textsc{Trac\_IK}\footcite{beeson2015trac}
		      \end{itemize}
		\item Also real-time tracking of mannequin is required
	\end{itemize}
\end{frame}

\section{Future work}
\begin{frame}{Tentative Research Plan}

	\begin{figure}
		\includegraphics[width=\textwidth]{timeline}
	\end{figure}
\end{frame}

\begin{frame}[noframenumbering]{References}
	\nocite{*}
	\hspace*{0.5cm}
	\begin{minipage}{\dimexpr\textwidth-1cm\relax}
		\printbibliography
	\end{minipage}
\end{frame}

\begin{frame}[noframenumbering]{The End}
	\begin{center}
		\Huge Thanks for your attention!
		\vskip 1em \huge Any questions?
		\vskip 2em \normalsize \url{www.ravijoshi.xyz}
	\end{center}
\end{frame}

\end{document}

### 2017-06-16 paper/images/flowchart/flowchart_beamer_hd.tex
[major] add updated presentation for conference

\documentclass[11pt]{beamer}
\usefonttheme{serif}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric,backgrounds,positioning-plus,node-families,calc}
\tikzset{
  basic box/.style = {
    shape = rectangle,
    align = center,
    draw  = #1,
    fill  = #1!25,
    font  = \Large,
    rounded corners},
  header node/.style = {
    %Minimum Width = header nodes,
    font          = \huge\bf,
    text depth    = +0pt,
    fill          = white,
    draw},
  header/.style = {%
    inner xsep = +1.2em,
    inner ysep = +1.5em,
    append after command = {
      \pgfextra{\let\TikZlastnode\tikzlastnode}
      node [header node] (header-\TikZlastnode) at (\TikZlastnode.north) {#1}
      node [span = (\TikZlastnode)(header-\TikZlastnode)]
        at (fit bounding box) (h-\TikZlastnode) {}
    }
  },
  hv/.style = {to path = {-|(\tikztotarget)\tikztonodes}},
  vh/.style = {to path = {|-(\tikztotarget)\tikztonodes}},
  fat blue line/.style = {ultra thick, blue}
}
\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=0.2em,text margin right=0.2em}

\def \scaling {0.15}
\begin{document}
\begin{frame}
%\hskip -2em
\begin{tikzpicture}[scale=0.52, every node/.style={transform shape}, thick, >=latex]
	\node[basic box = blue, header = Teaching Phase] (teaching) {
		\includegraphics[scale=\scaling]{teaching_hd}\\
		A demonstration is performed by moving the \\
		Baxter arms in the appropriate trajectory
	};

	\node[north right = of teaching, basic box = orange, header = Trajectory Parameterization, shift = (right:1.2*x_node_dist)] (dmp) {
		Baxter Left Arm Trajectory\\
		\includegraphics[scale=\scaling]{dmp_hd}\\
		Recorded trajectory is parameterized by DMP
	};

	\node[east below = of teaching, basic box = green, header = Testing Phase] (testing) {
		Modified Posture\\
		\includegraphics[scale=\scaling]{testing_hd}\\
		DMP can accomodate any posture by \\
		changing goal parameter
	};

	\node[north right = of testing, basic box = red, header = DMP Generalization, shift = (right:1.2*x_node_dist)] (generalization){
		DMP Trajectory\\
		\includegraphics[scale=\scaling]{dmp_new_hd}
	};

    \path[ultra thick, blue, ->](teaching) edge[->] (dmp);
	\path[ultra thick, orange, ->](dmp) edge[->] (testing);
	\path[ultra thick, green, ->](testing) edge[->] (generalization);
\end{tikzpicture}
\end{frame}
\end{document}

### 2017-06-16 paper/paper.tex
[minor] comments from sensei
[major] add updated presentation for conference

@@
 
-where desired acceleration $\dot{v}(t)$ can be calculated by double differentiating position data recorded from demonstration as
+where desired acceleration $\dot{v}(t)$ can be calculated by taking second derivative of the positional data recorded from demonstration as
 
@@
 \label{sec:experiments}
-Robotic cloth manipulation task contains a dual arm humanoid robot Baxter.
-Setup of our system is shown in figure \ref{fig:setup}.
-We choose soft mannequin instead of a human for this experiment.
-Both the arms of mannequin are open and given support by a metallic stand, to avoid falling down.
-Mannequin is positioned in such a way so that it resides within limits of workspace of Baxter robot.
-Both the arms of mannequin are facing towards robot.
-A Kinect V2 \cite{microsoft2014kinect} sensor is mounted on LCD display of Baxter robot.
-Kinect sensor can see the mannequin and clothing article and provides depth information, which is necessary for mannequin tracking.
-The clothing article is put in the arms of Baxter robot manually before starting experiment.
-
-Baxter robot is connected to a computer directly using Ethernet cable.
-It is controlled using Robot Operating System (ROS) \cite{quigley2009ros}, one of the widely used tools by the researchers in robotics community.
-We used Baxter robot's API, which is available and supported by ROS to command the robot.
-Kinect sensor is controlled by open source Kinect API for ROS \cite{iai_kinect2, libfreenect2}.
-We performed following two experiments to validate our approach: (a) Clothing task using position DMP (b) Failure detection using end-effector forces.
-
 \subsection{Clothing task using position DMP}

### 2017-06-16 presentation/presentation.tex
[major] add updated presentation for conference

@@
 
-%\setbeamerfont{author}{size=\footcitesize}
-%\setbeamerfont{institute}{size=\tiny}
 \setbeamertemplate{navigation symbols}{}
@@
 \author[Ravi P. Joshi]{Ravi P. Joshi$^a$, Nishanth Koganti$^{a,b}$, and Tomohiro Shibata$^a$}
-\institute[]{\tiny{$^a$ Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Kitakyushu, Japan\\$^b$ Graduate School of Information Science, Nara Institute of Science and Technology, Nara, Japan}}
+\institute[]{\tiny{$^a$Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Kitakyushu, Japan\\$^b$Graduate School of Information Science, Nara Institute of Science and Technology, Nara, Japan}}
 
-\date[]{{June 28, 2017}}
-%\date[]{}
+\date[]{{June 29, 2017}}
 
@@
 {
-  \usebackgroundtemplate{\includegraphics[width=\paperwidth]{background.pdf}}
+	\usebackgroundtemplate{\includegraphics[width=\paperwidth]{background}}
 	\setbeamertemplate{footline}{} 
@@
 \begin{frame}{Introduction}
-	\linespread{1.6}
-
+	\linespread{1.5}
+	\begin{columns}[t]
+		\begin{column}{0.65\textwidth}
 			\begin{itemize}
@@
 			\end{itemize}
+		\end{column}
+
+		\begin{column}{0.35\textwidth}
+			\begin{figure}
+				\includegraphics[width=0.8\textwidth]{robotic_clothing_assistance}
+			\end{figure}
+		\end{column}
+	\end{columns}
 
@@
 					\item[\color{green}{\checkmark}] Triangulated mesh model for simulating clothing article
-					\item[\color{red}{$\times$}] Simple manipulations such as gripping using one arm only
+					\item[\color{red}{$\times$}] Highly depends on simulated contour information.
 				\end{itemize}
@@
 	\begin{figure}
-		\includegraphics[width=0.85\textwidth]{flowchart_beamer_hd}
+		\includegraphics[width=0.9\textwidth]{flowchart_beamer}
 	\end{figure}
@@
 	\begin{itemize}
+		\item Baxter APIs\footcite{fitzgerald2013developing} are used to get the end-effector forces. Raw forces are found noisy in nature.
 		\item Result shows that DMPs are able to generalize the movement trajectory
-		\item The converted trajectory from Cartesian Space to Joint Space was not smooth in some regions
-		      \begin{itemize}
-		      	\item It was calculated using \textsc{Trac\_IK}\footcite{beeson2015trac}
-		      \end{itemize}
-		\item Also real-time tracking of mannequin is required
+		\item Proposed failure detection method by using force information can detect failures
+		\item DMP should incorporate orientation information as well
 	\end{itemize}
@@
 \section{Future work}
-\begin{frame}{Tentative Research Plan}
+\begin{frame}{Future work}
+	\linespread{1.5}
 
-	\begin{figure}
-		\includegraphics[width=\textwidth]{timeline}
-	\end{figure}
+	\begin{itemize}
+		\item Make approach more robust by using combination of visual and force information
+		\item Need for designing an adaptive controller
+		      \begin{itemize}
+		      	\item For real-time tracking of mannequin
+		      	\item To adapt various failure scenarios
+		      \end{itemize}
+	\end{itemize}
+
+	\begin{exampleblock}{Acknowledgments}
+		This work was supported in part by the Grant-in-Aid for Scientific Research from Japan Society for the Promotion of Science (No. 16H01749).
+	\end{exampleblock}
 \end{frame}

### 2017-06-20 presentation/presentation.tex
[major] ppt for air2017

@@
 
-\section{Results}
-\begin{frame}{Results}
+\section{Experiments and results}
+\begin{frame}{Experiments and results}
 	\begin{columns}[b]
@@
 	}
+\end{frame}
+
+\begin{frame}{Accuracy measurement}
+	Angle of Inclination measures the bending of arms w.r.t. horizontal line in two-dimensional space
+	\begin{columns}[t]
+		\begin{column}{0.4\textwidth}
+			\begin{figure}
+				\includegraphics[width=\textwidth]{inclination_plus}
+				%\caption{Angle of Inclination measures the bending of arms w.r.t. horizontal line in two-dimensional space}
+			\end{figure}
+		\end{column}
+
+		\begin{column}{0.5\textwidth}
+			\begin{figure}
+				\includegraphics[width=\textwidth]{success_rate}
+				%\caption{Left arm trajectories of Baxter Robot}
+			\end{figure}
+		\end{column}
+	\end{columns}
+\end{frame}
+
+\begin{frame}{Failure detection using end-effector forces}
+	\begin{exampleblock}{Procedure}
+		\begin{enumerate}
+			\item Each trajectory is computed by calculating the mean. 
+			\item The force value is norm of force applied in all three Cartesian directions.
+		\end{enumerate}
+	\end{exampleblock}
+
+	\vskip -1em
+	\begin{columns}[t]
+		\begin{column}{0.3\textwidth}
+			\begin{figure}
+				\includegraphics[width=0.8\textwidth]{failure_scenario_2}
+				\caption{A failure scenario}
+			\end{figure}
+		\end{column}
+
+		\begin{column}{0.5\textwidth}
+			\begin{figure}
+				\includegraphics[width=0.9\textwidth]{position_force}
+				\caption{Forces acting on left arm of Baxter}
+			\end{figure}
+		\end{column}
+	\end{columns}
 \end{frame}

### 2017-06-21 presentation/presentation.tex
[major] add improved ppt

--- 2017-06-16 presentation/presentation.tex
@@
 			\item Safe human-robot interaction
-			\item Accurate estimation of human-cloth relationship
+			\item Estimation of human-cloth relationship
 		\end{itemize}
@@
 
-	\vskip -1em
+	%\vskip -1em
 	\begin{columns}[t]
 		\begin{column}{0.5\textwidth}
-			Towner \textit{et al.}\footnotemark, ~Identifying and manipulating clothing article by dual-arm robot
+			Towner \textit{et al.}\footnotemark, ~Manipulating clothing article by dual-arm robot
 			{\scriptsize
 				\begin{itemize}
-					\item[\color{green}{\checkmark}] Used Hidden Markov Model for tracking
-					\item[\color{green}{\checkmark}] Triangulated mesh model for simulating clothing article
-					\item[\color{red}{$\times$}] Highly depends on simulated contour information.
+					%\item[\color{green}{\checkmark}] Used Hidden Markov Model for tracking
+					%\item[\color{green}{\checkmark}] Triangulated mesh model for simulating clothing article
+					%\item[\color{red}{$\times$}] Highly depends on simulated contour information.
+					\item Used Hidden Markov Model for tracking
+					\item Triangulated mesh model for simulating clothing article
+					\item Highly depends on simulated contour information.
 				\end{itemize}
@@
 				\begin{itemize}
-					\item[\color{green}{\checkmark}] Used Reinforcement
-					      learning (RL)
-					\item[\color{green}{\checkmark}] Topology coordinates for human and cloth extremities relationship
-					\item[\color{red}{$\times$}] Limited generalization capability for new postures
+					%\item[\color{green}{\checkmark}] Used Reinforcement learning (RL)
+					%\item[\color{green}{\checkmark}] Topology coordinates for human and cloth extremities relationship
+					%\item[\color{red}{$\times$}] Limited generalization capability for new postures
+					\item Used Reinforcement learning (RL)
+					\item Topology coordinates for human and cloth extremities relationship
+					\item Via-point trajectory with minimum jerk criterion
 				\end{itemize}
@@
 	\vskip -1em
-	\begin{equation}
+	\begin{equation*}
 		\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y}) + f
 		\label{eq:attractor_with_f}
-	\end{equation}
+	\end{equation*}
 	%\vskip -0.5em
@@
 $f$ is defined as
-	\begin{equation}
+\vskip-2.8em
+	\begin{equation*}
 		f(x,g) = \frac{\Sigma_{i=1}^N \psi_i w_i}{\Sigma_{i=1}^N \psi_i} x(g - y_0)
 		\label{eq:cs_with_f}
-	\end{equation}
-
+	\end{equation*}
+\vskip-0.5em
+{\small
 where:
+\vskip-0.8em
 	\begin{itemize}
+	\setlength\itemsep{0.2em}
 		\item $y_0$ is the initial state of the system
@@
 	\end{itemize}
-
-	\vskip -1em
-	\begin{columns}
-		\begin{column}{0.5\textwidth}
-			\begin{figure}
-				\includegraphics[height=2.1cm]{psi_activation}
-				\vskip -0.3em
-				\caption{$\psi$ Activation}
-			\end{figure}
-		\end{column}
-
-		\begin{column}{0.5\textwidth}
-			\begin{figure}
-				\includegraphics[height=2.1cm]{weighted_summation}
-				\vskip -0.3em
-				\caption{Weighted Summation}
-			\end{figure}
-		\end{column}
-	\end{columns}
-\end{frame}
-
-\begin{frame}{Imitating a desired path}
-	\linespread{1.4}
+}
+\vskip-1.2em
+\begin{exampleblock}{Imitating a desired path}
 	The desired forcing term $f$ which affects the system acceleration, is written as
-	\vskip -1.5em
-	\begin{equation}
+	\vskip-2.4em
+	\begin{equation*}
 		\textbf{f}_d = \ddot{\textbf{y}}_d - \alpha_y ( \beta_y (g - \textbf{y}) - \dot{\textbf{y}})
 		\label{eq:imitate_f}
-	\end{equation}
+	\end{equation*}
 	\vskip -0.5em
@@
 	}
-	\vskip-0.5em
-	\begin{exampleblock}{}
 Choose the weights over the basis functions i.e., minimize\footnotemark
-		\vskip-2em
-		\begin{equation}
+		\vskip-1em
+		\begin{equation*}
 			\Sigma_t \psi_i(t) \left[ f_d(t) - w_i \left\lbrace x(t) (g - y_0)\right\rbrace\right]^2
 			\label{eq:minize_fd}
-		\end{equation}
+		\end{equation*}
 \end{exampleblock}
-	\vskip-0.5em
-	\begin{figure}
-		\includegraphics[width=0.8\textwidth]{imitate_path}
-	\end{figure}
 \vskip-1.5em
@@
 \end{frame}
+
+%\begin{frame}{Forcing function $f$}
+%	$f$ is defined as
+%	\begin{equation}
+%		f(x,g) = \frac{\Sigma_{i=1}^N \psi_i w_i}{\Sigma_{i=1}^N \psi_i} x(g - y_0)
+%		\label{eq:cs_with_f}
+%	\end{equation}
+%
+%	where:
+%	\begin{itemize}
+%		\item $y_0$ is the initial state of the system
+%		\item $w_i$ is a weighting for a given basis function $\psi_i$
+%		\item $\psi_i = \textrm{exp}\left( -h_i \left( x - c_i\right)^2 \right)$ is Gaussian with mean $c_i$ and variance $h_i$
+%	\end{itemize}
+%
+%	\vskip -1em
+%	\begin{columns}
+%		\begin{column}{0.5\textwidth}
+%			\begin{figure}
+%				\includegraphics[height=2.1cm]{psi_activation}
+%				\vskip -0.3em
+%				\caption{$\psi$ Activation}
+%			\end{figure}
+%		\end{column}
+%
+%		\begin{column}{0.5\textwidth}
+%			\begin{figure}
+%				\includegraphics[height=2.1cm]{weighted_summation}
+%				\vskip -0.3em
+%				\caption{Weighted Summation}
+%			\end{figure}
+%		\end{column}
+%	\end{columns}
+%\end{frame}
+%
+%\begin{frame}{Imitating a desired path}
+%	\linespread{1.4}
+%	The desired forcing term $f$ which affects the system acceleration, is written as
+%	\vskip -1.5em
+%	\begin{equation}
+%		\textbf{f}_d = \ddot{\textbf{y}}_d - \alpha_y ( \beta_y (g - \textbf{y}) - \dot{\textbf{y}})
+%		\label{eq:imitate_f}
+%	\end{equation}
+%	\vskip -0.5em
+%	{\small
+%		where
+%		\vskip -1em
+%		\begin{itemize}
+%			\item $\textbf{y}_d$ is desired trajectory, given by $\ddot{\textbf{y}}_d = \frac{\partial}{\partial t} \dot{\textbf{y}}_d = %\frac{\partial}{\partial t} \frac{\partial}{\partial t} \textbf{y}_d$
+%		\end{itemize}
+%	}
+%	\vskip-0.5em
+%	\begin{exampleblock}{}
+%		Choose the weights over the basis functions i.e., minimize\footnotemark
+%		\vskip-2em
+%		\begin{equation}
+%			\Sigma_t \psi_i(t) \left[ f_d(t) - w_i \left\lbrace x(t) (g - y_0)\right\rbrace\right]^2
+%			\label{eq:minize_fd}
+%		\end{equation}
+%	\end{exampleblock}
+%	\vskip-0.5em
+%	\begin{figure}
+%		\includegraphics[width=0.8\textwidth]{imitate_path}
+%	\end{figure}
+%	\vskip-1.5em
+%	\footcitetext{schaal2002scalable}
+%\end{frame}
 
@@
 
-\section{Results}
-\begin{frame}{Results}
+\section{Experiments and Results}
+\begin{frame}{Experiments and Results}
 	\begin{columns}[b]
@@
 			\begin{figure}
-				\includegraphics[width=\textwidth]{various_posture}
+				\includegraphics[trim={4cm 0 5cm 0},clip,width=\textwidth]{various_posture}
 				\caption{Old \& modified posture of mannequin}
@@
 			\begin{figure}
-				\includegraphics[width=\textwidth]{trajectory}
+				\includegraphics[width=\textwidth]{all_traj}
 				\caption{Left arm trajectories of Baxter Robot}
@@
 	\centering{
-		\href{run:./videos/video.mp4}{\beamerbutton{Video demonstration}}
+		\href{run:./videos/video.mp4}{\beamerbutton{Video Demonstration}}
 	}
@@
 
-\section{Conclusion and Discussion}
-\begin{frame}{Conclusion and Discussion}
+\begin{frame}{Accuracy measurement}
+	Angle of Inclination measures the bending of arms w.r.t. horizontal line in two-dimensional space
+	\begin{columns}[t]
+		\begin{column}{0.4\textwidth}
+			\begin{figure}
+				\includegraphics[width=\textwidth]{inclination_plus}
+				%\caption{Angle of Inclination measures the bending of arms w.r.t. horizontal line in two-dimensional space}
+			\end{figure}
+		\end{column}
+
+		\begin{column}{0.5\textwidth}
+			\begin{figure}
+				\includegraphics[width=\textwidth]{success_rate}
+				%\caption{Left arm trajectories of Baxter Robot}
+			\end{figure}
+		\end{column}
+	\end{columns}
+\end{frame}
+
+%\begin{frame}{Failure detection using end-effector forces}
+%	\begin{exampleblock}{Procedure}
+%		\begin{enumerate}
+%			\item Each trajectory is computed by calculating the mean.
+%			\item The force value is norm of force applied in all three Cartesian directions.
+%		\end{enumerate}
+%	\end{exampleblock}
+%
+%	\vskip -1em
+%	\begin{columns}[t]
+%		\begin{column}{0.3\textwidth}
+%			\begin{figure}
+%				\includegraphics[width=0.8\textwidth]{failure_scenario_2}
+%				\caption{A failure scenario}
+%			\end{figure}
+%		\end{column}
+%
+%		\begin{column}{0.5\textwidth}
+%			\begin{figure}
+%				\includegraphics[width=0.9\textwidth]{position_force}
+%				\caption{Forces acting on left arm of Baxter}
+%			\end{figure}
+%		\end{column}
+%	\end{columns}
+%\end{frame}
+
+\section{Discussion and Conclusion}
+\begin{frame}{Discussion and Conclusion}
 	\linespread{1.5}
@@
 	\begin{itemize}
-		\item Baxter APIs\footcite{fitzgerald2013developing} are used to get the end-effector forces. Raw forces are found noisy in nature.
+		%\item Baxter APIs\footcite{fitzgerald2013developing} are used to get the end-effector forces. Raw forces are found noisy in nature.
+		\item Robotic clothing assistance is challenging since it requires cooperative manipulation
+		\item Clothing article inherits non-rigid and highly deformable properties
 		\item Result shows that DMPs are able to generalize the movement trajectory
-		\item Proposed failure detection method by using force information can detect failures
+		%\item Proposed failure detection method by using force information can detect failures
 		\item DMP should incorporate orientation information as well

### 2017-06-22 presentation/presentation.tex
[minor] add supplement ppt

--- 2017-06-16 presentation/presentation.tex
@@
 
-\begin{frame}[noframenumbering]{Outline}
+\begin{frame}[noframenumbering,label=main]{Outline}
 	\tableofcontents
@@
 		\begin{column}{0.5\textwidth}
-			Towner \textit{et al.}\footnotemark, ~Identifying and manipulating clothing article by dual-arm robot
+			Towner \textit{et al.}\footnotemark, ~Manipulating clothing article by dual-arm robot
 			{\scriptsize
 				\begin{itemize}
-					\item[\color{green}{\checkmark}] Used Hidden Markov Model for tracking
-					\item[\color{green}{\checkmark}] Triangulated mesh model for simulating clothing article
-					\item[\color{red}{$\times$}] Highly depends on simulated contour information.
+					\item Used Hidden Markov Model for tracking
+					\item Triangulated mesh model for simulating clothing article
+					\item Highly depends on simulated contour information.
 				\end{itemize}
@@
 				\begin{itemize}
-					\item[\color{green}{\checkmark}] Used Reinforcement
-					      learning (RL)
-					\item[\color{green}{\checkmark}] Topology coordinates for human and cloth extremities relationship
-					\item[\color{red}{$\times$}] Limited generalization capability for new postures
+					\item Used Reinforcement learning (RL)
+					\item Topology coordinates for human and cloth extremities relationship
+					\item Via-point trajectory with minimum jerk criterion
 				\end{itemize}
@@
 \begin{frame}{Dynamic Movement Primitives (DMP)}
-	%\linespread{1.2}
-
-	\begin{exampleblock}{DMP in a nutshell}
+	%\linespread{0.8}
+	Used for generating control signal to guide real system\footnotemark
+	\begin{exampleblock}{Why DMP?}
 		\begin{itemize}
-			\item It is used for generating a control signal to guide the real system\footnotemark
-			\item It can represent \textit{nonlinear} motion with a set of differential equations
+			\item A \textit{non-linear} dynamical system used for policy parameterization
+			\item Can adapt to complex motor-skills
+			\item Also perform target tracking and obstacle avoidance
 		\end{itemize}
@@
 
-	%	We start with point attractor dynamics\footcite{ijspeert2002movement} \hskip1em $\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y})$
-
-	%	\vskip -1em
-	%	\begin{equation}
-	%		\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y})
-	%		\label{eq:attractor}
-	%	\end{equation}
-	%	\vskip -0.5em
-
-	%	\vskip 1em
-	%	Now add a forcing term $f$ on eq(\ref{eq:attractor}) that will let us to modify this trajectory
 	The system is defined as
 	\vskip -1em
-	\begin{equation}
+	\begin{equation*}
 		\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y}) + f
 		\label{eq:attractor_with_f}
-	\end{equation}
-	%\vskip -0.5em
+	\end{equation*}
+	\vskip -0.5em
 	{\small
@@
 		\begin{itemize}
-			\itemsep-0.2em
+			\itemsep0.1em
 			\item $y$ is system state and $g$ is goal state
@@
 	}
-
+	\vskip -0.6em
 	\begin{exampleblock}{}
@@
 
+	\vskip -0.6em
 	\footcitetext{schaal2006dynamic}
@@
 	$f$ is defined as
-	\begin{equation}
+	\vskip-2.8em
+	\begin{equation*}
 		f(x,g) = \frac{\Sigma_{i=1}^N \psi_i w_i}{\Sigma_{i=1}^N \psi_i} x(g - y_0)
 		\label{eq:cs_with_f}
-	\end{equation}
-
+	\end{equation*}
+	\vskip-0.5em
+	{\small
 		where:
+		%\vskip-0.8em
 		\begin{itemize}
+			\setlength\itemsep{0.2em}
 			\item $y_0$ is the initial state of the system
@@
 		\end{itemize}
-
-	\vskip -1em
-	\begin{columns}
-		\begin{column}{0.5\textwidth}
-			\begin{figure}
-				\includegraphics[height=2.1cm]{psi_activation}
-				\vskip -0.3em
-				\caption{$\psi$ Activation}
-			\end{figure}
-		\end{column}
-
-		\begin{column}{0.5\textwidth}
-			\begin{figure}
-				\includegraphics[height=2.1cm]{weighted_summation}
-				\vskip -0.3em
-				\caption{Weighted Summation}
-			\end{figure}
-		\end{column}
-	\end{columns}
-\end{frame}
-
-\begin{frame}{Imitating a desired path}
-	\linespread{1.4}
+	}
+	\vskip-1em
+	\begin{exampleblock}{Imitating a desired path}
 		The desired forcing term $f$ which affects the system acceleration, is written as
-	\vskip -1.5em
-	\begin{equation}
+		\vskip-1em
+		\begin{equation*}
 			\textbf{f}_d = \ddot{\textbf{y}}_d - \alpha_y ( \beta_y (g - \textbf{y}) - \dot{\textbf{y}})
 			\label{eq:imitate_f}
-	\end{equation}
-	\vskip -0.5em
-	{\small
-		where 
-		\vskip -1em
-		\begin{itemize}
-			\item $\textbf{y}_d$ is desired trajectory, given by $\ddot{\textbf{y}}_d = \frac{\partial}{\partial t} \dot{\textbf{y}}_d = \frac{\partial}{\partial t} \frac{\partial}{\partial t} \textbf{y}_d$
-		\end{itemize}
-	}
-	\vskip-0.5em
-	\begin{exampleblock}{}
+		\end{equation*}
+
 		Choose the weights over the basis functions i.e., minimize\footnotemark
-		\vskip-2em
-		\begin{equation}
+		\vskip-1em
+		\begin{equation*}
 			\Sigma_t \psi_i(t) \left[ f_d(t) - w_i \left\lbrace x(t) (g - y_0)\right\rbrace\right]^2
 			\label{eq:minize_fd}
-		\end{equation}
+		\end{equation*}
 	\end{exampleblock}
-	\vskip-0.5em
-	\begin{figure}
-		\includegraphics[width=0.8\textwidth]{imitate_path}
-	\end{figure}
 	\vskip-1.5em
@@
 
-\section{Conclusion and Discussion}
-\begin{frame}{Conclusion and Discussion}
+\begin{frame}{Accuracy measurement}
+	Angle of Inclination measures the bending of arms w.r.t. horizontal line in two-dimensional space
+	\begin{columns}[t]
+		\begin{column}{0.4\textwidth}
+			\begin{figure}
+				\includegraphics[width=\textwidth]{inclination_plus}
+			\end{figure}
+		\end{column}
+
+		\begin{column}{0.5\textwidth}
+			\begin{figure}
+				\includegraphics[width=\textwidth]{success_rate}
+			\end{figure}
+		\end{column}
+	\end{columns}
+\end{frame}
+
+\section{Discussion and Conclusion}
+\begin{frame}{Discussion and Conclusion}
 	\linespread{1.5}
@@
 	\begin{itemize}
-		\item Baxter APIs\footcite{fitzgerald2013developing} are used to get the end-effector forces. Raw forces are found noisy in nature.
+		\item Robotic clothing assistance is challenging since it requires cooperative manipulation
+		\item Clothing article inherits non-rigid and highly deformable properties
 		\item Result shows that DMPs are able to generalize the movement trajectory
-		\item Proposed failure detection method by using force information can detect failures
 		\item DMP should incorporate orientation information as well
@@
 	\end{center}
+	\centering{\hyperlink{supplemental}{\beamerbutton{supplemental here}}}
 \end{frame}
 
+\appendix
+\section{More}
+\begin{frame}[noframenumbering,label=supplemental]
+	\frametitle{Dynamic Movement Primitives (DMP)}
+	\linespread{1.2}
+
+	\begin{exampleblock}{DMP in a nutshell}
+		\begin{itemize}
+			\item A method of trajectory control/planning\footnotemark
+			\item Complex movements are considered as composed of sets of primitive action ‘building blocks’
+			      \begin{itemize}
+			      	\item Executed in sequence \textit{and/or} in parallel
+			      	\item DMPs are a proposed mathematical formalization of these primitives.
+			      \end{itemize}
+			\item It can represent \textit{nonlinear} motion with a set of differential equations
+			\item These equations can be adapted to generate any movement trajectory
+		\end{itemize}
+	\end{exampleblock}
+
+	\footnotetext{\tiny Schaal, Stefan.
+``Dynamic movement primitives-a framework for motor control in humans and humanoid robotics." Adaptive Motion of Animals and Machines.
+Springer Tokyo, 2006.
+261-280.}
+\end{frame}
+
+\begin{frame}[noframenumbering]{Formulation of DMP}
+	\linespread{1.2}
+
+	\textit{DMP is for generating a control signal to guide the real system}
+
+	\begin{alertblock}{Underlying Idea\footnotemark}
+		\begin{enumerate}
+			\item Take a dynamical system with well specified stable behaviour
+			\item Add another term that makes it follow some interesting trajectory
+		\end{enumerate}
+	\end{alertblock}
+
+	\vskip 1em			
+	There are two kinds of DMP:
+	\vskip -0.5em
+	\begin{columns}
+		\begin{column}{0.5\textwidth}
+			\begin{center}
+				\textsc{Discrete} DMP
+				\vskip -0.5em
+				\begin{figure}
+					\includegraphics[height=2cm]{images/ptp_motion}
+					\vskip -0.5em
+					\caption{Point to Point Motion}
+				\end{figure}
+			\end{center}
+		\end{column}
+
+		\begin{column}{0.5\textwidth}
+			\begin{center}
+				\textsc{Rhythmic} DMP
+				\vskip -0.5em
+				\begin{figure}
+					\includegraphics[height=2cm]{images/human_locomotion}
+					\vskip -0.5em
+					\caption{Human Walking}
+				\end{figure}
+			\end{center}
+		\end{column}
+	\end{columns}
+
+	\footnotetext{\tiny Ijspeert, A. J., J. Nakanishi, and S. Schaal. ``Learning control policies for movement imitation and movement recognition." Neural information processing system. Vol. 15. 2003.}
+\end{frame}
+
+\begin{frame}[noframenumbering]{Formulation of DMP}
+	Let's start with point attractor dynamics\footnote{\tiny Ijspeert, Auke Jan, Jun Nakanishi, and Stefan Schaal.
+``Movement imitation with nonlinear dynamical systems in humanoid robots." Robotics and Automation, 2002.
+Proceedings.
+ICRA'02.
+IEEE International Conference on.
+Vol.
+2.
+IEEE, 2002.}
+
+	\vskip -1em
+	\begin{equation}
+		\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y})
+		\label{eq:attractor}
+	\end{equation}
+	\vskip -0.5em
+	where:
+	\begin{itemize}
+		\item $y$ is system state and $g$ is goal state
+		\item $\alpha$ and $\beta$ are gain terms
+	\end{itemize}
+
+	\vskip 1em
+	Now add a forcing term $f$ on eq(\ref{eq:attractor}) that will let us to modify this trajectory
+	\begin{equation}
+		\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y}) + f
+		\label{eq:attractor_with_f}
+	\end{equation}
+	$f$ is nonlinear function defined over time.
+
+	\begin{exampleblock}{}
+		\begin{itemize}
+			\item[*] The introduced system in eq(\ref{eq:attractor_with_f}) is called the \textit{canonical system}.
+			\item[*]  It is denoted by $x$ as $\dot{x} = -\alpha_x x$
+		\end{itemize}
+	\end{exampleblock}
+\end{frame}
+
+\begin{frame}[noframenumbering]{Formulation of DMP}
+	The forcing function $f$ is defined as a function of the canonical system:
+	\begin{equation}
+		f(x,g) = \frac{\Sigma_{i=1}^N \psi_i w_i}{\Sigma_{i=1}^N \psi_i} x(g - y_0)
+		\label{eq:cs_with_f}
+	\end{equation}
+	\vskip -1.0em
+	where:
+	\begin{itemize}
+		\item $y_0$ is the initial state of the system
+		\item $w_i$ is a weighting for a given basis function $\psi_i$
+		\item $\psi_i = \textrm{exp}\left( -h_i \left( x - c_i\right)^2 \right)$ is Gaussian with mean $c_i$ and variance $h_i$
+	\end{itemize}
+	\begin{alertblock}{}
+		\small Forcing function $f$ is a set of Gaussians that are \textit{activated} as the canonical system $x$ converges to its target.
+	\end{alertblock}
+
+	\vskip -0.5em
+	\begin{columns}
+		\begin{column}{0.5\textwidth}
+			\begin{figure}
+				\includegraphics[height=2cm]{images/psi_activation}
+				\vskip -0.5em
+				\caption{$\psi$ Activation}
+			\end{figure}
+		\end{column}
+
+		\begin{column}{0.5\textwidth}
+			\begin{figure}
+				\includegraphics[height=2cm]{images/weighted_summation}
+				\vskip -0.5em
+				\caption{Weighted Summation}
+			\end{figure}
+		\end{column}
+	\end{columns}
+\end{frame}
+
+\begin{frame}[noframenumbering]{Imitating a desired path}
+	\linespread{1.4}
+	The forcing term $f$ which affects the system acceleration, can be re-written as
+	\begin{equation}
+		\textbf{f}_d = \ddot{\textbf{y}}_d - \alpha_y ( \beta_y (g - \textbf{y}) - \dot{\textbf{y}})
+		\label{eq:imitate_f}
+	\end{equation}
+	where
+	\begin{itemize}
+		\item $\textbf{y}_d$ is desired trajectory, given by $\ddot{\textbf{y}}_d = \frac{\partial}{\partial t} \dot{\textbf{y}}_d = \frac{\partial}{\partial t} \frac{\partial}{\partial t} \textbf{y}_d$
+	\end{itemize}
+
+	\begin{exampleblock}{Forcing term}					
+		\begin{itemize}
+			\item Comprised of weighted summation of basis functions
+			\item We can use optimization technique like LWR\footnotemark
+			      \begin{itemize}
+			      	\item[*] To choose the weights over our basis functions
+			      	\item[*] Minimize
+			      	      \vskip -2em
+			      	      \begin{equation}
+			      	      	\Sigma_t \psi_i(t)(f_d(t) - w_i (x(t) (g - y_0)))^2
+			      	      	\label{eq:minize_fd}
+			      	      \end{equation}
+			      \end{itemize}
+		\end{itemize}
+	\end{exampleblock}
+
+	\footnotetext{\tiny Cleveland, William S. ``Robust locally weighted regression and smoothing scatterplots." Journal of the American statistical association 74.368 (1979): 829-836.}
+\end{frame}
+
+\begin{frame}[noframenumbering]{Imitating a desired path}
+	The solution\footnote{\tiny Schaal, Stefan, Christopher G.
+Atkeson, and Sethu Vijayakumar.
+``Scalable techniques from nonparametric statistics for real time robot learning." Applied Intelligence 17.1 (2002): 49-60.} of eq(\ref{eq:minize_fd}) $w_i = \frac{\textbf{s}^T \pmb{\psi}_i \textbf{f}_d}{\textbf{s}^T \pmb{\psi}_i \textbf{s}}$	\\
+	where
+	\begin{itemize}
+		\item[] $\textbf{s} = \left( \begin{array}{c}x_{t_0}(g - y_0) \\ \vdots \\ x_{t_N}(g - y_0) \end{array} \right)$ and $\pmb{\psi}_i = \left( \begin{array}{ccc} \psi_i(t_0) & \dots & 0 \\ 0 & \ddots & 0 \\ 0 & \dots & \psi_i(t_n) \end{array} \right)$
+	\end{itemize}
+
+	\begin{figure}
+		\includegraphics[width=0.9\textwidth]{images/imitate_path}
+	\end{figure}
+	\vskip-0.7em
+	%\centering{
+	\tiny{Back to \hyperlink{main}{\beamerbutton{main}}}
+	%}
+\end{frame}
 \end{document}

### 2017-06-25 presentation/presentation.tex
[major] add final ppt for air2017

@@
 
-\begin{frame}[noframenumbering,label=main]{Outline}
-	\tableofcontents
-\end{frame}
+%\begin{frame}[noframenumbering,label=main]{Outline}
+%	\tableofcontents
+%\end{frame}
 
@@
 \begin{frame}{Introduction}
-	\linespread{1.5}
+	%\linespread{1.5}
+
+	\vskip -2em
 	\begin{columns}[t]
-		\begin{column}{0.65\textwidth}
+		\begin{column}{0.6\textwidth}
 			\begin{itemize}
-				\item Clothing assistance is a basic and important assistance activity in the daily life of the elderly and disabled people
-				\item Need of robotic clothing assistance is growing
+				\item Japan is a super-aging society
+				\item In 2030, 1.8 person is supposed to care 1 elderly
+				\item 400,000 care givers are lacking now
+				\item Clothing is one of the most suffering daily activities for elderly
 			\end{itemize}
@@
 
-		\begin{column}{0.35\textwidth}
+		\begin{column}{0.4\textwidth}
+			\vskip -1em
 			\begin{figure}
-				\includegraphics[width=0.8\textwidth]{robotic_clothing_assistance}
+				\includegraphics[trim={4px 4px 4px 4px},clip,width=\textwidth]{japan_population}
+				\caption{Japan population growth\footnotemark}
 			\end{figure}
@@
 
-	\vskip 1em
+	\vskip -1em
+	\begin{columns}[t]
+		\begin{column}{0.7\textwidth}
 			\begin{block}{Major challenges involved}
 				\begin{itemize}
-			\item Close interaction of the robot with non-rigid clothing article
+					\item Close interaction of the robot with cloth
 					\item Safe human-robot interaction
@@
 			\end{block}
+		\end{column}
+
+		\begin{column}{0.25\textwidth}
+			\begin{figure}
+				\includegraphics[width=0.7\textwidth]{robotic_clothing_assistance}
+			\end{figure}
+		\end{column}
+	\end{columns}
+
+	\footcitetext{jonMcDonald2016japan}
 \end{frame}
@@
 	\begin{equation*}
-		\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y}) + f
+		\ddot{y} = \alpha \left( \beta \left(g - y\right) - \dot{y}\right) + f
 		\label{eq:attractor_with_f}
 	\end{equation*}
+	%\begin{equation*}
+	%	\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y}) + f
+	%	\label{eq:attractor_with_f}
+	%\end{equation*}
 	\vskip -0.5em
@@
 	\begin{exampleblock}{}
-		$f$ is a function of \textit{canonical system}, denoted by $x$ as $\dot{x} = -\alpha_x x$
+		$f$ is a function of \textit{canonical system}%, denoted by $x$ as $\dot{x} = -\alpha_x x$
 	\end{exampleblock}
@@
 	\end{equation*}
-	\vskip-0.5em
+	\vskip -0.5em
 	{\small
@@
 	}
-	\vskip-1em
+	\vskip -1em
 	\begin{exampleblock}{Imitating a desired path}
 		The desired forcing term $f$ which affects the system acceleration, is written as
-		\vskip-1em
+		\vskip -1em
 		\begin{equation*}
@@
 		Choose the weights over the basis functions i.e., minimize\footnotemark
-		\vskip-1em
+		\vskip -1em
 		\begin{equation*}
@@
 	\end{exampleblock}
-	\vskip-1.5em
+	\vskip -1.5em
 	\footcitetext{schaal2002scalable}
+\end{frame}
+
+\begin{frame}{Example of DMP}
+	\vskip -2em
+	\begin{figure}
+		\includegraphics[trim={0 15px 0 0},clip, width=0.9\textwidth]{DMP_BFs}
+		\caption{\small{Effect of \textit{no. of basis functions}}}
+	\end{figure}
+
+	\vskip -2em
+	\begin{figure}
+		\includegraphics[trim={0 14px 0 20px},clip, width=0.9\textwidth]{DMP_Goal}
+		\caption{\small{DMP adaptation to new goal \textit{(new goal = 1.5 * old goal)}}}
+	\end{figure}
 \end{frame}
@@
 	\end{figure}
-	\vskip-0.7em
+	\vskip -0.7em
 	%\centering{

### 2017-08-28 paper/paper.tex
[minor] add DOI in paper.pdf

--- 2017-05-27 paper/paper.tex
@@
 
+\copyrightyear{2017}
+\acmYear{2017}
+
 % Copyright
-%\setcopyright{none}
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
+\setcopyright{acmcopyright}
+
+%Conference
+\acmConference{AIR '17}{June 28-July 2, 2017}{New Delhi, India}
+\acmPrice{15.00}
+
+%ISBN
+\acmISBN{978-1-4503-5294-9/17/06}
 
 % DOI
-\acmDOI{to_be_inserted_after_paper_is_accepted}
-
-% ISBN
-\acmISBN{1-58113-000-0/00/0010}
-
-%Conference
-\acmConference[AIR 2017]{Advances in Robotics}{June 28-July 02, 2017}{New Delhi, India}
-\acmYear{2017}
-\copyrightyear{2017}
-
-\acmPrice{15.00}
+\acmDOI{10.1145/3132446.3134878}
 
@@
 
-\begin{figure}
-	\includegraphics[width=\linewidth]{setup}
-	\caption{Setup of robotic cloth manipulation task}
-	\label{fig:setup}
-\end{figure}
-
 \section{Introduction}
@@
 Clothing assistance is a challenging problem since robot is required to manage two difficulties: (a) robot must do cooperative manipulation by holding clothing article using both the arms while interacting with non-rigid and highly deformable clothing article and (b) maintain safe human-robot interaction with the assisted person whose posture can vary during assistance.
+
+\begin{figure}
+	\includegraphics[width=\linewidth]{setup}
+	\caption{Setup of robotic cloth manipulation task}
+	\label{fig:setup}
+\end{figure}
 
@@
 We choose soft mannequin instead of a human for this experiment.
-Both the arms of mannequin are open and given support by a metallic stand, to avoid falling down.
+Both the arms of mannequin are open and given support by a metallic stand, to avoid falling down the arms.
 Mannequin is positioned in such a way so that it resides within limits of workspace of Baxter robot.
